### 2014-10-08 guidelinesAJS.Rnw
saeSim-Paper template

\documentclass[article]{ajs}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%% almost as usual
\author{Matthias Templ\\ Vienna University of Technology \And 
        Second Author\\Plus Affiliation}
\title{A Capitalized Title: Something about a Topic}

%% for pretty printing and a nice hypersummary also set:
\Plainauthor{Matthias Templ, Second Author} %% comma-separated
\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
\Shorttitle{A Capitalized Title} %% a short title (if necessary)

%% an abstract and keywords
\Abstract{
  The abstract of the article in English

}
\Keywords{keywords, comma-separated, not capitalized, \proglang{R}}
\Plainkeywords{keywords, comma-separated, not capitalized, R} %% without formatting
%% at least one keyword must be supplied

%% publication information
%% NOTE: Typically, this can be left commented and will be filled out by the technical editor
%% \Volume{50}
%% \Issue{9}
%% \Month{June}
%% \Year{2012}
%% \Submitdate{2012-06-04}
%% \Acceptdate{2012-06-04}
%% \setcounter{page}{1}
\Pages{1--xx}

%% The address of (at least) one author should be given
%% in the following format:
\Address{
  Matthias Templ\\
  Department of Statistics and Probability Theory\\
  Vienna University of Technology\\
  A-1040 Vienna, Austria\\
  E-mail: \email{templ@tuwien.ac.at}\\
  URL: \url{http://www.statistik.tuwien.ac.at/public/templ}
}
%% It is also possible to add a telephone and fax number
%% before the e-mail in the following format:
%% Telephone: +43/512/507-7103
%% Fax: +43/512/507-2851

%% for those who use Sweave please include the following line (with % symbols):
%% need no \usepackage{Sweave.sty}

%% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%% include your article here, just as usual

<<echo=FALSE>>=
suppressPackageStartupMessages(library(saeSim))
@

<<>>=
sim_base_lm()
@

\section{Introduction}

Besides the general objectives of the Austrian Journal of
Statistics, this should contain general instructions for
preparation of manuscripts to be submitted. This \LaTeXe\ file can
also be used as a template for the setting up of a text to be
submitted in computer readable form. In any case, use \texttt{pdflatex} to compile your \LaTeX \ file.

The style file of the Austrian Journal of Statsitics uses mainly the style file from the Journal of Statistical Software (JSS) plus minor modifications. We thank Achim Zeileis for his great work on the JSS style file.

The Austrian Journal of Statistics is freely available over the net. Free and open-source tools used for production of your manuscript are therefore also highly supported. Manuscripts can also be sent as \texttt{Sweave} \citep[see, e.g.,][]{leisch02} or \texttt{knitr} \citep{yihui13} files.

%Graphics should be inserted as PostScript files using the
%package {\tt psfig} or {\tt graphicx}. Bibliographic references
%should be given using {\tt bibtex} in the {\em author-date\/}
%style.

\section{Objectives of the journal}

The journal is published approximately quarterly by the Austrian
Statistical Society. Its general objective is to promote and
extend the use of statistical methods in all kind of theoretical
and applied disciplines. Special emphasis is on methods and
results in official or governmental statistics.

Original papers and review articles will be published in the
Austrian Journal of Statistics if judged consistently with these
general aims. All papers will be refereed.

Special issues will appear from time to time. Each
section will have as a theme a specialized area of statistical
application, theory, or methodology.

Technical notes or problems for considerations under Shorter
Communications are also invited.

One author of each article obtains a free copy of the entire issue
in which the article is contained. Members of the Austrian
Statistical Society receive a copy of the Journal free of charge.
Specific volumes may be purchased from the Society.

Articles will also be made available through the web at 
\begin{center}
\href{http://www.ajs.or.at}{http://www.ajs.or.at}
\end{center}

\subsection{Statistics: theory and applications}

The section for {\bf theory} and methods publishes articles that
make original contributions to the foundations, theoretical
development, and methodology of statistics and probability. {\em
Theory and Methods\/} should be interpreted broadly to include all
techniques relevant to statistics and probability. This may
include computational and graphical methods as well as more
traditional mathematical methods. The research reported should be
motivated by a scientific or practical problem and illustrated by
application of the proposed methodology to that problem.
Illustration of techniques with real data is especially welcomed
and strongly encouraged.
\medskip

{\bf Applications} and case studies are published if they present
original articles which
\begin{list}{$\bullet$}{\setlength{\topsep}{0mm}\setlength{\itemsep}{-1mm}}
 \item show analysis with real data that are statistically
       innovative as well as scientifically and practically relevant, or
 \item contribute substantially to a scientific field through the
       use of sound statistical methods, or
 \item present new and useful data, such as a new life table for
       a segment of the population or a new social or economic
       indicator, or
 \item using empirical tests, examine or illustrate for an important
       application the utility of a valuable statistical technique, or
 \item evaluate the quality of important data sources.
\end{list}
Note that careful analysis of data of substantive importance may be
published even there are no methodological innovations.

\subsection{Official statistics}

The section for {\bf official statistics} publishes articles which
deal with conceptual methods and computational issues. The
different fields covered include
\begin{list}{$\bullet$}{\setlength{\topsep}{0mm}\setlength{\itemsep}{-1mm}}
 \item population and social statistics
 \item economic statistics
 \item price statistics
 \item regional and urban statistics
 \item economic and social statistics
 \item tourism statistics
 \item research, development and innovation statistics
 \item environmental statistics including environmental accounting and
       environmental indicators
 \item national accounts including input-output tables and analysis.
\end{list}
Especially welcomed are articles which are concerned in
\begin{list}{$\bullet$}{\setlength{\topsep}{0mm}\setlength{\itemsep}{-1mm}}
 \item statistical disclosure control methods
 \item model-based methods
 \item publication policies (presentation of statistics)
 \item data pre-processing
 \item data visualisation
 \item survey methodology
\end{list}
Of course, papers treating national as well as international
concepts (e.g.~EU-statistics) are of interest.

\section{Style files for the manuscript}

The Journal is produced on the basis of computer readable
manuscripts provided by the authors.

In order to obtain a uniform layout and to ease the production as
much as possible it is highly recommended to use \LaTeXe\ for the
text processing. Graphics should be added in pdf or png format
 at suitable places of the manuscript.

We highly recommend
to follow exactly the provided instructions already at the very
beginning when writing the paper. The present document can be used
directly as template. The file named {\tt guidelinesAJS.tex} may be
obtained from the site

\href{http://www.ajs.or.at/index.php/ajs/about/submissions\#authorGuidelines}{http://www.ajs.or.at/index.php/ajs/about/submissions\#authorGuidelines}

Please consider title case for titles and for references. Sentence case for  sections and subsections.

\subsection{Submission}

A manuscript should be submitted to
\begin{center}
\href{http://www.ajs.or.at/index.php/ajs/about/submissions\#onlineSubmissions}{http://www.ajs.or.at/index.php/ajs/about/submissions\#onlineSubmissions}
\end{center}

in
electronic form following the editorial system. For further questions for submission and on the editorial system, send an e-mail to \href{templ@statistik.tuwien.ac.at}{templ@statistik.tuwien.ac.at}.

\subsection{Formal configuration}

Each article must have a summary in English and German which
inform the reader quickly on the contents and the substantial
results. The length surely depends on the contents, however, it
should not exceed 150 words. Mathematical formulas and references should be
avoided in the summary.

Headings and footings as well as pagination will be added during
the production. Footnotes should be avoided as much as possible.

The article should be structured by enumerated sections and
subsections. The title should be in title case style, sections and subsections in section case style. Graphics and tables must contain captions, above
tables and below graphics (figures). Examples are (see Figure~\ref{Fig3.4} and Table~\ref{Tab3.4})

\begin{figure}[hbt]
\centerline{\sl Here should be a graphic using the includegraphics command (pdf or png format).}
\caption{\label{Fig3.4}The caption of the figure to be filled in.} 
\end{figure}

\begin{table}[hbt]
\caption{\label{Tab3.4}80 measured values of access time.}
\vspace*{-5mm}
\small
\hspace{1.5cm}
\begin{center}
\begin{tabular}{llllllll}
70.0 & 68.6 & 67.9 & 66.3 & 71.0 & 64.2 & 69.6 & 71.0\\
... & ... & ... & ... & ... & ... & ... & ...\\
%69.7 & 69.0 & 73.4 & 69.0 & 70.1 & 69.8 & 69.0 & 73.0\\
%70.0 & 69.1 & 69.5-& 67.9 & 72.8 & 72.1 & 69.5+& 70.1\\
%70.2 & 69.1 & 68.9 & 68.3 & 74.9 & 68.4 & 69.1 & 66.6\\
%71.1 & 69.2 & 71.2 & 68.9 & 70.9 & 70.6 & 69.9 & 69.9\\
%69.4 & 69.5+& 68.5+& 70.9 & 71.6 & 68.9 & 72.0 & 70.3\\
%68.6 & 68.5-& 67.8 & 72.2 & 68.7 & 70.6 & 66.9 & 69.3\\
%71.4 & 68.7 & 74.2 & 68.8 & 71.4 & 71.8 & 67.5-& 70.4\\
%71.4 & 67.4 & 69.5-& 72.4 & 70.4 & 69.3 & 68.2 & 67.0\\
71.7 & 70.5+& 72.5-& 68.2 & 67.6 & 68.6 & 70.5-& 65.8
\vspace*{-5mm}
\end{tabular}
\end{center}
\end{table}

Mathematical formulas should be enumerated as far as they are
referenced. E.g.~Equation~(\ref{form3.1}) shows the density ...
\begin{equation}\label{form3.1}
f(x) =
\frac1{\sqrt{2\pi}\sigma}e^{-\frac{(x-\mu)^2}{2\sigma^2}}\,.
\end{equation}

Cited literature should be summarized at the end of the article in
form of a non-enumerated section. \cite{leisch02} is a reference
to an article. If the citation is in parentheses, it
should look like \citep{leisch02}.
References should be in title case.

Correspondence addresses of author(s) should be added at the end
of the manuscript.

\section{Submission and refereeing}

Consideration of the previously stated rules are of great help for
the editing process. Whenever technically possible, manuscripts
should be submitted through the editorial system at \href{www.ajs.or.at}{www.ajs.or.at}.

All contributions will be anonymously refereed. Cited literature which is
hardly available should accompany the submitted manuscript. It
should also be considered to place used and analyzed data at
disposal for the referees (if there are no legal or technical
arguments against).

Editor and referees must trust that the contribution has not been
submitted for publication at the same time at another place. It is
fair that the submitting author notifies if an earlier version has
already been submitted somewhere before.

Manuscripts stay with the publisher and referees. The refereeing
and publishing in the Austrian Journal of Statistics is free of
charge. The publisher, the Austrian Statistical Society requires a
grant of copyright from authors in order to effectively publish
and distribute this journal worldwide.

%\bibliographystyle{plainat}
\bibliography{guidelinesAJS}

\end{document}

### 2014-10-10 guidelinesAJS.Rnw
saeSim paper template

@@
 %% almost as usual
-\author{Matthias Templ\\ Vienna University of Technology \And 
-        Second Author\\Plus Affiliation}
-\title{A Capitalized Title: Something about a Topic}
+\author{Sebastian Warnholz\\ Freie Universit\"at Berlin \And 
+        Timo Schmid \\ Freie Universit\"at Berlin}
+\title{Simulation Tools for Small Area Estimation: Introducing the \proglang{R}-package \proglang{saeSim}}
 
 %% for pretty printing and a nice hypersummary also set:
-\Plainauthor{Matthias Templ, Second Author} %% comma-separated
-\Plaintitle{A Capitalized Title: Something about a Topic} %% without formatting
-\Shorttitle{A Capitalized Title} %% a short title (if necessary)
+\Plainauthor{Sebastian Warnholz, Timo Schmid} %% comma-separated
+\Plaintitle{Simulation Tools for Small Area Estimation: Introducing the R-package saeSim} %% without formatting
+\Shorttitle{Simulation Tools for Small Area Estimation} %% a short title (if necessary)
 
@@
 }
-\Keywords{keywords, comma-separated, not capitalized, \proglang{R}}
-\Plainkeywords{keywords, comma-separated, not capitalized, R} %% without formatting
+\Keywords{package, small area estimation, reproducible research, simulation, \proglang{R}}
+\Plainkeywords{package, small area estimation, reproducible research, simulation, R} %% without formatting
 %% at least one keyword must be supplied
@@
 \Address{
-  Matthias Templ\\
-  Department of Statistics and Probability Theory\\
-  Vienna University of Technology\\
-  A-1040 Vienna, Austria\\
-  E-mail: \email{templ@tuwien.ac.at}\\
-  URL: \url{http://www.statistik.tuwien.ac.at/public/templ}
+  Sebastian Warnholz\\
+  Department of Economics\\
+  Freie Universit\"at Berlin\\
+  D-14195 Berlin, Germany\\
+  E-mail: \email{Sebastian.Warnholz@fu-berlin.de}\\
+  URL: \url{http://www.wiwiss.fu-berlin.de/fachbereich/vwl/Schmid/Team/Warnholz.html}
 }
@@
 
+% Loading (and installing) necessary packages.
 <<echo=FALSE>>=
-suppressPackageStartupMessages(library(saeSim))
-@
+if(!suppressPackageStartupMessages(require(saeSim))) {
+  if(!require(devtools)) {
+    install.packages("devtools", repos = "http://cran.at.r-project.org/", dependencies = TRUE)
+    library(devtools)
+  }
 
-<<>>=
-sim_base_lm()
+  install.packages(c("dplyr", "ggplot2", "MASS", "spdep"), 
+                   repos = "http://cran.at.r-project.org/", dependencies = TRUE)
+  install_github("wahani/saeSim")
+}
 @

### 2014-10-10 guidelinesAJS.tex
saeSim-Paper template
saeSim paper template

--- 2014-10-08 guidelinesAJS.Rnw
@@
 
-<<echo=FALSE>>=
-suppressPackageStartupMessages(library(saeSim))
-@
-
-<<>>=
-sim_base_lm()
-@
+% Loading (and installing) necessary packages.
 

### 2014-10-10 saeSim.Rnw
saeSim paper template

--- 2014-10-10 guidelinesAJS.Rnw
@@
 \section{Introduction}
-
-Besides the general objectives of the Austrian Journal of
-Statistics, this should contain general instructions for
-preparation of manuscripts to be submitted. This \LaTeXe\ file can
-also be used as a template for the setting up of a text to be
-submitted in computer readable form. In any case, use \texttt{pdflatex} to compile your \LaTeX \ file.
-
-The style file of the Austrian Journal of Statsitics uses mainly the style file from the Journal of Statistical Software (JSS) plus minor modifications.
-We thank Achim Zeileis for his great work on the JSS style file.
-
-The Austrian Journal of Statistics is freely available over the net.
-Free and open-source tools used for production of your manuscript are therefore also highly supported.
-Manuscripts can also be sent as \texttt{Sweave} \citep[see, e.g.,][]{leisch02} or \texttt{knitr} \citep{yihui13} files.
+A brief overview of what the reader can expect of this article.
+What is the aim of this article and where can it be located in science.
+Discussion of the reproducible research movement and where the package may be beneficial.
+Packages like Sweave, knitr, R-markdown.
+How can simulation studies (the \proglang{R}-code) be published?
+As script?
+As stand-alone-package?
+How can ideas for specific data generation tools be shared amongst the small area community and thus be more transparent: saeSim (far-fetched but anyway).
 
@@
 
-\section{Objectives of the journal}
+\section{Simulation studies in small area estimation}
+The role of simulation studies in the field.
+Separation into model-based and design-based simulation studies.
+How does \proglang{saeSim} address these 2 perspectives?
+Identifying steps/phases/components of simulation studies (data generation, sampling, computation).
 
-The journal is published approximately quarterly by the Austrian
-Statistical Society. Its general objective is to promote and
-extend the use of statistical methods in all kind of theoretical
-and applied disciplines. Special emphasis is on methods and
-results in official or governmental statistics.
+\section{saeSim: A simulation framework}
+Introducing a simulation study as a data manipulation process.
+From data generation to estimating models.
+How can this process be mapped into the \proglang{R}-language.
+Present the simulation phases as flow-diagram and map the function names to the problem domain.
+Defining interfaces between phases: \proglang{data.frame} in, \proglang{data.frame} out.
+What is the difference between a design-based (fixed-population) and model-based (random-population) approach.
 
-Original papers and review articles will be published in the
-Austrian Journal of Statistics if judged consistently with these
-general aims. All papers will be refereed.
+Why is this package helping in terms of literate programming (code is written for humans not machines) and reproducible research?
+Package naming conventions.
+Use the \proglang{\%>\%} operator to compose simulation set-ups.
+Reuse defined scenarios to compose new scenarios: What is a contamination scenario?
+A standard scenario plus contamination:
 
-Special issues will appear from time to time. Each
-section will have as a theme a specialized area of statistical
-application, theory, or methodology.
+<<eval=FALSE>>=
+contaminatedSetup <- standardSetup %>% sim_gen_cont()
+@
 
-Technical notes or problems for considerations under Shorter
-Communications are also invited.
+\subsection{Data generation}
+This is not a data generation tool.
+However, it supports some useful functions to add random variates to the data.
+Definition of outliers, see Rao (?) -- how is it addressed in the package.
+More than linear models, define any response with:
+<<eval=FALSE>>=
+setup %>% sim_resp_eq(y = g(2 * x) + e)
+@
 
-One author of each article obtains a free copy of the entire issue
-in which the article is contained. Members of the Austrian
-Statistical Society receive a copy of the Journal free of charge.
-Specific volumes may be purchased from the Society.
+\subsection{Drawing samples}
+Is present in unit-level simulation studies.
+Draw with simple random sampling from the whole population or within cluster/domains.
+Specify the sample size as integer or fraction and add weights if necessary.
+Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
 
-Articles will also be made available through the web at 
-\begin{center}
-\href{http://www.ajs.or.at}{http://www.ajs.or.at}
-\end{center}
+\subsection{Adding customized computations}
+Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
+The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
+I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
 
-\subsection{Statistics: theory and applications}
+\subsection{Separation of designing and running simulations}
+First develop a scenario outside any looping structures, then run it R-times:
 
-The section for {\bf theory} and methods publishes articles that
-make original contributions to the foundations, theoretical
-development, and methodology of statistics and probability. {\em
-Theory and Methods\/} should be interpreted broadly to include all
-techniques relevant to statistics and probability. This may
-include computational and graphical methods as well as more
-traditional mathematical methods. The research reported should be
-motivated by a scientific or practical problem and illustrated by
-application of the proposed methodology to that problem.
-Illustration of techniques with real data is especially welcomed
-and strongly encouraged.
-\medskip
+<<eval=FALSE>>=
+simulationResults <- simSetup %>% sim(R = 500)
+@
 
-{\bf Applications} and case studies are published if they present
-original articles which
-\begin{list}{$\bullet$}{\setlength{\topsep}{0mm}\setlength{\itemsep}{-1mm}}
- \item show analysis with real data that are statistically
-       innovative as well as scientifically and practically relevant, or
- \item contribute substantially to a scientific field through the
-       use of sound statistical methods, or
- \item present new and useful data, such as a new life table for
-       a segment of the population or a new social or economic
-       indicator, or
- \item using empirical tests, examine or illustrate for an important
-       application the utility of a valuable statistical technique, or
- \item evaluate the quality of important data sources.
-\end{list}
-Note that careful analysis of data of substantive importance may be
-published even there are no methodological innovations.
+There is an easy back-end to run simulations in parallel (in Windows with special care):
 
-\subsection{Official statistics}
+<<eval=FALSE>>=
+simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE)
+@
 
-The section for {\bf official statistics} publishes articles which
-deal with conceptual methods and computational issues. The
-different fields covered include
-\begin{list}{$\bullet$}{\setlength{\topsep}{0mm}\setlength{\itemsep}{-1mm}}
- \item population and social statistics
- \item economic statistics
- \item price statistics
- \item regional and urban statistics
- \item economic and social statistics
- \item tourism statistics
- \item research, development and innovation statistics
- \item environmental statistics including environmental accounting and
-       environmental indicators
- \item national accounts including input-output tables and analysis.
-\end{list}
-Especially welcomed are articles which are concerned in
-\begin{list}{$\bullet$}{\setlength{\topsep}{0mm}\setlength{\itemsep}{-1mm}}
- \item statistical disclosure control methods
- \item model-based methods
- \item publication policies (presentation of statistics)
- \item data pre-processing
- \item data visualisation
- \item survey methodology
-\end{list}
-Of course, papers treating national as well as international
-concepts (e.g.~EU-statistics) are of interest.
-
-\section{Style files for the manuscript}
-
-The Journal is produced on the basis of computer readable
-manuscripts provided by the authors.
-
-In order to obtain a uniform layout and to ease the production as
-much as possible it is highly recommended to use \LaTeXe\ for the
-text processing. Graphics should be added in pdf or png format
- at suitable places of the manuscript.
-
-We highly recommend
-to follow exactly the provided instructions already at the very
-beginning when writing the paper. The present document can be used
-directly as template. The file named {\tt guidelinesAJS.tex} may be
-obtained from the site
-
-\href{http://www.ajs.or.at/index.php/ajs/about/submissions\#authorGuidelines}{http://www.ajs.or.at/index.php/ajs/about/submissions\#authorGuidelines}
-
-Please consider title case for titles and for references. Sentence case for  sections and subsections.
-
-\subsection{Submission}
-
-A manuscript should be submitted to
-\begin{center}
-\href{http://www.ajs.or.at/index.php/ajs/about/submissions\#onlineSubmissions}{http://www.ajs.or.at/index.php/ajs/about/submissions\#onlineSubmissions}
-\end{center}
-
-in
-electronic form following the editorial system. For further questions for submission and on the editorial system, send an e-mail to \href{templ@statistik.tuwien.ac.at}{templ@statistik.tuwien.ac.at}.
-
-\subsection{Formal configuration}
-
-Each article must have a summary in English and German which
-inform the reader quickly on the contents and the substantial
-results. The length surely depends on the contents, however, it
-should not exceed 150 words. Mathematical formulas and references should be
-avoided in the summary.
-
-Headings and footings as well as pagination will be added during
-the production. Footnotes should be avoided as much as possible.
-
-The article should be structured by enumerated sections and
-subsections. The title should be in title case style, sections and subsections in section case style. Graphics and tables must contain captions, above
-tables and below graphics (figures). Examples are (see Figure~\ref{Fig3.4} and Table~\ref{Tab3.4})
-
-\begin{figure}[hbt]
-\centerline{\sl Here should be a graphic using the includegraphics command (pdf or png format).}
-\caption{\label{Fig3.4}The caption of the figure to be filled in.} 
-\end{figure}
-
-\begin{table}[hbt]
-\caption{\label{Tab3.4}80 measured values of access time.}
-\vspace*{-5mm}
-\small
-\hspace{1.5cm}
-\begin{center}
-\begin{tabular}{llllllll}
-70.0 & 68.6 & 67.9 & 66.3 & 71.0 & 64.2 & 69.6 & 71.0\\
-... & ... & ... & ... & ... & ... & ... & ...\\
-%69.7 & 69.0 & 73.4 & 69.0 & 70.1 & 69.8 & 69.0 & 73.0\\
-%70.0 & 69.1 & 69.5-& 67.9 & 72.8 & 72.1 & 69.5+& 70.1\\
-%70.2 & 69.1 & 68.9 & 68.3 & 74.9 & 68.4 & 69.1 & 66.6\\
-%71.1 & 69.2 & 71.2 & 68.9 & 70.9 & 70.6 & 69.9 & 69.9\\
-%69.4 & 69.5+& 68.5+& 70.9 & 71.6 & 68.9 & 72.0 & 70.3\\
-%68.6 & 68.5-& 67.8 & 72.2 & 68.7 & 70.6 & 66.9 & 69.3\\
-%71.4 & 68.7 & 74.2 & 68.8 & 71.4 & 71.8 & 67.5-& 70.4\\
-%71.4 & 67.4 & 69.5-& 72.4 & 70.4 & 69.3 & 68.2 & 67.0\\
-71.7 & 70.5+& 72.5-& 68.2 & 67.6 & 68.6 & 70.5-& 65.8
-\vspace*{-5mm}
-\end{tabular}
-\end{center}
-\end{table}
-
-Mathematical formulas should be enumerated as far as they are
-referenced. E.g.~Equation~(\ref{form3.1}) shows the density ...
-\begin{equation}\label{form3.1}
-f(x) =
-\frac1{\sqrt{2\pi}\sigma}e^{-\frac{(x-\mu)^2}{2\sigma^2}}\,.
-\end{equation}
-
-Cited literature should be summarized at the end of the article in
-form of a non-enumerated section. \cite{leisch02} is a reference
-to an article. If the citation is in parentheses, it
-should look like \citep{leisch02}.
-References should be in title case.
-
-Correspondence addresses of author(s) should be added at the end
-of the manuscript.
-
-\section{Submission and refereeing}
-
-Consideration of the previously stated rules are of great help for
-the editing process. Whenever technically possible, manuscripts
-should be submitted through the editorial system at \href{www.ajs.or.at}{www.ajs.or.at}.
-
-All contributions will be anonymously refereed. Cited literature which is
-hardly available should accompany the submitted manuscript. It
-should also be considered to place used and analyzed data at
-disposal for the referees (if there are no legal or technical
-arguments against).
-
-Editor and referees must trust that the contribution has not been
-submitted for publication at the same time at another place. It is
-fair that the submitting author notifies if an earlier version has
-already been submitted somewhere before.
-
-Manuscripts stay with the publisher and referees. The refereeing
-and publishing in the Austrian Journal of Statistics is free of
-charge. The publisher, the Austrian Statistical Society requires a
-grant of copyright from authors in order to effectively publish
-and distribute this journal worldwide.
+\section{Outlook}
+Use this package to share and publish simulation studies alongside papers.
+Contribute to the package to make your ideas available.
+Contribute to the package and make your whole simulation study available.
 

### 2014-10-10 saeSim.tex
saeSim paper template

--- 2014-10-10 saeSim.Rnw
@@
 % Loading (and installing) necessary packages.
-<<echo=FALSE>>=
-if(!suppressPackageStartupMessages(require(saeSim))) {
-  if(!require(devtools)) {
-    install.packages("devtools", repos = "http://cran.at.r-project.org/", dependencies = TRUE)
-    library(devtools)
-  }
-
-  install.packages(c("dplyr", "ggplot2", "MASS", "spdep"), 
-                   repos = "http://cran.at.r-project.org/", dependencies = TRUE)
-  install_github("wahani/saeSim")
-}
-@
 
@@
 
-<<eval=FALSE>>=
-contaminatedSetup <- standardSetup %>% sim_gen_cont()
-@
+\begin{Schunk}
+\begin{Sinput}
+> contaminatedSetup <- standardSetup %>% sim_gen_cont()
+\end{Sinput}
+\end{Schunk}
 
@@
 More than linear models, define any response with:
-<<eval=FALSE>>=
-setup %>% sim_resp_eq(y = g(2 * x) + e)
-@
+\begin{Schunk}
+\begin{Sinput}
+> setup %>% sim_resp_eq(y = g(2 * x) + e)
+\end{Sinput}
+\end{Schunk}
 
@@
 
-<<eval=FALSE>>=
-simulationResults <- simSetup %>% sim(R = 500)
-@
+\begin{Schunk}
+\begin{Sinput}
+> simulationResults <- simSetup %>% sim(R = 500)
+\end{Sinput}
+\end{Schunk}
 
@@
 
-<<eval=FALSE>>=
-simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE)
-@
+\begin{Schunk}
+\begin{Sinput}
+> simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE, mc.cores = 8)
+\end{Sinput}
+\end{Schunk}
 

### 2014-10-10 saeSim.Rnw
saeSim paper update

@@
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+\usepackage{wrapfig}
+\usepackage{graphicx}
 
@@
 
+% R CMD Sweave %.Rnw
 % Loading (and installing) necessary packages.
@@
 \section{Introduction}
-A brief overview of what the reader can expect of this article.
-What is the aim of this article and where can it be located in science.
-Discussion of the reproducible research movement and where the package may be beneficial.
-Packages like Sweave, knitr, R-markdown.
-How can simulation studies (the \proglang{R}-code) be published?
-As script?
-As stand-alone-package?
-How can ideas for specific data generation tools be shared amongst the small area community and thus be more transparent: saeSim (far-fetched but anyway).
+Reproducible Research has become a widely discussed topic inside science and also the field of statistics.
+Thanks to the many mostly open-source tools like the \proglang{R}-language and \LaTeX, and also packages like knitr and Sweave, the integration of source code and text is possible and as a problem solved.
+In that sense the demand for Literate Programming can be if wanted incorporated in the work flow of a scientist.
+Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising.
+What this means is, that the source-code and data is published alongside an article.
+However, the requirements in style and clarity of source code are different from the written words in the article itself.
+This demand \textit{human readable source-code} has already been expressed by Knuth (1984):
+\begin{quote}
+\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.}
+\end{quote}
+Small Area Estimation is a growing field inside the field of statistics, where simulation studies play an important role.
+New statistical models are applied in model-based and design-based simulation studies.
+Considering the demands in reproducibility we want to propose a framework for simulation studies.
+This framework addresses three demands.
+First, making tools for data generation available and reusable.
+Second, unify the process behind simulation studies inside the field of Small Area Estimation.
+And third, making source-code of simulation studies available, such that it supports the conducted research in a transparent manner.
+In this article we want to introduce a new package for the \proglang{R}-language addressing these demands.
+We will show the importance of simulation studies in the field.
+Introduce the simulation framework.
+And demonstrate how to use the package to map the simulation as a process to \proglang{R}.
 
-%Graphics should be inserted as PostScript files using the
-%package {\tt psfig} or {\tt graphicx}. Bibliographic references
-%should be given using {\tt bibtex} in the {\em author-date\/}
-%style.
+\section{Small Area Estimation}
+What is small area estimation? 2 Models to introduce. FH + BHF. Why are simulation studies important in the field.
 
-\section{Simulation studies in small area estimation}
-The role of simulation studies in the field.
-Separation into model-based and design-based simulation studies.
-How does \proglang{saeSim} address these 2 perspectives?
-Identifying steps/phases/components of simulation studies (data generation, sampling, computation).
+\section{A simulation framework}
 
-\section{saeSim: A simulation framework}
+%% flow-diagram
+\begin{wrapfigure}{R}{0.5\textwidth}
+\begin{center}
+\includegraphics[width=0.5\textwidth]{flowdiagram}
+\end{center}
+\caption{\label{fig:flowdiagram}Process of simulation.} 
+\end{wrapfigure}
+
+Design- vs. model-based simulation, we do not promote one or the other. 
+Figure \ref{fig:flowdiagram} illustrates the steps in a simulation.
+Based on a data table, which may be a real or synthetic population or a set of ID variables representing the hierarchy of the data, you start a simulation.
+
 Introducing a simulation study as a data manipulation process.
@@
 
+asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+
 <<eval=FALSE>>=
@@
 
-\subsection{Data generation}
-This is not a data generation tool.
-However, it supports some useful functions to add random variates to the data.
-Definition of outliers, see Rao (?) -- how is it addressed in the package.
-More than linear models, define any response with:
-<<eval=FALSE>>=
-setup %>% sim_resp_eq(y = g(2 * x) + e)
-@
-
-\subsection{Drawing samples}
-Is present in unit-level simulation studies.
-Draw with simple random sampling from the whole population or within cluster/domains.
-Specify the sample size as integer or fraction and add weights if necessary.
-Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
-
-\subsection{Adding customized computations}
-Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
-The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
-I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
-
-\subsection{Separation of designing and running simulations}
 First develop a scenario outside any looping structures, then run it R-times:
@@
 
+\section{Data generation}
+This is not a data generation tool.
+However, it supports some useful functions to add random variates to the data.
+Definition of outliers, see Rao (?) -- how is it addressed in the package.
+More than linear models, define any response with:
+<<eval=FALSE>>=
+setup %>% sim_resp_eq(y = g(2 * x) + e)
+@
+
+\section{Adding steps to a simulation}
+Is present in unit-level simulation studies.
+Draw with simple random sampling from the whole population or within cluster/domains.
+Specify the sample size as integer or fraction and add weights if necessary.
+Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
+Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
+The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
+I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
+
+\section{Case study}
+
 \section{Outlook}
@@
 %\bibliographystyle{plainat}
-\bibliography{guidelinesAJS}
+\bibliography{saeSim}
 

### 2014-10-10 saeSim.tex
saeSim paper update

@@
 
+asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+
 \begin{Schunk}
@@
 
-\subsection{Data generation}
-This is not a data generation tool.
-However, it supports some useful functions to add random variates to the data.
-Definition of outliers, see Rao (?) -- how is it addressed in the package.
-More than linear models, define any response with:
-\begin{Schunk}
-\begin{Sinput}
-> setup %>% sim_resp_eq(y = g(2 * x) + e)
-\end{Sinput}
-\end{Schunk}
-
-\subsection{Drawing samples}
-Is present in unit-level simulation studies.
-Draw with simple random sampling from the whole population or within cluster/domains.
-Specify the sample size as integer or fraction and add weights if necessary.
-Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
-
-\subsection{Adding customized computations}
-Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
-The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
-I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
-
-\subsection{Separation of designing and running simulations}
 First develop a scenario outside any looping structures, then run it R-times:
@@
 \begin{Sinput}
-> simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE, mc.cores = 8)
+> simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE)
 \end{Sinput}
 \end{Schunk}
+
+\section{Data generation}
+This is not a data generation tool.
+However, it supports some useful functions to add random variates to the data.
+Definition of outliers, see Rao (?) -- how is it addressed in the package.
+More than linear models, define any response with:
+\begin{Schunk}
+\begin{Sinput}
+> setup %>% sim_resp_eq(y = g(2 * x) + e)
+\end{Sinput}
+\end{Schunk}
+
+\section{Adding steps to a simulation}
+Is present in unit-level simulation studies.
+Draw with simple random sampling from the whole population or within cluster/domains.
+Specify the sample size as integer or fraction and add weights if necessary.
+Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
+Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
+The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
+I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
+
+\section{Case study}
 

### 2014-10-14 saeSim.tex
update saeSim

@@
 \usepackage{graphicx}
+\include{mathOperators}
 
@@
 Reproducible Research has become a widely discussed topic inside science and also the field of statistics.
-Thanks to the many mostly open-source tools like the \proglang{R}-language and \LaTeX, and also packages like knitr and Sweave, the integration of source code and text is possible and as a problem solved.
+Thanks to the many mostly open-source tools like the \proglang{R}-language \cite{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration of source code and text is possible and as a problem solved.
 In that sense the demand for Literate Programming can be if wanted incorporated in the work flow of a scientist.
 Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising.
-What this means is, that the source-code and data is published alongside an article.
+This means, that the source-code and data is published alongside an article.
 However, the requirements in style and clarity of source code are different from the written words in the article itself.
@@
 \begin{quote}
-\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.}
+\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.} \cite[p.99]{knuth92} 
 \end{quote}
@@
 In this article we want to introduce a new package for the \proglang{R}-language addressing these demands.
-We will show the importance of simulation studies in the field.
-Introduce the simulation framework.
-And demonstrate how to use the package to map the simulation as a process to \proglang{R}.
+We will show the importance of simulation studies in the field, introduce the simulation framework and demonstrate how to use the package to map the simulation as a process to \proglang{R}.
 
-\section{Small Area Estimation}
-What is small area estimation? 2 Models to introduce. FH + BHF. Why are simulation studies important in the field.
+\section{Small area estimation}
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+Groups may be areas or other entities, for example defined by socio-economic characteristics.
+The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
+As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
+This can be achieved by using additional information from census data to assist the prediction for non-sampled or domains with little information.
+For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese1988} and the area-level model introduced by \cite{fay79}.
+
+As applications in small area estimations rely often on sensitive information unit-level information is not always available.
+Instead only aggregates, or rather the direct estimators are.
+In such situations area-level models are used.
+The area-level model introduced by \cite{fay79} is build on a sampling model:
+%
+\[\directStat_{\indexDomain} = \trueStat_{\indexDomain} + \samplingError_{\indexDomain},\]
+%
+where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$ with $\indexDomain = 1, \dots, \nDomains$ and $\nDomains$ being the total number of areas.
+The sampling error $\samplingError_{\indexDomain}$ is assumed to be independent and normally distributed with known variances $\samplingVarianceIndexed$, i.e.
+$\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$.
+The model is modified with the linking model by assuming a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
+%
+\[\trueStat_{\indexDomain} = \xArea^\top \beta + \randomEffectIndexed,\] 
+%
+with $\indexDomain=1,\dots, \nDomains$.
+Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship.
+The model errors $\randomEffectIndexed$ are assumed to be independent and normally distributed, i.e.
+$\randomEffectIndexed \sim \mathit{N}(0, \randomEffectVariance)$.
+Furthermore $\samplingErrorIndexed$ and $\randomEffectIndexed$ are assumed to be independent.
+Combining the sampling and linking model leads to:
+\begin{equation}
+\label{eq:FH}
+\directStatIndexed = \xArea^\top \beta + \randomEffectIndexed + \samplingErrorIndexed.
+\end{equation} 
+%
+Model \ref{eq:FH} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
 
@@
 
+asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+
+asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+
+asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+
 \begin{Schunk}
@@
 
-\section{Data generation}
-This is not a data generation tool.
-However, it supports some useful functions to add random variates to the data.
-Definition of outliers, see Rao (?) -- how is it addressed in the package.
-More than linear models, define any response with:
-\begin{Schunk}
-\begin{Sinput}
-> setup %>% sim_resp_eq(y = g(2 * x) + e)
-\end{Sinput}
-\end{Schunk}
-
-\section{Adding steps to a simulation}
-Is present in unit-level simulation studies.
-Draw with simple random sampling from the whole population or within cluster/domains.
-Specify the sample size as integer or fraction and add weights if necessary.
-Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
-Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
-The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
-I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
-
 \section{Case study}

### 2014-10-16 saeSim.Rnw
update saeSim

@@
 \begin{document}
-
+%
 %% include your article here, just as usual
-
+%
 % R CMD Sweave %.Rnw
@@
 @
-
+%
 \section{Introduction}
@@
 
-\section{Small Area Estimation}
-What is small area estimation? 2 Models to introduce. FH + BHF. Why are simulation studies important in the field.
-
 \section{A simulation framework}
-
+%
 %% flow-diagram
@@
 \end{wrapfigure}
+%
+In our opinion simulation studies can best be summarised when understood as a process of data manipulation.
+Thus the main focus of \proglang{saeSim} is to define the steps in that process which can then be \textit{cleanly} defined and repeated.
+Before we go into any detail of the functionality of the package we will discuss the process behind simulation studies and later how \proglang{saeSim} maps this process into \proglang{R}.
 
-Design- vs. model-based simulation, we do not promote one or the other. 
-Figure \ref{fig:flowdiagram} illustrates the steps in a simulation.
-Based on a data table, which may be a real or synthetic population or a set of ID variables representing the hierarchy of the data, you start a simulation.
+Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level, as illustrated in figure \ref{fig:flowdiagram}.
+The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model.
+We see three different point of views to define a population.
+First \textit{design-based}, which means that a simulation study is based on true or synthetic data of \textit{one} population.
+Second a \textit{semi-model-based} point of view, where only one population is drawn from a model and is fixed in the whole simulation study.
+And third, \textit{model-based} studies which have changing random populations drawn from a model.
 
-Introducing a simulation study as a data manipulation process.
-From data generation to estimating models.
-How can this process be mapped into the \proglang{R}-language.
-Present the simulation phases as flow-diagram and map the function names to the problem domain.
-Defining interfaces between phases: \proglang{data.frame} in, \proglang{data.frame} out.
-What is the difference between a design-based (fixed-population) and model-based (random-population) approach.
+The scope of this article is not not to promote any of those viewpoints, but simply to identify the similarity in them.
+The \textit{base} (first component in figure \ref{fig:flowdiagram}) of any simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over the course of the simulation.
+Or from a more technical point of view, is the data generation (the second step in figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted?
 
-Why is this package helping in terms of literate programming (code is written for humans not machines) and reproducible research?
-Package naming conventions.
-Use the \proglang{\%>\%} operator to compose simulation set-ups.
-Reuse defined scenarios to compose new scenarios: What is a contamination scenario?
-A standard scenario plus contamination:
+Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in figure \ref{fig:flowdiagram}).
 
-asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+The \textbf{sample-level} is when domain predictions are conducted for unit-level models.
+Independently of how the population is treated, fixed or random, this phase consists of two steps, first drawing a sample, and second conducting computations on the samples (fourth and fifth component in figure \ref{fig:flowdiagram}).
+Given a sample, design or model based small area methods are applied.
+Of interest are estimated parameters, which can be estimated model parameters or domain predictions as well as measures of uncertainty for the estimates.
 
-<<eval=FALSE>>=
-contaminatedSetup <- standardSetup %>% sim_gen_cont()
+As the sample-level is when unit-level models are applied, the \textbf{aggregate-level} is when area-level models are applied (the seventh and last component in figure \ref{fig:flowdiagram}).
+Area-level models in small area estimation typically only use information available for domains (in contrast to units).
+Thus, the question for simulation studies for area-level methods is, if the data is generated on unit-level and used after the aggregation (sixth component in figure \ref{fig:flowdiagram}) or if the data is generated directly on area-level, i.e.
+drawn from an area-level model.
+Depending on whether unit-level data and sampling are part of the simulation the aggregate-level follows the generation of the population or is based on the aggregated sample.
+Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.
+
+Depending on the topic of research steps in this simulation framework can be more relevant than others or completely irrelevant.
+We see these steps more as a complete list of phases one can encounter, thus single components can be omitted if not relevant in specific applications.
+For example \textit{data generation} is not relevant if you have population data, or the \textit{sample-level} is not used, when the sample is directly drawn from the model.
+
+From this considerations, \proglang{saeSim} maps the different steps into \proglang{R}.
+Two layers with separate responsibilities need to be discussed.
+The first is \textit{how} different simulation components can be combined, and the second \textit{when} or in which order they are applied.
+Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component, which is to use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value.
+This is a widely used approach for data manipulation and promoted recently in the package \proglang{dplyr} \citep{wickham14}.
+This definition of interfaces, the return value of one component is the input of the next, is also used in \proglang{saeSim}.
+
+Understanding a simulation as a process of manipulating one data object, see the second column in figure \ref{fig:flowdiagram} how the different steps in a simulation can be accessed.
+It is important to note that the functions in figure \ref{fig:flowdiagram} control the process, the second layer, i.e.
+\textit{when} components are applied.
+Each of these functions take a simulation setup object to be modified and a function with the discussed interface as arguments.
+Hence a simulation setup is a collection of functions to be applied in a certain sequence.
+As the first-layer functions, also have a defined interface: a \proglang{sim\_setup} as input to be modified and a \proglang{sim\_setup} as output.
+Thus, components can be chained together using the \textit{pipe operator} (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14}.
+
+Braking the responsibility into what is applied and when it is applied addresses several aspects of reproducibility.
+First, by defining the interface between all components, it is easy to combine them in any combination and thus easy to share and reuse.
+Second, by controlling when components are applied we avoid the necessity of control structures in syntax and emphasise on the definition of components.
+The following example shows these aspects of the package using a predefined simulation setup:
+
+<<>>=
+setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
+setup2 <- sim_base_lm() %>% sim_sample(sample_fraction(0.05))
 @
 
-First develop a scenario outside any looping structures, then run it R-times:
+Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we can see that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme.
+\proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
+The pipe operator \proglang{\%>\%} is used to add new components to the setup.
+As said before the composition of a simulation in that manner will focus on the definition of components and hide control structures.
+The next example will repeat the simulation stored in \proglang{setup1} two times.
+The results are returned in a list of \proglang{data.frame}s which have five rows as we sample 5 observations:
 
-<<eval=FALSE>>=
-simulationResults <- simSetup %>% sim(R = 500)
+<<>>=
+setup1 %>% sim(R = 2) %>% sapply(nrow)
 @
 
-There is an easy back-end to run simulations in parallel (in Windows with special care):
-
-<<eval=FALSE>>=
-simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE)
-@
-
-\section{Data generation}
-This is not a data generation tool.
-However, it supports some useful functions to add random variates to the data.
-Definition of outliers, see Rao (?) -- how is it addressed in the package.
-More than linear models, define any response with:
-<<eval=FALSE>>=
-setup %>% sim_resp_eq(y = g(2 * x) + e)
-@
-
-\section{Adding steps to a simulation}
-Is present in unit-level simulation studies.
-Draw with simple random sampling from the whole population or within cluster/domains.
-Specify the sample size as integer or fraction and add weights if necessary.
-Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
-Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
-The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
-I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
+With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
+We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as designed a platform to make them accessible.
+By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
+In the next section we will present a case study and focus more on the concrete functionality provided by the package.
 

### 2014-10-16 saeSim.tex
update saeSim

--- 2014-10-10 saeSim.tex
@@
 \begin{document}
-
+%
 %% include your article here, just as usual
-
+%
 % R CMD Sweave %.Rnw
 % Loading (and installing) necessary packages.
-
+%
 \section{Introduction}
@@
 \end{wrapfigure}
+%
+In our opinion simulation studies can best be summarised when understood as a process of data manipulation.
+Thus the main focus of \proglang{saeSim} is to define the steps in that process which can then be \textit{cleanly} defined and repeated.
+Before we go into any detail of the functionality of the package we will discuss the process behind simulation studies and later how \proglang{saeSim} maps this process into \proglang{R}.
 
-Design- vs. model-based simulation, we do not promote one or the other. 
-Figure \ref{fig:flowdiagram} illustrates the steps in a simulation.
-Based on a data table, which may be a real or synthetic population or a set of ID variables representing the hierarchy of the data, you start a simulation.
+Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level, as illustrated in figure \ref{fig:flowdiagram}.
+The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model.
+We see three different point of views to define a population.
+First \textit{design-based}, which means that a simulation study is based on true or synthetic data of \textit{one} population.
+Second a \textit{semi-model-based} point of view, where only one population is drawn from a model and is fixed in the whole simulation study.
+And third, \textit{model-based} studies which have changing random populations drawn from a model.
 
-Introducing a simulation study as a data manipulation process.
-From data generation to estimating models.
-How can this process be mapped into the \proglang{R}-language.
-Present the simulation phases as flow-diagram and map the function names to the problem domain.
-Defining interfaces between phases: \proglang{data.frame} in, \proglang{data.frame} out.
-What is the difference between a design-based (fixed-population) and model-based (random-population) approach.
+The scope of this article is not not to promote any of those viewpoints, but simply to identify the similarity in them.
+The \textit{base} (first component in figure \ref{fig:flowdiagram}) of any simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over the course of the simulation.
+Or from a more technical point of view, is the data generation (the second step in figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted?
 
-Why is this package helping in terms of literate programming (code is written for humans not machines) and reproducible research?
-Package naming conventions.
-Use the \proglang{\%>\%} operator to compose simulation set-ups.
-Reuse defined scenarios to compose new scenarios: What is a contamination scenario?
-A standard scenario plus contamination:
+Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in figure \ref{fig:flowdiagram}).
 
-asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd asd
+The \textbf{sample-level} is when domain predictions are conducted for unit-level models.
+Independently of how the population is treated, fixed or random, this phase consists of two steps, first drawing a sample, and second conducting computations on the samples (fourth and fifth component in figure \ref{fig:flowdiagram}).
+Given a sample, design or model based small area methods are applied.
+Of interest are estimated parameters, which can be estimated model parameters or domain predictions as well as measures of uncertainty for the estimates.
+
+As the sample-level is when unit-level models are applied, the \textbf{aggregate-level} is when area-level models are applied (the seventh and last component in figure \ref{fig:flowdiagram}).
+Area-level models in small area estimation typically only use information available for domains (in contrast to units).
+Thus, the question for simulation studies for area-level methods is, if the data is generated on unit-level and used after the aggregation (sixth component in figure \ref{fig:flowdiagram}) or if the data is generated directly on area-level, i.e.
+drawn from an area-level model.
+Depending on whether unit-level data and sampling are part of the simulation the aggregate-level follows the generation of the population or is based on the aggregated sample.
+Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.
+
+Depending on the topic of research steps in this simulation framework can be more relevant than others or completely irrelevant.
+We see these steps more as a complete list of phases one can encounter, thus single components can be omitted if not relevant in specific applications.
+For example \textit{data generation} is not relevant if you have population data, or the \textit{sample-level} is not used, when the sample is directly drawn from the model.
+
+From this considerations, \proglang{saeSim} maps the different steps into \proglang{R}.
+Two layers with separate responsibilities need to be discussed.
+The first is \textit{how} different simulation components can be combined, and the second \textit{when} or in which order they are applied.
+Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component, which is to use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value.
+This is a widely used approach for data manipulation and promoted recently in the package \proglang{dplyr} \citep{wickham14}.
+This definition of interfaces, the return value of one component is the input of the next, is also used in \proglang{saeSim}.
+
+Understanding a simulation as a process of manipulating one data object, see the second column in figure \ref{fig:flowdiagram} how the different steps in a simulation can be accessed.
+It is important to note that the functions in figure \ref{fig:flowdiagram} control the process, the second layer, i.e.
+\textit{when} components are applied.
+Each of these functions take a simulation setup object to be modified and a function with the discussed interface as arguments.
+Hence a simulation setup is a collection of functions to be applied in a certain sequence.
+As the first-layer functions, also have a defined interface: a \proglang{sim\_setup} as input to be modified and a \proglang{sim\_setup} as output.
+Thus, components can be chained together using the \textit{pipe operator} (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14}.
+
+Braking the responsibility into what is applied and when it is applied addresses several aspects of reproducibility.
+First, by defining the interface between all components, it is easy to combine them in any combination and thus easy to share and reuse.
+Second, by controlling when components are applied we avoid the necessity of control structures in syntax and emphasise on the definition of components.
+The following example shows these aspects of the package using a predefined simulation setup:
 
@@
 \begin{Sinput}
-> contaminatedSetup <- standardSetup %>% sim_gen_cont()
+> setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
+> setup2 <- sim_base_lm() %>% sim_sample(sample_fraction(0.05))
 \end{Sinput}
@@
 
-First develop a scenario outside any looping structures, then run it R-times:
+Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we can see that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme.
+\proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
+The pipe operator \proglang{\%>\%} is used to add new components to the setup.
+As said before the composition of a simulation in that manner will focus on the definition of components and hide control structures.
+The next example will repeat the simulation stored in \proglang{setup1} two times.
+The results are returned in a list of \proglang{data.frame}s which have five rows as we sample 5 observations:
 
@@
 \begin{Sinput}
-> simulationResults <- simSetup %>% sim(R = 500)
+> setup1 %>% sim(R = 2) %>% sapply(nrow)
 \end{Sinput}
+\begin{Soutput}
+[1] 5 5
+\end{Soutput}
 \end{Schunk}
 
-There is an easy back-end to run simulations in parallel (in Windows with special care):
-
-\begin{Schunk}
-\begin{Sinput}
-> simulationResults <- simSetup %>% sim(R = 500, parallel = TRUE)
-\end{Sinput}
-\end{Schunk}
-
-\section{Data generation}
-This is not a data generation tool.
-However, it supports some useful functions to add random variates to the data.
-Definition of outliers, see Rao (?) -- how is it addressed in the package.
-More than linear models, define any response with:
-\begin{Schunk}
-\begin{Sinput}
-> setup %>% sim_resp_eq(y = g(2 * x) + e)
-\end{Sinput}
-\end{Schunk}
-
-\section{Adding steps to a simulation}
-Is present in unit-level simulation studies.
-Draw with simple random sampling from the whole population or within cluster/domains.
-Specify the sample size as integer or fraction and add weights if necessary.
-Wrappers around \proglang{dplyr::sample\_n} and \proglang{dplyr::sample\_frac}.
-Adding user specified functions to the simulation process is what separates this package from a mere data generation tool.
-The interface is simple: Add functions with one argument which is the data at that moment and which return the modified data.
-I am not sure if this and the sampling section is necessary -- maybe it should just be summarized in the overview section...
+With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
+We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as designed a platform to make them accessible.
+By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
+In the next section we will present a case study and focus more on the concrete functionality provided by the package.
 

### 2014-10-17 saeSim.Rnw

@@
 
+%% additional packages
 \usepackage{wrapfig}
 \usepackage{graphicx}
+
+%% definitions of entities in formulae
+\include{mathOperators}
 
@@
 \section{Introduction}
-Reproducible Research has become a widely discussed topic inside science and also the field of statistics.
-Thanks to the many mostly open-source tools like the \proglang{R}-language and \LaTeX, and also packages like knitr and Sweave, the integration of source code and text is possible and as a problem solved.
-In that sense the demand for Literate Programming can be if wanted incorporated in the work flow of a scientist.
-Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising.
-What this means is, that the source-code and data is published alongside an article.
-However, the requirements in style and clarity of source code are different from the written words in the article itself.
-This demand \textit{human readable source-code} has already been expressed by Knuth (1984):
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+Groups may be areas or other entities, for example defined by socio-economic characteristics.
+New statistical methods are applied in model-based and design-based simulation studies.
+Considering the demands for reproducible research we propose a framework for simulation studies inside the field of small area estimation.
+
+Reproducible Research has become a widely discussed topic in general and also the field of statistics.
+Thanks to the many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration of text and source code for statistical analysis is possible.
+Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising which is supported by the rising number of Open Access Journals.
+Publishing source-code and data alongside an article draws special attention to authoring an analysis.
+However, the requirements for source code are different from the written words in the article itself.
+
 \begin{quote}
-\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.}
+\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.} \cite[p.99]{knuth92} 
 \end{quote}
-Small Area Estimation is a growing field inside the field of statistics, where simulation studies play an important role.
-New statistical models are applied in model-based and design-based simulation studies.
-Considering the demands in reproducibility we want to propose a framework for simulation studies.
-This framework addresses three demands.
+
+In this article we want to introduce a new package for the \proglang{R}-language to support the process of making simulation studies reproducible as well as supporting a \textit{human-readable} interface.
+Three points in specific.
 First, making tools for data generation available and reusable.
@@
 And third, making source-code of simulation studies available, such that it supports the conducted research in a transparent manner.
-In this article we want to introduce a new package for the \proglang{R}-language addressing these demands.
-We will show the importance of simulation studies in the field.
-Introduce the simulation framework.
-And demonstrate how to use the package to map the simulation as a process to \proglang{R}.
+
+In section \ref{sec:SAE} we will give a short introduction into small area estimation and the role of simulation studies. Section \ref{sec:framework}
+
+\section{\label{sec:SAE} Small area estimation}
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+Groups may be areas or other entities, for example defined by socio-economic characteristics.
+The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
+As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
+This can be achieved by using additional information from census data to assist the prediction for non-sampled or domains with little information.
+For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese1988} and the area-level model introduced by \cite{fay79}.
+
+As applications in small area estimations rely often on sensitive information unit-level information is not always available.
+Instead only aggregates, or rather the direct estimators are.
+In such situations area-level models are used.
+The area-level model introduced by \cite{fay79} is build on a sampling model:
+%
+\[\directStat_{\indexDomain} = \trueStat_{\indexDomain} + \samplingError_{\indexDomain},\]
+%
+where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$ with $\indexDomain = 1, \dots, \nDomains$ and $\nDomains$ being the total number of areas.
+The sampling error $\samplingError_{\indexDomain}$ is assumed to be independent and normally distributed with known variances $\samplingVarianceIndexed$, i.e.
+$\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$.
+The model is modified with the linking model by assuming a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
+%
+\[\trueStat_{\indexDomain} = \xArea^\top \beta + \randomEffectIndexed,\] 
+%
+with $\indexDomain=1,\dots, \nDomains$.
+Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship.
+The model errors $\randomEffectIndexed$ are assumed to be independent and normally distributed, i.e.
+$\randomEffectIndexed \sim \mathit{N}(0, \randomEffectVariance)$.
+Furthermore $\samplingErrorIndexed$ and $\randomEffectIndexed$ are assumed to be independent.
+Combining the sampling and linking model leads to:
+\begin{equation}
+\label{eq:FH}
+\directStatIndexed = \xArea^\top \beta + \randomEffectIndexed + \samplingErrorIndexed.
+\end{equation} 
+%
+Model \ref{eq:FH} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
 

### 2014-10-17 saeSim.tex

@@
 \section{Introduction}
-Reproducible Research has become a widely discussed topic inside science and also the field of statistics.
-Thanks to the many mostly open-source tools like the \proglang{R}-language and \LaTeX, and also packages like knitr and Sweave, the integration of source code and text is possible and as a problem solved.
-In that sense the demand for Literate Programming can be if wanted incorporated in the work flow of a scientist.
+Reproducible Research has become a widely discussed topic in general and also the field of statistics.
+Thanks to the many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration text and source code for statistical analysis is possible.
 Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising.
-What this means is, that the source-code and data is published alongside an article.
+Publishing source-code and data alongside an article draws special attention to authoring an analysis.
 However, the requirements in style and clarity of source code are different from the written words in the article itself.
-This demand \textit{human readable source-code} has already been expressed by Knuth (1984):
+
 \begin{quote}
-\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.}
+\textit{Instead of imagining that our main task is to instruct a computer what to do, let us concentrate rather on explaining to human beings what we want a computer to do.} \cite[p.99]{knuth92} 
 \end{quote}
+
 Small Area Estimation is a growing field inside the field of statistics, where simulation studies play an important role.
@@
 And third, making source-code of simulation studies available, such that it supports the conducted research in a transparent manner.
+
 In this article we want to introduce a new package for the \proglang{R}-language addressing these demands.
-We will show the importance of simulation studies in the field.
-Introduce the simulation framework.
-And demonstrate how to use the package to map the simulation as a process to \proglang{R}.
+We will show the importance of simulation studies in the field, introduce the simulation framework and demonstrate how to use the package to map the simulation as a process to \proglang{R}.
+
+\section{Small area estimation}
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+Groups may be areas or other entities, for example defined by socio-economic characteristics.
+The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
+As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
+This can be achieved by using additional information from census data to assist the prediction for non-sampled or domains with little information.
+For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese1988} and the area-level model introduced by \cite{fay79}.
+
+As applications in small area estimations rely often on sensitive information unit-level information is not always available.
+Instead only aggregates, or rather the direct estimators are.
+In such situations area-level models are used.
+The area-level model introduced by \cite{fay79} is build on a sampling model:
+%
+\[\directStat_{\indexDomain} = \trueStat_{\indexDomain} + \samplingError_{\indexDomain},\]
+%
+where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$ with $\indexDomain = 1, \dots, \nDomains$ and $\nDomains$ being the total number of areas.
+The sampling error $\samplingError_{\indexDomain}$ is assumed to be independent and normally distributed with known variances $\samplingVarianceIndexed$, i.e.
+$\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$.
+The model is modified with the linking model by assuming a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
+%
+\[\trueStat_{\indexDomain} = \xArea^\top \beta + \randomEffectIndexed,\] 
+%
+with $\indexDomain=1,\dots, \nDomains$.
+Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship.
+The model errors $\randomEffectIndexed$ are assumed to be independent and normally distributed, i.e.
+$\randomEffectIndexed \sim \mathit{N}(0, \randomEffectVariance)$.
+Furthermore $\samplingErrorIndexed$ and $\randomEffectIndexed$ are assumed to be independent.
+Combining the sampling and linking model leads to:
+\begin{equation}
+\label{eq:FH}
+\directStatIndexed = \xArea^\top \beta + \randomEffectIndexed + \samplingErrorIndexed.
+\end{equation} 
+%
+Model \ref{eq:FH} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
 

### 2014-10-19 saeSim.Rnw
update paper saeSim

@@
 
-Reproducible Research has become a widely discussed topic in general and also the field of statistics.
+Reproducible Research has become a widely discussed topic in general and also in the field of statistics.
 Thanks to the many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration of text and source code for statistical analysis is possible.
@@
 In this article we want to introduce a new package for the \proglang{R}-language to support the process of making simulation studies reproducible as well as supporting a \textit{human-readable} interface.
-Three points in specific.
-First, making tools for data generation available and reusable.
+With this package we have three objectives in specific: First, making tools for data generation available and reusable.
 Second, unify the process behind simulation studies inside the field of Small Area Estimation.
@@
 
-In section \ref{sec:SAE} we will give a short introduction into small area estimation and the role of simulation studies. Section \ref{sec:framework}
+In section \ref{sec:SAE} we will give a short introduction to small area estimation and the role of simulation studies within that field.
+Section \ref{sec:framework} will then introduce a framework for simulation studies and how it is supported by \proglang{saeSim}.
+To illustrate some of the package's features we present a case study in section \ref{sec:caseStudy}.
 
-\section{\label{sec:SAE} Small area estimation}
+\section{Small area estimation}
+\label{sec:SAE}
 The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
@@
 As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
-This can be achieved by using additional information from census data to assist the prediction for non-sampled or domains with little information.
+This can be achieved by using additional information from census data to assist the prediction for non-sampled domains or domains with little information.
 For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese1988} and the area-level model introduced by \cite{fay79}.
 
-As applications in small area estimations rely often on sensitive information unit-level information is not always available.
-Instead only aggregates, or rather the direct estimators are.
-In such situations area-level models are used.
+Due to reasons of confidentiality unit-level information is not always available.
+Instead only aggregates, or rather the direct estimators may be supplied.
+However, these direct estimations are known to be unreliable, hence in such situations area-level models can be valuable.
 The area-level model introduced by \cite{fay79} is build on a sampling model:
@@
 \section{A simulation framework}
+\label{sec:framework}
 %
@@
 \section{Case study}
+\label{sec:caseStudy}
 

### 2014-10-20 saeSim.Rnw
raw case study

@@
 This can be achieved by using additional information from census data to assist the prediction for non-sampled domains or domains with little information.
-For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese1988} and the area-level model introduced by \cite{fay79}.
+For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese88} and the area-level model introduced by \cite{fay79}.
+
+The unit level model \citep{battese88} can be expressed as:
+\begin{eqnarray}
+	 y_{\indexDomain\indexUnit} =& \xUnit^\top\beta + \randomEffectIndexed + \samplingErrorUnitIndexed \nonumber \\
+	\randomEffectIndexed \stackrel{iid}{\sim}& N(0, \randomEffectVariance)  \nonumber \\
+	\samplingErrorUnitIndexed \stackrel{iid}{\sim}& N(0, \samplingVariance) \nonumber
+\end{eqnarray}
+
+where $\indexDomain = 1, \dots, \nDomains$ and $\indexUnit = 1, \dots, \nUnitIndexed$.
+$y_{\indexDomain\indexUnit}$ is the the dependent variable for domain $\indexDomain$ and unit $\indexUnit$, and $\xUnit$ the corresponding auxiliary information for that unit.
+Furthermore $\randomEffect$ and $\samplingError$ are independent.
+This model can be seen as a linear mixed model from which the best linear unbiased predictor (BLUP) can be derived and is used for the domain prediction \citep{rao03}.
 
@@
 With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
-We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as designed a platform to make them accessible.
+We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as a platform to make them accessible.
 By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
@@
 \label{sec:caseStudy}
+\subsection{Model-based simulation}
+<<>>=
+suppressPackageStartupMessages(library(saeSim))
+suppressPackageStartupMessages(library(sae))
+suppressPackageStartupMessages(library(dplyr))
+suppressPackageStartupMessages(library(reshape2))
+suppressPackageStartupMessages(library(ggplot2))
+
+set.seed(1) # for reproduction of the results
+@
+
+<<>>=
+comp_FH <- function(dat) {
+  # Computes the EBLUP under a Fay-Herriot model
+  modelFH <- eblupFH(y ~ x, vardir, data = dat, method = "FH")
+  dat$FH <- modelFH$eblup
+  dat
+}
+@
+
+<<>>=
+simResults <- base_id(nDomains = 40, nUnits = 1) %>% 
+  sim_gen_fe() %>%
+  sim_gen_re() %>% 
+  sim_gen(comp_var(vardir = seq(0.1, 4, length.out = 40))) %>%
+  sim_gen(comp_var(e = rnorm(nrow(dat), sd = sqrt(vardir)))) %>%
+  sim_resp_eq(y = 100 + 2 * x + v + e) %>%
+  sim_comp_agg(comp_var(trueStat = y - e)) %>%
+  sim_comp_agg(comp_FH) %>%
+  sim(R = 500) %>%
+  rbind_all
+@
+
+<<>>=
+ggDat <- simResults %>% 
+  melt(id.vars = c("idD", "trueStat"), 
+       measure.vars = c("FH", "y"), 
+       variable.name = "method",
+       value.name = "prediction") %>% 
+  mutate(RBIAS = (prediction - trueStat)/trueStat,
+         RRMSE = (prediction - trueStat)^2/trueStat) %>%
+  group_by(idD, method) %>% 
+  summarise(RBIAS = mean(RBIAS),
+            RMSE = mean(RRMSE)) %>%
+  as.data.frame
+
+head(ggDat)
+@
+
+<<modelSimBIAS, fig=TRUE, width = 8, height=4, include=FALSE>>=
+ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
+@
+
+\includegraphics[width = \textwidth]{saeSim-modelSimBIAS.pdf}
+
+<<modelSimRMSE, fig=TRUE, width = 8, height=4, include=FALSE>>=
+ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
+@
+
+\includegraphics[width = \textwidth]{saeSim-modelSimRMSE.pdf}
+
+\subsection{Design-based simulation}
+<<>>=
+data(eusilcP, package = "simFrame")
+
+simDat <- eusilcP %>% 
+  mutate(agesq = age^2, eqIncome = as.numeric(eqIncome)) %>%
+  filter(main) %>%
+  select(region, eqIncome, age, agesq, gender) %>%
+  base_add_id(c("region"))
+
+attr(simDat, "popMeans") <- 
+  simDat %>% 
+  group_by(idD, region) %>%
+  summarise(age = mean(age),
+            agesq = mean(agesq),
+            genderFemale = mean(as.integer(gender) - 1),
+            trueStat = mean(eqIncome))
+
+attr(simDat, "popN") <- 
+  simDat %>%
+  group_by(idD) %>%
+  summarise(N = n())
+
+attr(simDat, "popN")
+attr(simDat, "popMeans")
+
+@
+
+<<>>=
+comp_BHF <- function(dat) {
+  popMeans <- attr(dat, "popMeans") %>% select(-trueStat, -region)
+  modelBHF <- 
+    eblupBHF(eqIncome ~ age + agesq + gender, idD, meanxpop = popMeans,
+             popnsize = attr(dat, "popN"), data = dat)
+  attr(dat, "BHF") <- modelBHF$eblup
+  dat
+}
+
+comp_direct <- function(dat) {
+  attr(dat, "sampleMean") <- 
+    dat %>% group_by(idD) %>% summarise(y = mean(eqIncome))
+  dat  
+}
+
+agg_results <- function(dat) {
+  cbind(attr(dat, "popMeans") %>% select(idD, region, trueStat), 
+        BHF = attr(dat, "BHF")$eblup,
+        y = attr(dat, "sampleMean")$y)
+}
+@
+
+<<>>=
+simResults <- simDat %>% 
+  sim_sample(sample_fraction(0.1, groupVars = "idD")) %>%
+  sim_comp_sample(comp_BHF) %>%
+  sim_comp_sample(comp_direct) %>%
+  sim_agg(agg_results) %>%
+  sim(R = 50) %>%
+  rbind_all
+
+ggDat <- simResults %>% 
+  melt(id.vars = c("idD", "region", "trueStat"), 
+       measure.vars = c("BHF", "y"), 
+       variable.name = "method",
+       value.name = "prediction")
+@
+
+<<designSimBIAS, fig=TRUE, width = 8.3, height=4, include=FALSE>>=
+ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
+  geom_boxplot() + theme(legend.position = "bottom")
+@
+
+\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+
+<<designSimMSE, fig=TRUE, width = 8.3, height=4, include=FALSE>>=
+ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
+  geom_boxplot() + scale_y_log10() + theme(legend.position = "bottom")
+@
+
+\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
 
@@
 Contribute to the package and make your whole simulation study available.
+\begin{itemize}
+	\item Link to simFrame
+	\item Package Features
+	\begin{itemize}
+		\item outliers
+		\item sampling
+		\item non-linear models
+	\end{itemize}
+	\item How to contribute?
+	\item parallel computations
+\end{itemize}
 

### 2014-10-20 saeSim.tex
raw case study

@@
 \section{Introduction}
-Reproducible Research has become a widely discussed topic in general and also the field of statistics.
-Thanks to the many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration text and source code for statistical analysis is possible.
-Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising.
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+Groups may be areas or other entities, for example defined by socio-economic characteristics.
+New statistical methods are applied in model-based and design-based simulation studies.
+Considering the demands for reproducible research we propose a framework for simulation studies inside the field of small area estimation.
+
+Reproducible Research has become a widely discussed topic in general and also in the field of statistics.
+Thanks to the many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration of text and source code for statistical analysis is possible.
+Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising which is supported by the rising number of Open Access Journals.
 Publishing source-code and data alongside an article draws special attention to authoring an analysis.
-However, the requirements in style and clarity of source code are different from the written words in the article itself.
+However, the requirements for source code are different from the written words in the article itself.
 
@@
 
-Small Area Estimation is a growing field inside the field of statistics, where simulation studies play an important role.
-New statistical models are applied in model-based and design-based simulation studies.
-Considering the demands in reproducibility we want to propose a framework for simulation studies.
-This framework addresses three demands.
-First, making tools for data generation available and reusable.
+In this article we want to introduce a new package for the \proglang{R}-language to support the process of making simulation studies reproducible as well as supporting a \textit{human-readable} interface.
+With this package we have three objectives in specific: First, making tools for data generation available and reusable.
 Second, unify the process behind simulation studies inside the field of Small Area Estimation.
@@
 
-In this article we want to introduce a new package for the \proglang{R}-language addressing these demands.
-We will show the importance of simulation studies in the field, introduce the simulation framework and demonstrate how to use the package to map the simulation as a process to \proglang{R}.
+In section \ref{sec:SAE} we will give a short introduction to small area estimation and the role of simulation studies within that field.
+Section \ref{sec:framework} will then introduce a framework for simulation studies and how it is supported by \proglang{saeSim}.
+To illustrate some of the package's features we present a case study in section \ref{sec:caseStudy}.
 
 \section{Small area estimation}
+\label{sec:SAE}
 The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
@@
 As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
-This can be achieved by using additional information from census data to assist the prediction for non-sampled or domains with little information.
-For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese1988} and the area-level model introduced by \cite{fay79}.
+This can be achieved by using additional information from census data to assist the prediction for non-sampled domains or domains with little information.
+For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese88} and the area-level model introduced by \cite{fay79}.
 
-As applications in small area estimations rely often on sensitive information unit-level information is not always available.
-Instead only aggregates, or rather the direct estimators are.
-In such situations area-level models are used.
+The unit level model \citep{battese88} can be expressed as:
+\begin{eqnarray}
+	 y_{\indexDomain\indexUnit} =& \xUnit^\top\beta + \randomEffectIndexed + \samplingErrorUnitIndexed \nonumber \\
+	\randomEffectIndexed \stackrel{iid}{\sim}& N(0, \randomEffectVariance)  \nonumber \\
+	\samplingErrorUnitIndexed \stackrel{iid}{\sim}& N(0, \samplingVariance) \nonumber
+\end{eqnarray}
+
+where $\indexDomain = 1, \dots, \nDomains$ and $\indexUnit = 1, \dots, \nUnitIndexed$.
+$y_{\indexDomain\indexUnit}$ is the the dependent variable for domain $\indexDomain$ and unit $\indexUnit$, and $\xUnit$ the corresponding auxiliary information for that unit.
+Furthermore $\randomEffect$ and $\samplingError$ are independent.
+This model can be seen as a linear mixed model from which the best linear unbiased predictor (BLUP) can be derived and is used for the domain prediction \citep{rao03}.
+
+Due to reasons of confidentiality unit-level information is not always available.
+Instead only aggregates, or rather the direct estimators may be supplied.
+However, these direct estimations are known to be unreliable, hence in such situations area-level models can be valuable.
 The area-level model introduced by \cite{fay79} is build on a sampling model:
@@
 \section{Case study}
+\label{sec:caseStudy}
+\subsection{Model-based simulation}
+\begin{Schunk}
+\begin{Sinput}
+> suppressPackageStartupMessages(library(saeSim))
+> suppressPackageStartupMessages(library(sae))
+> suppressPackageStartupMessages(library(dplyr))
+> suppressPackageStartupMessages(library(reshape2))
+> suppressPackageStartupMessages(library(ggplot2))
+> set.seed(1) # for reproduction of the results
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> comp_FH <- function(dat) {
++   # Computes the EBLUP under a Fay-Herriot model
++   modelFH <- eblupFH(y ~ x, vardir, data = dat, method = "FH")
++   dat$FH <- modelFH$eblup
++   dat
++ }
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> simResults <- base_id(nDomains = 40, nUnits = 1) %>% 
++   sim_gen_fe() %>%
++   sim_gen_re() %>% 
++   sim_gen(comp_var(vardir = seq(0.1, 4, length.out = 40))) %>%
++   sim_gen(comp_var(e = rnorm(nrow(dat), sd = sqrt(vardir)))) %>%
++   sim_resp_eq(y = 100 + 2 * x + v + e) %>%
++   sim_comp_agg(comp_var(trueStat = y - e)) %>%
++   sim_comp_agg(comp_FH) %>%
++   sim(R = 500) %>%
++   rbind_all
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> ggDat <- simResults %>% 
++   melt(id.vars = c("idD", "trueStat"), 
++        measure.vars = c("FH", "y"), 
++        variable.name = "method",
++        value.name = "prediction") %>% 
++   mutate(RBIAS = (prediction - trueStat)/trueStat,
++          RRMSE = (prediction - trueStat)^2/trueStat) %>%
++   group_by(idD, method) %>% 
++   summarise(RBIAS = mean(RBIAS),
++             RMSE = mean(RRMSE)) %>%
++   as.data.frame
+> head(ggDat)
+\end{Sinput}
+\begin{Soutput}
+  idD method         RBIAS         RMSE
+1   1     FH -0.0001326439 0.0009412468
+2   1      y -0.0001285281 0.0009413428
+3   2     FH  0.0002999555 0.0017042498
+4   2      y  0.0002214372 0.0018404586
+5   3     FH  0.0004056162 0.0027148056
+6   3      y  0.0003529474 0.0032745696
+\end{Soutput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
+\end{Sinput}
+\end{Schunk}
+
+\includegraphics[width = \textwidth]{saeSim-modelSimBIAS.pdf}
+
+\begin{Schunk}
+\begin{Sinput}
+> ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
+\end{Sinput}
+\end{Schunk}
+
+\includegraphics[width = \textwidth]{saeSim-modelSimRMSE.pdf}
+
+\subsection{Design-based simulation}
+\begin{Schunk}
+\begin{Sinput}
+> data(eusilcP, package = "simFrame")
+> simDat <- eusilcP %>% 
++   mutate(agesq = age^2, eqIncome = as.numeric(eqIncome)) %>%
++   filter(main) %>%
++   select(region, eqIncome, age, agesq, gender) %>%
++   base_add_id(c("region"))
+> attr(simDat, "popMeans") <- 
++   simDat %>% 
++   group_by(idD, region) %>%
++   summarise(age = mean(age),
++             agesq = mean(agesq),
++             genderFemale = mean(as.integer(gender) - 1),
++             trueStat = mean(eqIncome))
+> attr(simDat, "popN") <- 
++   simDat %>%
++   group_by(idD) %>%
++   summarise(N = n())
+> attr(simDat, "popN")
+\end{Sinput}
+\begin{Soutput}
+Source: local data frame [9 x 2]
+
+  idD    N
+1   1  799
+2   2 4619
+3   3 5857
+4   4 1723
+5   5 3386
+6   6 4071
+7   7 1671
+8   8 1889
+9   9  985
+\end{Soutput}
+\begin{Sinput}
+> attr(simDat, "popMeans")
+\end{Sinput}
+\begin{Soutput}
+Source: local data frame [9 x 6]
+Groups: idD
+
+  idD        region      age    agesq genderFemale trueStat
+1   1    Burgenland 54.50063 3269.677    0.3366708 22005.42
+2   2 Lower Austria 51.95259 3009.934    0.3777874 19813.37
+3   3        Vienna 46.98310 2486.448    0.4662797 20395.84
+4   4     Carinthia 51.81428 2995.735    0.3540337 19486.18
+5   5        Styria 50.64087 2886.845    0.3573538 19335.39
+6   6 Upper Austria 50.18644 2795.804    0.3443871 20517.29
+7   7      Salzburg 51.44943 2965.268    0.4189108 19890.33
+8   8         Tyrol 51.76707 2995.451    0.3975648 19350.89
+9   9    Vorarlberg 49.06904 2697.382    0.3583756 22156.12
+\end{Soutput}
+\begin{Sinput}
+> 
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> comp_BHF <- function(dat) {
++   popMeans <- attr(dat, "popMeans") %>% select(-trueStat, -region)
++   modelBHF <- 
++     eblupBHF(eqIncome ~ age + agesq + gender, idD, meanxpop = popMeans,
++              popnsize = attr(dat, "popN"), data = dat)
++   attr(dat, "BHF") <- modelBHF$eblup
++   dat
++ }
+> comp_direct <- function(dat) {
++   attr(dat, "sampleMean") <- 
++     dat %>% group_by(idD) %>% summarise(y = mean(eqIncome))
++   dat  
++ }
+> agg_results <- function(dat) {
++   cbind(attr(dat, "popMeans") %>% select(idD, region, trueStat), 
++         BHF = attr(dat, "BHF")$eblup,
++         y = attr(dat, "sampleMean")$y)
++ }
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> simResults <- simDat %>% 
++   sim_sample(sample_fraction(0.1, groupVars = "idD")) %>%
++   sim_comp_sample(comp_BHF) %>%
++   sim_comp_sample(comp_direct) %>%
++   sim_agg(agg_results) %>%
++   sim(R = 50) %>%
++   rbind_all
+> ggDat <- simResults %>% 
++   melt(id.vars = c("idD", "region", "trueStat"), 
++        measure.vars = c("BHF", "y"), 
++        variable.name = "method",
++        value.name = "prediction")
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
++   geom_boxplot() + theme(legend.position = "bottom")
+\end{Sinput}
+\end{Schunk}
+
+\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+
+\begin{Schunk}
+\begin{Sinput}
+> ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
++   geom_boxplot() + scale_y_log10() + theme(legend.position = "bottom")
+\end{Sinput}
+\end{Schunk}
+
+\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
 

### 2014-10-21 saeSim.Rnw
update paper

@@
 \usepackage{graphicx}
+\usepackage{subcaption}
 
@@
 Hence a simulation setup is a collection of functions to be applied in a certain sequence.
-As the first-layer functions, also have a defined interface: a \proglang{sim\_setup} as input to be modified and a \proglang{sim\_setup} as output.
+Also the second-layer functions have a defined interface: a \proglang{sim\_setup} as input to be modified and a \proglang{sim\_setup} as output.
 Thus, components can be chained together using the \textit{pipe operator} (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14}.
 
+With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
+We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as a platform to make them accessible.
+By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
+In the next section we will present a case study and focus more on the concrete functionality provided by the package.
+
+\section{Case study}
 Braking the responsibility into what is applied and when it is applied addresses several aspects of reproducibility.
@@
 
-With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
-We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as a platform to make them accessible.
-By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
-In the next section we will present a case study and focus more on the concrete functionality provided by the package.
+As a side remark: The pipe operator, \proglang{\%>\%}, is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
+As a minimal example see the following lines which are equivalent:
 
-\section{Case study}
+<<>>=
+sum(1:10)
+1:10 %>% sum
+@
+
 \label{sec:caseStudy}
 \subsection{Model-based simulation}
-<<>>=
-suppressPackageStartupMessages(library(saeSim))
-suppressPackageStartupMessages(library(sae))
-suppressPackageStartupMessages(library(dplyr))
-suppressPackageStartupMessages(library(reshape2))
-suppressPackageStartupMessages(library(ggplot2))
 
+<<echo=FALSE>>=
 set.seed(1) # for reproduction of the results
@@
 
+The first task for the model-based simulation is to generate the data under the model:
+
+\[ y_i = 100 + 2 \cdot x_i + v_i + e_i\]
+
+where $x_i \stackrel{iid}{\sim} N(0, 4^2)$, $v_i \stackrel{iid}{\sim} N(0, 1)$ and $e_i \stackrel{indep}{\sim} N(0, \sigma_i^2)$ with $\sigma_i^2 = 0.1, 0.2, \dots, 4$ and $i = 1, \dots, 40$ as index for the domains.
+Also are $x_i$, $v_i$ and $e_i$ independent from each other.
+The starting point is always a data table as \textit{base-component}, in this case just with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
+Any random number generator in \proglang{R} can be used, however we have a strictly \textit{normal} model, for which some predefined functions can be used.
+
+<<results=hide>>=
+library(saeSim)
+@
+<<>>=
+setup <- base_id(nDomains = 40, nUnits = 1) %>% 
+  sim_gen_x(mean = 0, sd = 4) %>%
+  sim_gen_v(mean = 0, sd = 1)
+setup
+@
+
+Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows of the resulting data table are printed.
+This enables interactivity with the object itself, however it hides that the setup object is a collection of functions to be called.
+The error component $e_i$ in the model has different variances which is not covered by a predefined function.
+Thus, as a \textit{generator} function we will define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
+
+<<>>=
+gen_e <- function(dat) {
+  dat$vardir <- seq(0.1, 4, length.out = nrow(dat))
+  dat$e <- rnorm(nrow(dat), sd = sqrt(dat$vardir))
+  dat
+}
+setup <- setup %>% sim_gen(gen_e)
+setup
+@
+
+The last step in data generation is to construct the response variable which will be named \proglang{y} and added to the data.
+Also we will add the \textit{true} area statistic under the model to the data:
+
+<<>>=
+setup <- setup %>% 
+  sim_resp_eq(y = 100 + 2 * x + v + e) %>%
+  sim_comp_pop(comp_var(trueStat = y - e))
+@
+
+Not all necessary functions can be provided by the package.
+As said before, one of the main objectives was to define the interface between components.
+To add the area-level predictions from a Fay-Herriot model we need to define a function for that.
+The function takes a \proglang{data.frame} as input and returns the modified version.
+Here we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13} to estimate the EBLUP under the FH model.
+Finally we add \proglang{comp\_FH} to the process:
+
+<<results=hide>>=
+library(sae)
+@
 <<>>=
 comp_FH <- function(dat) {
-  # Computes the EBLUP under a Fay-Herriot model
-  modelFH <- eblupFH(y ~ x, vardir, data = dat, method = "FH")
+  modelFH <- eblupFH(y ~ x, vardir, data = dat)
   dat$FH <- modelFH$eblup
@@
 }
+setup <- setup %>% sim_comp_agg(comp_FH)
+setup
 @
 
+The object \proglang{setup} stores all necessary information to run one iteration of the simulation.
+To start more repetitions, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
+We use \proglang{rbind\_all} from the package \proglang{dplyr} to append the resulting \proglang{list}:
+
+<<results=hide>>=
+library(dplyr)
+@
 <<>>=
-simResults <- base_id(nDomains = 40, nUnits = 1) %>% 
-  sim_gen_fe() %>%
-  sim_gen_re() %>% 
-  sim_gen(comp_var(vardir = seq(0.1, 4, length.out = 40))) %>%
-  sim_gen(comp_var(e = rnorm(nrow(dat), sd = sqrt(vardir)))) %>%
-  sim_resp_eq(y = 100 + 2 * x + v + e) %>%
-  sim_comp_agg(comp_var(trueStat = y - e)) %>%
-  sim_comp_agg(comp_FH) %>%
-  sim(R = 500) %>%
-  rbind_all
+simResults <- sim(setup, R = 100) %>%rbind_all
+simResults %>% select(idD, idR, trueStat, y, FH)
 @
 
-<<>>=
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration.
+At this time we do not provide further tools to process the resulting data.
+As it is a \proglang{data.frame} many packages for processing that data are available in \proglang{R}, in this case \proglang{dplyr} \citep{wickham14} and \proglang{reshape2} \citep{wickham07} have been used.
+The Rmd-file for this article can be checked for further detail, thus we do not see need to provide further tools from here on.
+
+<<echo=FALSE>>=
+library(reshape2)
+library(ggplot2)
 ggDat <- simResults %>% 
@@
   as.data.frame
-
-head(ggDat)
 @
 
-<<modelSimBIAS, fig=TRUE, width = 8, height=4, include=FALSE>>=
+<<modelSimBIAS, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
 ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
@@
 
-\includegraphics[width = \textwidth]{saeSim-modelSimBIAS.pdf}
-
-<<modelSimRMSE, fig=TRUE, width = 8, height=4, include=FALSE>>=
+<<modelSimRMSE, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
 ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
@@
 
-\includegraphics[width = \textwidth]{saeSim-modelSimRMSE.pdf}
+\begin{figure}[h!]
+\begin{subfigure}{.5\textwidth}
+\centering
+\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
+\caption{}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+\centering
+\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
+\caption{}
+\end{subfigure}
+\caption{RBIAS and RMSE for the conducted model-based simulation}
+\end{figure}
 
 \subsection{Design-based simulation}
+
+In the design-based simulation we want to illustrate the use of \proglang{saeSim} when starting from data of a population.
+For this purpose we use a synthetic population generated from Austrian EU-SILC (European Union Statistics on Income and Living Conditions) data.
+We use this data to illustrate the functionality of the package, the data consists of 25 thousand households and does not represent the true population size of Austria.
+It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{alfons10} where it is used as example data.
+
 <<>>=

### 2014-10-21 saeSim.tex
update paper

@@
 
-With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
-We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as a platform to make them accessible.
-By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
-In the next section we will present a case study and focus more on the concrete functionality provided by the package.
+As a side remark: The pipe operator, \proglang{\%>\%}, is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
+As a minimal example see the following lines which are equivalent:
 
-\section{Case study}
+\begin{Schunk}
+\begin{Sinput}
+> sum(1:10)
+\end{Sinput}
+\begin{Soutput}
+[1] 55
+\end{Soutput}
+\begin{Sinput}
+> 1:10 %>% sum
+\end{Sinput}
+\begin{Soutput}
+[1] 55
+\end{Soutput}
+\end{Schunk}
+
 \label{sec:caseStudy}
 \subsection{Model-based simulation}
+
+The first task for the model-based simulation is to generate the data under the model:
+
+\[ y_i = 100 + 2 \cdot x_i + v_i + e_i\]
+
+where $x_i \stackrel{iid}{\sim} N(0, 4^2)$, $v_i \stackrel{iid}{\sim} N(0, 1)$ and $e_i \stackrel{indep}{\sim} N(0, \sigma_i^2)$ with $\sigma_i^2 = 0.1, 0.2, \dots, 4$ and $i = 1, \dots, 40$ as index for the domains.
+Also are $x_i$, $v_i$ and $e_i$ independent from each other.
+The starting point is always a data table as \textit{base-component}, in this case just with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
+Any random number generator in \proglang{R} can be used, however we have a strictly \textit{normal} model, for which some predefined functions can be used.
+
 \begin{Schunk}
 \begin{Sinput}
-> suppressPackageStartupMessages(library(saeSim))
-> suppressPackageStartupMessages(library(sae))
-> suppressPackageStartupMessages(library(dplyr))
-> suppressPackageStartupMessages(library(reshape2))
-> suppressPackageStartupMessages(library(ggplot2))
-> set.seed(1) # for reproduction of the results
+> library(saeSim)
+\end{Sinput}
+\end{Schunk}
+\begin{Schunk}
+\begin{Sinput}
+> setup <- base_id(nDomains = 40, nUnits = 1) %>% 
++   sim_gen_x(mean = 0, sd = 4) %>%
++   sim_gen_v(mean = 0, sd = 1)
+> setup
+\end{Sinput}
+\begin{Soutput}
+  idD          x          v
+1   1 -2.5058152 -0.1645236
+2   2  0.7345733 -0.2533617
+3   3 -3.3425144  0.6969634
+4   4  6.3811232  0.5566632
+5   5  1.3180311 -0.6887557
+6   6 -3.2818735 -0.7074952
+\end{Soutput}
+\end{Schunk}
+
+Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows of the resulting data table are printed.
+This enables interactivity with the object itself, however it hides that the setup object is a collection of functions to be called.
+The error component $e_i$ in the model has different variances which is not covered by a predefined function.
+Thus, as a \textit{generator} function we will define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
+
+\begin{Schunk}
+\begin{Sinput}
+> gen_e <- function(dat) {
++   dat$vardir <- seq(0.1, 4, length.out = nrow(dat))
++   dat$e <- rnorm(nrow(dat), sd = sqrt(dat$vardir))
++   dat
++ }
+> setup <- setup %>% sim_gen(gen_e)
+> setup
+\end{Sinput}
+\begin{Soutput}
+  idD          x          v vardir          e
+1   1 -2.2746749 -0.5059575    0.1  0.1344285
+2   2 -0.5407145  1.3430388    0.2 -0.1067262
+3   3  4.7123480 -0.2145794    0.3  0.5797550
+4   4 -6.0942672 -0.1795565    0.4  0.5606229
+5   5  2.3757848 -0.1001907    0.5 -0.4378710
+6   6  1.3318015  0.7126663    0.6  1.7088396
+\end{Soutput}
+\end{Schunk}
+
+The last step in data generation is to construct the response variable which will be named \proglang{y} and added to the data.
+Also we will add the \textit{true} area statistic under the model to the data:
+
+\begin{Schunk}
+\begin{Sinput}
+> setup <- setup %>% 
++   sim_resp_eq(y = 100 + 2 * x + v + e) %>%
++   sim_comp_pop(comp_var(trueStat = y - e))
 \end{Sinput}
@@
 
+Not all necessary functions can be provided by the package.
+As said before, one of the main objectives was to define the interface between components.
+To add the area-level predictions from a Fay-Herriot model we need to define a function for that.
+The function takes a \proglang{data.frame} as input and returns the modified version.
+Here we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13} to estimate the EBLUP under the FH model.
+Finally we add \proglang{comp\_FH} to the process:
+
+\begin{Schunk}
+\begin{Sinput}
+> library(sae)
+\end{Sinput}
+\end{Schunk}
 \begin{Schunk}
@@
 > comp_FH <- function(dat) {
-+   # Computes the EBLUP under a Fay-Herriot model
-+   modelFH <- eblupFH(y ~ x, vardir, data = dat, method = "FH")
++   modelFH <- eblupFH(y ~ x, vardir, data = dat)
 +   dat$FH <- modelFH$eblup
@@
 + }
+> setup <- setup %>% sim_comp_agg(comp_FH)
+> setup
 \end{Sinput}
+\begin{Soutput}
+  idD         x          v vardir          e         y  trueStat        FH
+1   1  1.637607  0.7073107    0.1  0.1258998 104.10843 103.98253 104.06121
+2   2  6.755493  1.0341077    0.2 -0.1822523 114.36284 114.54509 114.23876
+3   3  6.346354  0.2234804    0.3  0.7253263 113.64151 112.91619 113.45213
+4   4 -1.323631 -0.8787076    0.4 -0.4434978  96.03053  96.47403  96.45416
+5   5 -9.140942  1.1629646    0.5 -0.4105563  82.47052  82.88108  82.46045
+6   6  9.990646 -2.0001649    0.6 -0.7754272 117.20570 117.98113 118.08379
+\end{Soutput}
 \end{Schunk}
+
+The object \proglang{setup} stores all necessary information to run one iteration of the simulation.
+To initialize more repetition, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
+We use \proglang{rbind\_all} from the package \proglang{dplyr} to append the resulting \proglang{list}:
 
@@
 \begin{Sinput}
-> simResults <- base_id(nDomains = 40, nUnits = 1) %>% 
-+   sim_gen_fe() %>%
-+   sim_gen_re() %>% 
-+   sim_gen(comp_var(vardir = seq(0.1, 4, length.out = 40))) %>%
-+   sim_gen(comp_var(e = rnorm(nrow(dat), sd = sqrt(vardir)))) %>%
-+   sim_resp_eq(y = 100 + 2 * x + v + e) %>%
-+   sim_comp_agg(comp_var(trueStat = y - e)) %>%
-+   sim_comp_agg(comp_FH) %>%
-+   sim(R = 500) %>%
-+   rbind_all
+> library(dplyr)
 \end{Sinput}
 \end{Schunk}
-
 \begin{Schunk}
 \begin{Sinput}
-> ggDat <- simResults %>% 
-+   melt(id.vars = c("idD", "trueStat"), 
-+        measure.vars = c("FH", "y"), 
-+        variable.name = "method",
-+        value.name = "prediction") %>% 
-+   mutate(RBIAS = (prediction - trueStat)/trueStat,
-+          RRMSE = (prediction - trueStat)^2/trueStat) %>%
-+   group_by(idD, method) %>% 
-+   summarise(RBIAS = mean(RBIAS),
-+             RMSE = mean(RRMSE)) %>%
-+   as.data.frame
-> head(ggDat)
+> simResults <- sim(setup, R = 100) %>%rbind_all
+> simResults %>% select(idD, idR, trueStat, y, FH)
 \end{Sinput}
 \begin{Soutput}
-  idD method         RBIAS         RMSE
-1   1     FH -0.0001326439 0.0009412468
-2   1      y -0.0001285281 0.0009413428
-3   2     FH  0.0002999555 0.0017042498
-4   2      y  0.0002214372 0.0018404586
-5   3     FH  0.0004056162 0.0027148056
-6   3      y  0.0003529474 0.0032745696
+Source: local data frame [4,000 x 5]
+
+   idD idR  trueStat         y        FH
+1    1   1 107.87088 108.21065 108.30528
+2    2   1 113.29033 114.13809 113.80733
+3    3   1 105.88208 105.55180 105.63108
+4    4   1  84.61171  84.36450  84.63272
+5    5   1 103.68692 103.39260 103.42371
+6    6   1 104.26130 103.97032 103.79131
+7    7   1  97.85114  97.54439  97.43298
+8    8   1 101.93187 101.66741 101.49500
+9    9   1  92.51517  93.88300  93.67397
+10  10   1 104.07055 103.37302 104.01407
+.. ... ...       ...       ...       ...
 \end{Soutput}
@@
 
-\begin{Schunk}
-\begin{Sinput}
-> ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
-\end{Sinput}
-\end{Schunk}
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration.
+At this time we do not provide further tools to process the resulting data.
+As it is a \proglang{data.frame} many packages for processing that data are available in \proglang{R}, in this case \proglang{dplyr} \citep{wickham14} and \proglang{reshape2} \citep{wickham07} have been used.
+The Rmd-file for this article can be checked for further detail, thus we do not see need to provide further tools from here on.
 
-\includegraphics[width = \textwidth]{saeSim-modelSimBIAS.pdf}
-
-\begin{Schunk}
-\begin{Sinput}
-> ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
-\end{Sinput}
-\end{Schunk}
-
-\includegraphics[width = \textwidth]{saeSim-modelSimRMSE.pdf}
+\begin{figure}[h!]
+\begin{subfigure}{.5\textwidth}
+\centering
+\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
+\caption{}
+\end{subfigure}
+\begin{subfigure}{.5\textwidth}
+\centering
+\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
+\caption{}
+\end{subfigure}
+\caption{RBIAS and RMSE for the conducted model-based simulation}
+\end{figure}
 
 \subsection{Design-based simulation}
+
+In the design-based simulation we want to illustrate the use of \proglang{saeSim} when starting from data of a population.
+For this purpose we use a synthetic population generated from Austrian EU-SILC (European Union Statistics on Income and Living Conditions) data.
+We use this data to illustrate the functionality of the package, the data consists of 25 thousand households and does not represent the true population size of Austria.
+It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{alfons10} where it is used as example data.
+
 \begin{Schunk}

### 2014-10-22 saeSim.Rnw
update paper saeSim

@@
 <<>>=
-simResults <- sim(setup, R = 100) %>%rbind_all
-simResults %>% select(idD, idR, trueStat, y, FH)
+simResults <- sim(setup, R = 100) %>% rbind_all
+simResults %>% select(idD, idR, simName, trueStat, y, FH)
 @
 
-An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration.
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} which purpose is to distinguish between scenarios, should there be more than one.
 At this time we do not provide further tools to process the resulting data.
@@
 It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{alfons10} where it is used as example data.
+To keep this study as simple as possible, we further restrict the data for the main income holder and will only use some of the provided auxiliary information.
 
@@
   filter(main) %>%
-  select(region, eqIncome, age, agesq, gender) %>%
-  base_add_id(c("region"))
+  select(region, eqIncome, age, agesq, gender)
 
-attr(simDat, "popMeans") <- 
-  simDat %>% 
-  group_by(idD, region) %>%
+head(simDat)
+@
+
+For the purpose of the design-based case study we want to apply the earlier introduced BHF estimator which is implemented in the \proglang{R}-package \proglang{sae} \citep{molina13}.
+The function we use, \proglang{eblupBHF}, expects three data objects to produce the predictions.
+The sampled data, the population means of the auxiliary variables and the population sizes in each domain.
+To store these informations and make them available during the simulation we attach them as attributes to the population data.
+There are other options but setting attributes to the processed data is supported in the package and presents a very flexible form of processing data on different aggregation levels.
+
+<<>>=
+attr(simDat, "popMeans") <- group_by(simDat, region) %>% 
   summarise(age = mean(age),
@@
 
-attr(simDat, "popN") <- 
-  simDat %>%
-  group_by(idD) %>%
-  summarise(N = n())
+attr(simDat, "popMeans")
+
+attr(simDat, "popN") <- group_by(simDat, region) %>% summarise(N = n())
 
 attr(simDat, "popN")
-attr(simDat, "popMeans")
-
 @
 
+Before we come to the estimation configuration, the first step is to add a sampling scheme.
+As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data.
+Then the sampling component is added, in which we define to draw 10 per cent of the observations from each domain with simple random sampling.
+
 <<>>=
+setup <- simDat %>% 
+  sim_sample(sample_fraction(0.1, groupVars = "region"))
+setup
+@
+
+What now needs to be done, is to define the components which add the desired estimates to the data.
+Here we will compute the mean of income in each domain as the direct estimator and the EBLUP under the BHF model.
+Although this could be done in one step, we will separate the two computations to illustrate how to combine several estimations and define each component independent of one another.
+This focus on the definition of each component and meeting the convention of the defined interface is the intended approach.
+It will automatically organise the simulation and each component is arranged using the simulation framework.
+Hence, we will define two functions, one for adding the direct estimates and one for adding the EBLUP.
+
+<<>>=
+comp_direct <- function(dat) {
+  attr(dat, "sampleMean") <- 
+    dat %>% group_by(region) %>% summarise(direct = mean(eqIncome))
+  dat
+}
+
 comp_BHF <- function(dat) {
-  popMeans <- attr(dat, "popMeans") %>% select(-trueStat, -region)
+  popMeans <- select(attr(dat, "popMeans"), -trueStat)
   modelBHF <- 
-    eblupBHF(eqIncome ~ age + agesq + gender, idD, meanxpop = popMeans,
+    eblupBHF(eqIncome ~ age + agesq + gender, region, meanxpop = popMeans,
              popnsize = attr(dat, "popN"), data = dat)
@@
 }
+@
 
-comp_direct <- function(dat) {
-  attr(dat, "sampleMean") <- 
-    dat %>% group_by(idD) %>% summarise(y = mean(eqIncome))
-  dat  
-}
+Another positive aspect of the above definitions is, that each step is relatively small and the purpose clearly defined, which will make them easy to understand, modify and reproduce.
+Finally we will combine the simulation results in an \textit{aggregation-component}, possibly followed by the application of area-level models but skipped in this example.
+The result of this aggregation step will be a \proglang{data.frame} with one row for each region.
 
+<<>>=
 agg_results <- function(dat) {
-  cbind(attr(dat, "popMeans") %>% select(idD, region, trueStat), 
+  cbind(attr(dat, "sampleMean"),
         BHF = attr(dat, "BHF")$eblup,
-        y = attr(dat, "sampleMean")$y)
+        trueStat = attr(dat, "popMeans")$trueStat)
 }
@@
 
+To combine the simulation setup and the defined components we arrange them using the function \proglang{sim\_comp\_sample} to ensure that the direct estimator and the EBLUP is computed on the sampled data, and \proglang{sim\_agg} to add the above aggregation step.
+
 <<>>=
-simResults <- simDat %>% 
-  sim_sample(sample_fraction(0.1, groupVars = "idD")) %>%
+setup <- setup %>%
   sim_comp_sample(comp_BHF) %>%
   sim_comp_sample(comp_direct) %>%
-  sim_agg(agg_results) %>%
-  sim(R = 50) %>%
-  rbind_all
+  sim_agg(agg_results)
+setup
+@
 
-ggDat <- simResults %>% 
-  melt(id.vars = c("idD", "region", "trueStat"), 
-       measure.vars = c("BHF", "y"), 
+To repeat the simulation $R$ times the simulation setup can be passed to the function \proglang{sim}, the resulting \proglang{list} is directly combined using \proglang{rbind\_all}.
+
+<<>>=
+simResults <- setup %>% sim(R = 50) %>% rbind_all
+simResults
+@
+
+To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07}. 
+<<>>=
+ggDat <- melt(simResults,
+              id.vars = c("region", "trueStat"), 
+              measure.vars = c("BHF", "direct"), 
               variable.name = "method",
@@
 	\item parallel computations
+	\item Process the results of a simulation
 \end{itemize}

### 2014-10-22 saeSim.tex
update paper saeSim

@@
 The object \proglang{setup} stores all necessary information to run one iteration of the simulation.
-To initialize more repetition, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
+To start more repetitions, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
 We use \proglang{rbind\_all} from the package \proglang{dplyr} to append the resulting \proglang{list}:
@@
 \begin{Sinput}
-> simResults <- sim(setup, R = 100) %>%rbind_all
-> simResults %>% select(idD, idR, trueStat, y, FH)
+> simResults <- sim(setup, R = 100) %>% rbind_all
+> simResults %>% select(idD, idR, simName, trueStat, y, FH)
 \end{Sinput}
 \begin{Soutput}
-Source: local data frame [4,000 x 5]
+Source: local data frame [4,000 x 6]
 
-   idD idR  trueStat         y        FH
+   idD idR simName  trueStat         y        FH
 1    1   1         107.87088 108.21065 108.30528
@@
 10  10   1         104.07055 103.37302 104.01407
-.. ... ...       ...       ...       ...
+.. ... ...     ...       ...       ...       ...
 \end{Soutput}
@@
 
-An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration.
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} which purpose is to distinguish between scenarios, should there be more than one.
 At this time we do not provide further tools to process the resulting data.
@@
 +   filter(main) %>%
-+   select(region, eqIncome, age, agesq, gender) %>%
-+   base_add_id(c("region"))
-> attr(simDat, "popMeans") <- 
-+   simDat %>% 
-+   group_by(idD, region) %>%
++   select(region, eqIncome, age, agesq, gender)
+> head(simDat)
+\end{Sinput}
+\begin{Soutput}
+         region eqIncome age agesq gender
+1 Upper Austria 11128.45  25   625   male
+2        Styria 19694.85  53  2809   male
+3        Styria  5066.24  30   900 female
+4 Upper Austria 31480.01  32  1024   male
+5        Vienna 17813.40  77  5929 female
+6 Lower Austria 13501.53  35  1225   male
+\end{Soutput}
+\end{Schunk}
+
+For the purpose of the design-based case study we want to apply the earlier introduced BHF estimator which is implemented in the \proglang{R}-package \proglang{sae} \citep{molina13}.
+The function we use, \proglang{eblupBHF}, expects three data objects to produce the predictions.
+The sampled data, the population means of the auxiliary variables and the population sizes in each domain.
+To store these informations and make them available during the simulation we attach them as attributes to the population data.
+There are other options but setting attributes to the processed data is supported in the package and presents a very flexible form of processing data on different aggregation levels.
+
+\begin{Schunk}
+\begin{Sinput}
+> attr(simDat, "popMeans") <- group_by(simDat, region) %>% 
 +   summarise(age = mean(age),
@@
 +             trueStat = mean(eqIncome))
-> attr(simDat, "popN") <- 
-+   simDat %>%
-+   group_by(idD) %>%
-+   summarise(N = n())
+> attr(simDat, "popMeans")
+\end{Sinput}
+\begin{Soutput}
+Source: local data frame [9 x 5]
+
+         region      age    agesq genderFemale trueStat
+1    Burgenland 54.50063 3269.677    0.3366708 22005.42
+2 Lower Austria 51.95259 3009.934    0.3777874 19813.37
+3        Vienna 46.98310 2486.448    0.4662797 20395.84
+4     Carinthia 51.81428 2995.735    0.3540337 19486.18
+5        Styria 50.64087 2886.845    0.3573538 19335.39
+6 Upper Austria 50.18644 2795.804    0.3443871 20517.29
+7      Salzburg 51.44943 2965.268    0.4189108 19890.33
+8         Tyrol 51.76707 2995.451    0.3975648 19350.89
+9    Vorarlberg 49.06904 2697.382    0.3583756 22156.12
+\end{Soutput}
+\begin{Sinput}
+> attr(simDat, "popN") <- group_by(simDat, region) %>% summarise(N = n())
 > attr(simDat, "popN")
@@
 
-  idD    N
-1   1  799
-2   2 4619
-3   3 5857
-4   4 1723
-5   5 3386
-6   6 4071
-7   7 1671
-8   8 1889
-9   9  985
+         region    N
+1    Burgenland  799
+2 Lower Austria 4619
+3        Vienna 5857
+4     Carinthia 1723
+5        Styria 3386
+6 Upper Austria 4071
+7      Salzburg 1671
+8         Tyrol 1889
+9    Vorarlberg  985
 \end{Soutput}
-\begin{Sinput}
-> attr(simDat, "popMeans")
-\end{Sinput}
-\begin{Soutput}
-Source: local data frame [9 x 6]
-Groups: idD
+\end{Schunk}
 
-  idD        region      age    agesq genderFemale trueStat
-1   1    Burgenland 54.50063 3269.677    0.3366708 22005.42
-2   2 Lower Austria 51.95259 3009.934    0.3777874 19813.37
-3   3        Vienna 46.98310 2486.448    0.4662797 20395.84
-4   4     Carinthia 51.81428 2995.735    0.3540337 19486.18
-5   5        Styria 50.64087 2886.845    0.3573538 19335.39
-6   6 Upper Austria 50.18644 2795.804    0.3443871 20517.29
-7   7      Salzburg 51.44943 2965.268    0.4189108 19890.33
-8   8         Tyrol 51.76707 2995.451    0.3975648 19350.89
-9   9    Vorarlberg 49.06904 2697.382    0.3583756 22156.12
-\end{Soutput}
-\begin{Sinput}
-> 
-\end{Sinput}
-\end{Schunk}
+Before we come to the estimation configuration, the first step is to add a sampling scheme.
+As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data.
+Then the sampling component is added, in which we define to draw 10 per cent of the observations from each domain with simple random sampling.
 
@@
 \begin{Sinput}
+> setup <- simDat %>% 
++   sim_sample(sample_fraction(0.1, groupVars = "region"))
+> setup
+\end{Sinput}
+\begin{Soutput}
+      region eqIncome age agesq gender
+1 Burgenland 23572.28  67  4489   male
+2 Burgenland 24056.37  26   676   male
+3 Burgenland 21613.73  46  2116   male
+4 Burgenland 11750.30  40  1600   male
+5 Burgenland  9664.08  80  6400 female
+6 Burgenland 19369.91  63  3969 female
+\end{Soutput}
+\end{Schunk}
+
+What now needs to be done, is to define the components which add the desired estimates to the data.
+Here we will compute the mean of income in each domain as the direct estimator and the EBLUP under the BHF model.
+Although this could be done in one step, we will separate the two computations to illustrate how to combine several estimations and define each component independent of one another.
+This focus on the definition of each component and meeting the convention of the defined interface is the intended approach.
+It will automatically organise the simulation and each component is arranged using the simulation framework.
+Hence, we will define two functions, one for adding the direct estimates and one for adding the EBLUP.
+
+\begin{Schunk}
+\begin{Sinput}
+> comp_direct <- function(dat) {
++   attr(dat, "sampleMean") <- 
++     dat %>% group_by(region) %>% summarise(direct = mean(eqIncome))
++   dat
++ }
 > comp_BHF <- function(dat) {
-+   popMeans <- attr(dat, "popMeans") %>% select(-trueStat, -region)
++   popMeans <- select(attr(dat, "popMeans"), -trueStat)
 +   modelBHF <- 
-+     eblupBHF(eqIncome ~ age + agesq + gender, idD, meanxpop = popMeans,
++     eblupBHF(eqIncome ~ age + agesq + gender, region, meanxpop = popMeans,
 +              popnsize = attr(dat, "popN"), data = dat)
@@
 + }
-> comp_direct <- function(dat) {
-+   attr(dat, "sampleMean") <- 
-+     dat %>% group_by(idD) %>% summarise(y = mean(eqIncome))
-+   dat  
-+ }
+\end{Sinput}
+\end{Schunk}
+
+Another positive aspect of the above definitions is, that each step is relatively small and the purpose clearly defined, which will make them easy to understand, modify and reproduce.
+Finally we will combine the simulation results in an \textit{aggregation-component}, possibly followed by the application of area-level models but skipped in this example.
+The result of this aggregation step will be a \proglang{data.frame} with one row for each region.
+
+\begin{Schunk}
+\begin{Sinput}
 > agg_results <- function(dat) {
-+   cbind(attr(dat, "popMeans") %>% select(idD, region, trueStat), 
++   cbind(attr(dat, "sampleMean"),
 +         BHF = attr(dat, "BHF")$eblup,
-+         y = attr(dat, "sampleMean")$y)
++         trueStat = attr(dat, "popMeans")$trueStat)
 + }
@@
 
+To combine the simulation setup and the defined components we arrange them using the function \proglang{sim\_comp\_sample} to ensure that the direct estimator and the EBLUP is computed on the sampled data, and \proglang{sim\_agg} to add the above aggregation step.
+
 \begin{Schunk}
 \begin{Sinput}
-> simResults <- simDat %>% 
-+   sim_sample(sample_fraction(0.1, groupVars = "idD")) %>%
+> setup <- setup %>%
 +   sim_comp_sample(comp_BHF) %>%
 +   sim_comp_sample(comp_direct) %>%
-+   sim_agg(agg_results) %>%
-+   sim(R = 50) %>%
-+   rbind_all
-> ggDat <- simResults %>% 
-+   melt(id.vars = c("idD", "region", "trueStat"), 
-+        measure.vars = c("BHF", "y"), 
++   sim_agg(agg_results)
+> setup
+\end{Sinput}
+\begin{Soutput}
+         region   direct      BHF trueStat
+1    Burgenland 21933.95 21255.53 22005.42
+2 Lower Austria 18885.08 19036.29 19813.37
+3        Vienna 20734.08 20720.48 20395.84
+4     Carinthia 19211.55 19377.21 19486.18
+5        Styria 18704.75 18955.96 19335.39
+6 Upper Austria 20636.94 20504.37 20517.29
+\end{Soutput}
+\end{Schunk}
+
+To repeat the simulation $R$ times the simulation setup can be passed to the function \proglang{sim}, the resulting \proglang{list} is directly combined using \proglang{rbind\_all}.
+
+\begin{Schunk}
+\begin{Sinput}
+> simResults <- setup %>% sim(R = 50) %>% rbind_all
+> simResults
+\end{Sinput}
+\begin{Soutput}
+Source: local data frame [450 x 6]
+
+          region   direct      BHF trueStat idR simName
+1     Burgenland 23083.61 20800.16 22005.42   1        
+2  Lower Austria 20414.91 20264.56 19813.37   1        
+3         Vienna 20756.78 20422.85 20395.84   1        
+4      Carinthia 19581.64 19912.42 19486.18   1        
+5         Styria 19443.11 19757.42 19335.39   1        
+6  Upper Austria 20417.38 20356.38 20517.29   1        
+7       Salzburg 19900.44 20009.83 19890.33   1        
+8          Tyrol 18493.29 19540.25 19350.89   1        
+9     Vorarlberg 21166.20 20444.35 22156.12   1        
+10    Burgenland 21340.42 20510.92 22005.42   2        
+..           ...      ...      ...      ... ...     ...
+\end{Soutput}
+\end{Schunk}
+
+To further process simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for 
+\begin{Schunk}
+\begin{Sinput}
+> ggDat <- melt(simResults,
++               id.vars = c("region", "trueStat"), 
++               measure.vars = c("BHF", "direct"), 
 +               variable.name = "method",

### 2014-10-22 saeSim.Rnw
update paper

@@
 \section{Outlook}
+With \proglang{saeSim} have three objects, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
+By providing the package we not only want to make our own tools available but also open it for contributions.
+The package source is available on CRAN \url{somewhere} and the repository for development at \utl{https://github.com/wahani/saeSim} where tools may be submitted.
+Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
+One aspect is the design of simulations as processes of data, which changes the
 Use this package to share and publish simulation studies alongside papers.

### 2014-10-22 saeSim.Rnw
Added new Introduction, beginning of conclusion

--- 2014-10-22 saeSim.Rnw
@@
 \section{Introduction}
-The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
-Groups may be areas or other entities, for example defined by socio-economic characteristics.
-New statistical methods are applied in model-based and design-based simulation studies.
-Considering the demands for reproducible research we propose a framework for simulation studies inside the field of small area estimation.
+The demand for reliable small area statistics from sample surveys has been substantial grown over the last decades due to their use in public and private sectors.
+In this paper we present a framework for simulation studies inside the field of small area estimation.
+This tool might be useful for the prospective researcher or data analyst to provide reproducible research.
 
-Reproducible Research has become a widely discussed topic in general and also in the field of statistics.
-Thanks to the many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, and also packages like knitr \citep{yihui13} and Sweave \citep{leisch02} and more recently rmarkdown \citep{allaire14}, the integration of text and source code for statistical analysis is possible.
-Not only are tools available to make research reproducible, also the demand of making the analysis of articles reproducible is rising which is supported by the rising number of Open Access Journals.
-Publishing source-code and data alongside an article draws special attention to authoring an analysis.
+Reproducible research has become a widely discussed topic in many academic areas.
+For instance in the field of statistics, many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
+Publishing source-code and data alongside in an article draws special attention to authoring the analysis.
 However, the requirements for source code are different from the written words in the article itself.
@@
 
-In this article we want to introduce a new package for the \proglang{R}-language to support the process of making simulation studies reproducible as well as supporting a \textit{human-readable} interface.
-With this package we have three objectives in specific: First, making tools for data generation available and reusable.
-Second, unify the process behind simulation studies inside the field of Small Area Estimation.
-And third, making source-code of simulation studies available, such that it supports the conducted research in a transparent manner.
+Next to the combination of text and source code, reproducible research aims that the full output of the academic research which is the paper combined with the full computational environment like data and source code, is available.
+However, real data is often very sensitive and governed by strictly confidentiality rules.
+Synthetic data generation mechanisms \citep{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.
+\cite{Bur14} interpreted this as an open research philosophy.
+Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework/ simulation.
+This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios.
+In general, statistical simulation studies are divided in the literature into two concepts:
+\begin{itemize}
+\item Design-based: The simulation study is based on true or synthetic data of a fixed population.
+Then, samples are selected repeatedly from the underlying finite population and different estimation methods are applied in each replication.
+The obtained estimates are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
+\item Model-based: The simulation study uses data drawn from certain distributions.
+In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme.
+The sample is used to estimate the quantity of interest and quality measures (like RB and RRMSE) are derived.
+\end{itemize}
+Further discussion regarding model- and design-based simulations is available in \cite{Mue03}, \cite{Sal10} or \cite{Alf10}.
 
-In section \ref{sec:SAE} we will give a short introduction to small area estimation and the role of simulation studies within that field.
-Section \ref{sec:framework} will then introduce a framework for simulation studies and how it is supported by \proglang{saeSim}.
-To illustrate some of the package's features we present a case study in section \ref{sec:caseStudy}.
+However, simulation studies are often presented very briefly in academic articles without providing enough details about the underlying structure of the study.
+\cite{Alf10} provide a framework (\proglang{simFrame}) which helps the prospective researcher or data analyst to conduct simulation studies in a reproducible environment.
+The \proglang{R}-package \proglang{simFrame} \citep{Alf10} is an object-oriented tool for statistical simulation studies based on \proglang{S}4 classes.
+It includes a wide range of different features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies.
+\proglang{simFrame} was originally developed for simulations in the context of survey statistics but is now designed to be as general as possible \citep[cf.][]{Alf10}.
+
+Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes.
+Especially regional or group-specific comparisons are of interest \citep[cf.][]{Sch13}.
+Surveys which shall provide the sufficient data for these regional indicators, however, are generally designed for larger areas (NUTS 1-2 level).
+Hence, sample information on more detailed levels, like NUTS3, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}.
+In this case, small area estimation methods may reveal highly improved results for the target estimates.
+Small area estimation has become more and more attractive over the last decade:
+
+\begin{quote}
+\textit{In 2002, small area estimation (SAE) was flourishing both in research and applications, but my own feeling then was that the topic has been more or less exhausted in terms of research and that it will just turn into a routine application in sample survey practice.
+As the past 9 years show, I was completely wrong; not only is the research in this area accelerating, but it now involves some of the best known statisticians...} \cite{pfeffermann13}
+\end{quote}
+
+However, the empirical part is also often presented very briefly in the context of small area estimation.
+Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis.
+To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
+
+The aim of this article is to inform the prospective researcher or data analyst of a new \proglang{R}-package (\proglang{simFrame}) which supports the process of making simulation studies reproducible and offers a \textit{human-readable} interface in the field of small area estimation.
+To be more precise, the package has three main objectives: First, provide tools for data generation which are reproducible.
+Second, unify the process of simulation studies.
+Third, make the source-code of simulation studies available, such that it supports the conducted research in a transparent manner.
+
+The paper is organised as follows.
+In Section \ref{sec:SAE} we give a short introduction to small area estimation focusing mainly on unit-level \citep{battese88} and area-level models \citep{fay79}.
+Section \ref{sec:framework} introduces a framework for simulation studies and how it is supported by the  \proglang{R}-package \proglang{saeSim}.
+To illustrate some of the features of the package we present a case study in Section \ref{sec:caseStudy}.
+We conclude the paper in Section \ref{sec:outlook} by summarising the main findings and by providing some avenues for further research.
+
+\textcolor{red}{SONSTIGER TEXT:
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+Groups may be areas or other entities, for example defined by socio-economic characteristics.
+New statistical methods are applied in model-based and design-based simulation studies.
+Considering the demands for reproducible research we propose a framework for simulation studies inside the field of small area estimation.}
 
@@
 
-<<echo=FALSE>>=
-library(reshape2)
-library(ggplot2)
-ggDat <- simResults %>% 
-  melt(id.vars = c("idD", "trueStat"), 
-       measure.vars = c("FH", "y"), 
-       variable.name = "method",
-       value.name = "prediction") %>% 
-  mutate(RBIAS = (prediction - trueStat)/trueStat,
-         RRMSE = (prediction - trueStat)^2/trueStat) %>%
-  group_by(idD, method) %>% 
-  summarise(RBIAS = mean(RBIAS),
-            RMSE = mean(RRMSE)) %>%
-  as.data.frame
-@
+%<<echo=FALSE>>=
+%library(reshape2)
+%library(ggplot2)
+%ggDat <- simResults %>% 
+%  melt(id.vars = c("idD", "trueStat"), 
+%       measure.vars = c("FH", "y"), 
+%       variable.name = "method",
+%       value.name = "prediction") %>% 
+%  mutate(RBIAS = (prediction - trueStat)/trueStat,
+%         RRMSE = (prediction - trueStat)^2/trueStat) %>%
+%  group_by(idD, method) %>% 
+%  summarise(RBIAS = mean(RBIAS),
+%            RMSE = mean(RRMSE)) %>%
+%  as.data.frame
+%@
+%
+%<<modelSimBIAS, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
+%ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
+%@
+%
+%<<modelSimRMSE, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
+%ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
+%@
 
-<<modelSimBIAS, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
-ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
-@
-
-<<modelSimRMSE, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
-ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
-@
-
-\begin{figure}[h!]
-\begin{subfigure}{.5\textwidth}
-\centering
-\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
-\caption{}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-\centering
-\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
-\caption{}
-\end{subfigure}
-\caption{RBIAS and RMSE for the conducted model-based simulation}
-\end{figure}
+%\begin{figure}[h!]
+%\begin{subfigure}{.5\textwidth}
+%\centering
+%\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
+%\caption{}
+%\end{subfigure}
+%\begin{subfigure}{.5\textwidth}
+%\centering
+%\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
+%\caption{}
+%\end{subfigure}
+%\caption{RBIAS and RMSE for the conducted model-based simulation}
+%\end{figure}
 
@@
 We use this data to illustrate the functionality of the package, the data consists of 25 thousand households and does not represent the true population size of Austria.
-It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{alfons10} where it is used as example data.
+It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is used as example data.
 To keep this study as simple as possible, we further restrict the data for the main income holder and will only use some of the provided auxiliary information.
@@
 To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07}.
+
 <<>>=
@@
 \section{Outlook}
-Use this package to share and publish simulation studies alongside papers.
-Contribute to the package to make your ideas available.
-Contribute to the package and make your whole simulation study available.
+\label{sec:outlook}
+With \proglang{saeSim} have three objects, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
+By providing the package we not only want to make our own tools available but also open it for contributions.
+The package source is available on CRAN \url{somewhere} and the repository for development at \url{https://github.com/wahani/saeSim}.
+As GitHub allows to share and contribute source code using version control, it is open for submissions.
+Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
+One aspect is the design of simulations as processes of data.
+Furthermore by supporting the definition of small and self contained components, i.e.
+functions, as this reduces the lines of code to be read in order to understand it's purpose.
+
+The package already provides more than introduced in this article and likewise some tools are still missing.
+The support of outlier contaminated data.
+At this time only representative outliers (outlying observations in the population) are supported.
+However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
+The inclusion of available random numbers from the R-language is already possible and supports easy access to generate group effects as needed in mixed models.
+As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables and errors can be introduced.
+
+A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R}.
+Still missing but maybe helpful are tools to process the data after the simulation as well as plotting methods for that data.
+Already available are some simple plots for the simulation setups as well as a summary method, to get information on the expected run time and structure of the resulting data.
+
 \begin{itemize}
-	\item Link to simFrame
-	\item Package Features
-	\begin{itemize}
-		\item outliers
-		\item sampling
-		\item non-linear models
-	\end{itemize}
-	\item How to contribute?
+	\item Link to simFrame?
 	\item parallel computations
 	\item Process the results of a simulation
+\end{itemize}
+
+\section{TODO}
+\begin{itemize}
+	\item Chapter 3 + 4 - what will happen in these chapters?
+	\item kein RBIAS + RRMSE in model-based
+	\item Einleitung 4.2 was ist das ziel der design-basierten simulation
+	\item Conclusion
 \end{itemize}

### 2014-10-22 saeSim.tex
Added new Introduction, beginning of conclusion

@@
 
-\begin{figure}[h!]
-\begin{subfigure}{.5\textwidth}
-\centering
-\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
-\caption{}
-\end{subfigure}
-\begin{subfigure}{.5\textwidth}
-\centering
-\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
-\caption{}
-\end{subfigure}
-\caption{RBIAS and RMSE for the conducted model-based simulation}
-\end{figure}
+%<<echo=FALSE>>=
+%library(reshape2)
+%library(ggplot2)
+%ggDat <- simResults %>% 
+%  melt(id.vars = c("idD", "trueStat"), 
+%       measure.vars = c("FH", "y"), 
+%       variable.name = "method",
+%       value.name = "prediction") %>% 
+%  mutate(RBIAS = (prediction - trueStat)/trueStat,
+%         RRMSE = (prediction - trueStat)^2/trueStat) %>%
+%  group_by(idD, method) %>% 
+%  summarise(RBIAS = mean(RBIAS),
+%            RMSE = mean(RRMSE)) %>%
+%  as.data.frame
+%@
+%
+%<<modelSimBIAS, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
+%ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
+%@
+%
+%<<modelSimRMSE, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
+%ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
+%@
+
+%\begin{figure}[h!]
+%\begin{subfigure}{.5\textwidth}
+%\centering
+%\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
+%\caption{}
+%\end{subfigure}
+%\begin{subfigure}{.5\textwidth}
+%\centering
+%\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
+%\caption{}
+%\end{subfigure}
+%\caption{RBIAS and RMSE for the conducted model-based simulation}
+%\end{figure}
 
@@
 
-To further process simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for 
+To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07}.
+
 \begin{Schunk}
@@
 +               value.name = "prediction")
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
-> ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
-+   geom_boxplot() + theme(legend.position = "bottom")
-\end{Sinput}
-\end{Schunk}
-
-\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
-
-\begin{Schunk}
-\begin{Sinput}
-> ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
-+   geom_boxplot() + scale_y_log10() + theme(legend.position = "bottom")
-\end{Sinput}
-\end{Schunk}
-
-\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
-
-\section{Outlook}
-Use this package to share and publish simulation studies alongside papers.
-Contribute to the package to make your ideas available.
-Contribute to the package and make your whole simulation study available.
-\begin{itemize}
-	\item Link to simFrame
-	\item Package Features
-	\begin{itemize}
-		\item outliers
-		\item sampling
-		\item non-linear models
-	\end{itemize}
-	\item How to contribute?
-	\item parallel computations
-\end{itemize}
-
-%\bibliographystyle{plainat}
-\bibliography{saeSim}
-
-\end{document}

### 2014-10-23 saeSim.Rnw
update paper

@@
 if(!suppressPackageStartupMessages(require(saeSim))) {
-  if(!require(devtools)) {
-    install.packages("devtools", repos = "http://cran.at.r-project.org/", dependencies = TRUE)
-    library(devtools)
-  }
-
-  install.packages(c("dplyr", "ggplot2", "MASS", "spdep"), 
-                   repos = "http://cran.at.r-project.org/", dependencies = TRUE)
-  install_github("wahani/saeSim")
+  install.packages("saeSim")
 }
@@
 
-To combine the simulation setup and the defined components we arrange them using the function \proglang{sim\_comp\_sample} to ensure that the direct estimator and the EBLUP is computed on the sampled data, and \proglang{sim\_agg} to add the above aggregation step.
+To combine the simulation setup and the defined components we arrange them using the function \proglang{sim\_comp\_sample} to ensure that the direct estimator and the EBLUP are computed on the sampled data, and \proglang{sim\_agg} to add the above aggregation step.
 
@@
 <<>>=
+library(reshape2)
 ggDat <- melt(simResults,
@@
 <<designSimBIAS, fig=TRUE, width = 8.3, height=4, include=FALSE>>=
+library(ggplot2)
 ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 \label{sec:outlook}
-With \proglang{saeSim} have three objects, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
+With \proglang{saeSim} we have three objectives, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
 By providing the package we not only want to make our own tools available but also open it for contributions.
-The package source is available on CRAN \url{somewhere} and the repository for development at \url{https://github.com/wahani/saeSim}.
-As GitHub allows to share and contribute source code using version control, it is open for submissions.
+The package source is available on CRAN (\url{http://cran.r-project.org/web/packages/saeSim/}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
+As GitHub allows to share and contribute source code using version-control, it is open for submissions.
 Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
 One aspect is the design of simulations as processes of data.
-Furthermore by supporting the definition of small and self contained components, i.e.
-functions, as this reduces the lines of code to be read in order to understand it's purpose.
+Furthermore, we encourage the definition of small and self contained components, i.e.
+functions, as this reduces the lines of code necessary to be read in order to understand it's purpose.
 
 The package already provides more than introduced in this article and likewise some tools are still missing.
-The support of outlier contaminated data.
+To mention is the support of outlier contaminated data.
 At this time only representative outliers (outlying observations in the population) are supported.
 However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
-The inclusion of available random numbers from the R-language is already possible and supports easy access to generate group effects as needed in mixed models.
-As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables and errors can be introduced.
+Furthermore, the inclusion of available random number generators available in the R-language is already possible and easy access to generate group effects as needed in mixed models is supported.
+Also, as the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
 
-A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R}.
-Still missing but maybe helpful are tools to process the data after the simulation as well as plotting methods for that data.
-Already available are some simple plots for the simulation setups as well as a summary method, to get information on the expected run time and structure of the resulting data.
+A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
+Tools to process result data after the simulation as well as plotting methods for that data are missing.
+Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
 
@@
 	\item Link to simFrame?
-	\item parallel computations
-	\item Process the results of a simulation
 \end{itemize}

### 2014-10-23 saeSim.tex
update paper

@@
           region   direct      BHF trueStat idR simName
-1     Burgenland 23083.61 20800.16 22005.42   1        
+1     Burgenland 23083.61 20800.15 22005.42   1        
 2  Lower Austria 20414.91 20264.56 19813.37   1        
 3         Vienna 20756.78 20422.85 20395.84   1        
-4      Carinthia 19581.64 19912.42 19486.18   1        
+4      Carinthia 19581.64 19912.43 19486.18   1        
 5         Styria 19443.11 19757.42 19335.39   1        
@@
 \begin{Sinput}
+> library(reshape2)
 > ggDat <- melt(simResults,
@@
 +               value.name = "prediction")
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
+> library(ggplot2)
+> ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
++   geom_boxplot() + theme(legend.position = "bottom")
+\end{Sinput}
+\end{Schunk}
+
+\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+
+\begin{Schunk}
+\begin{Sinput}
+> ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
++   geom_boxplot() + scale_y_log10() + theme(legend.position = "bottom")
+\end{Sinput}
+\end{Schunk}
+
+\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
+
+\section{Outlook}
+\label{sec:outlook}
+With \proglang{saeSim} we have three objectives, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
+By providing the package we not only want to make our own tools available but also open it for contributions.
+The package source is available on CRAN (\url{http://cran.r-project.org/web/packages/saeSim/}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
+As GitHub allows to share and contribute source code using version-control, it is open for submissions.
+Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
+One aspect is the design of simulations as processes of data.
+Furthermore, we encourage the definition of small and self contained components, i.e.
+functions, as this reduces the lines of code necessary to be read in order to understand it's purpose.
+
+The package already provides more than introduced in this article and likewise some tools are still missing.
+To mention is the support of outlier contaminated data.
+At this time only representative outliers (outlying observations in the population) are supported.
+However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
+Furthermore, the inclusion of available random number generators available in the R-language is already possible and easy access to generate group effects as needed in mixed models is supported.
+Also, as the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
+
+A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
+Tools to process result data after the simulation as well as plotting methods for that data are missing.
+Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
+
+\begin{itemize}
+	\item Link to simFrame?
+\end{itemize}
+
+\section{TODO}
+\begin{itemize}
+	\item Chapter 3 + 4 - what will happen in these chapters?
+	\item kein RBIAS + RRMSE in model-based
+	\item Einleitung 4.2 was ist das ziel der design-basierten simulation
+	\item Conclusion
+\end{itemize}
+
+%\bibliographystyle{plainat}
+\bibliography{saeSim}
+
+\end{document}

### 2014-10-24 saeSim.tex
clean-up

@@
 To start more repetitions, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
-We use \proglang{rbind\_all} from the package \proglang{dplyr} to append the resulting \proglang{list}:
+We use \proglang{rbind\_all} from the package \proglang{dplyr} to combine the resulting \proglang{list} into one \proglang{data.frame}:
 
@@
 The Rmd-file for this article can be checked for further detail, thus we do not see need to provide further tools from here on.
-
-%<<echo=FALSE>>=
-%library(reshape2)
-%library(ggplot2)
-%ggDat <- simResults %>% 
-%  melt(id.vars = c("idD", "trueStat"), 
-%       measure.vars = c("FH", "y"), 
-%       variable.name = "method",
-%       value.name = "prediction") %>% 
-%  mutate(RBIAS = (prediction - trueStat)/trueStat,
-%         RRMSE = (prediction - trueStat)^2/trueStat) %>%
-%  group_by(idD, method) %>% 
-%  summarise(RBIAS = mean(RBIAS),
-%            RMSE = mean(RRMSE)) %>%
-%  as.data.frame
-%@
-%
-%<<modelSimBIAS, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
-%ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
-%@
-%
-%<<modelSimRMSE, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
-%ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
-%@
-
-%\begin{figure}[h!]
-%\begin{subfigure}{.5\textwidth}
-%\centering
-%\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
-%\caption{}
-%\end{subfigure}
-%\begin{subfigure}{.5\textwidth}
-%\centering
-%\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
-%\caption{}
-%\end{subfigure}
-%\caption{RBIAS and RMSE for the conducted model-based simulation}
-%\end{figure}
 
@@
 > library(ggplot2)
+\end{Sinput}
+\end{Schunk}
+
+\begin{Schunk}
+\begin{Sinput}
 > ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 
-\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+%\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
 
@@
 
-\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
+%\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
 
@@
 \label{sec:outlook}
-With \proglang{saeSim} we have three objectives, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
+With \proglang{saeSim} have three objects, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
 By providing the package we not only want to make our own tools available but also open it for contributions.
-The package source is available on CRAN (\url{http://cran.r-project.org/web/packages/saeSim/}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
-As GitHub allows to share and contribute source code using version-control, it is open for submissions.
+The package source is available on CRAN \url{somewhere} and the repository for development at \url{https://github.com/wahani/saeSim}.
+As GitHub allows to share and contribute source code using version control, it is open for submissions.
 Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
 One aspect is the design of simulations as processes of data.
-Furthermore, we encourage the definition of small and self contained components, i.e.
-functions, as this reduces the lines of code necessary to be read in order to understand it's purpose.
+Furthermore by supporting the definition of small and self contained components, i.e.
+functions, as this reduces the lines of code to be read in order to understand it's purpose.
 
 The package already provides more than introduced in this article and likewise some tools are still missing.
-To mention is the support of outlier contaminated data.
+The support of outlier contaminated data.
 At this time only representative outliers (outlying observations in the population) are supported.
 However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
-Furthermore, the inclusion of available random number generators available in the R-language is already possible and easy access to generate group effects as needed in mixed models is supported.
-Also, as the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
+The inclusion of available random numbers from the R-language is already possible and supports easy access to generate group effects as needed in mixed models.
+As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables and errors can be introduced.
 
-A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
-Tools to process result data after the simulation as well as plotting methods for that data are missing.
-Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
+A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R}.
+Still missing but maybe helpful are tools to process the data after the simulation as well as plotting methods for that data.
+Already available are some simple plots for the simulation setups as well as a summary method, to get information on the expected run time and structure of the resulting data.
 
@@
 	\item Link to simFrame?
+	\item parallel computations
+	\item Process the results of a simulation
 \end{itemize}
@@
 	\item Chapter 3 + 4 - what will happen in these chapters?
-	\item kein RBIAS + RRMSE in model-based
 	\item Einleitung 4.2 was ist das ziel der design-basierten simulation

### 2014-10-24 saeSim.Rnw
Überarbeitung von sec 3-4

--- 2014-10-22 saeSim.Rnw
@@
 if(!suppressPackageStartupMessages(require(saeSim))) {
-  if(!require(devtools)) {
-    install.packages("devtools", repos = "http://cran.at.r-project.org/", dependencies = TRUE)
-    library(devtools)
-  }
-
-  install.packages(c("dplyr", "ggplot2", "MASS", "spdep"), 
-                   repos = "http://cran.at.r-project.org/", dependencies = TRUE)
-  install_github("wahani/saeSim")
+  install.packages("saeSim")
+  library(saeSim)
 }
@@
 \end{center}
-\caption{\label{fig:flowdiagram}Process of simulation.} 
+\caption{\label{fig:flowdiagram}Process of simulation. Left column are the steps in a simulation. Right column are the corresponding function names to represent those steps in \proglang{R}} 
 \end{wrapfigure}
 %
-In our opinion simulation studies can best be summarised when understood as a process of data manipulation.
-Thus the main focus of \proglang{saeSim} is to define the steps in that process which can then be \textit{cleanly} defined and repeated.
-Before we go into any detail of the functionality of the package we will discuss the process behind simulation studies and later how \proglang{saeSim} maps this process into \proglang{R}.
+In this section we will present the simulation framework implemented in \proglang{saeSim}.
+The framework relies strongly on the idea to describe a simulation as a process of data manipulation.
+Independent of simulation studies, \cite{wickham14a} as well as \cite{wickham14b} strongly promote this idea by providing tools for cleaning and transforming data.
+In those frameworks every defined function takes a \proglang{data.frame} as input and also returns it modified.
+This leads to a natural connection between all defined functions as the result of one function can be directly passed to the next.
+The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasises the process of data manipulation.
 
-Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level, as illustrated in figure \ref{fig:flowdiagram}.
+In \proglang{saeSim} we want to extend this approach to simulation studies where we have the field of small area estimation in mind.
+The main focus lies on the description of a simulation as a process of data manipulation.
+Each step in this process can be defined as a self contained component (function) and thus easily replaces extended and most importantly reused.
+Before we go into any detail of the functionality of the package we will discuss this process behind simulation studies followed by how \proglang{saeSim} maps this process into \proglang{R}.
+
+Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level.
+Figure \ref{fig:flowdiagram} illustrates these levels.
+In the left column the steps of data manipulation are described, the right column presents the function names to define those steps.
 The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model.
@@
 
-Depending on the topic of research steps in this simulation framework can be more relevant than others or completely irrelevant.
+Depending on the topic of research, steps in this simulation framework can be more relevant than others or completely irrelevant.
 We see these steps more as a complete list of phases one can encounter, thus single components can be omitted if not relevant in specific applications.
@@
 Two layers with separate responsibilities need to be discussed.
-The first is \textit{how} different simulation components can be combined, and the second \textit{when} or in which order they are applied.
+The first is \textit{how} different simulation components can be combined, and the second is \textit{when} or in which order they are applied.
 Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component, which is to use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value.
-This is a widely used approach for data manipulation and promoted recently in the package \proglang{dplyr} \citep{wickham14}.
-This definition of interfaces, the return value of one component is the input of the next, is also used in \proglang{saeSim}.
+This definition of interfaces, the return value of one component is the input of the next, is used for all existing tools in \proglang{saeSim}.
 
-Understanding a simulation as a process of manipulating one data object, see the second column in figure \ref{fig:flowdiagram} how the different steps in a simulation can be accessed.
+The second column in figure \ref{fig:flowdiagram} shows how the different steps in a simulation can be accessed.
 It is important to note that the functions in figure \ref{fig:flowdiagram} control the process, the second layer, i.e.
@@
 Also the second-layer functions have a defined interface: a \proglang{sim\_setup} as input to be modified and a \proglang{sim\_setup} as output.
-Thus, components can be chained together using the \textit{pipe operator} (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14}.
+Thus, components can be chained together using the \textit{pipe operator} (\proglang{\%>\%}) from the package \proglang{magrittr}.
 
@@
 By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
-In the next section we will present a case study and focus more on the concrete functionality provided by the package.
+In the next section we present two case studies and introduce some of the main features provided by the package.
 
-\section{Case study}
-Braking the responsibility into what is applied and when it is applied addresses several aspects of reproducibility.
-First, by defining the interface between all components, it is easy to combine them in any combination and thus easy to share and reuse.
-Second, by controlling when components are applied we avoid the necessity of control structures in syntax and emphasise on the definition of components.
-The following example shows these aspects of the package using a predefined simulation setup:
+\section{Case studies}
+\label{sec:caseStudy}
+We will present two case studies, one model-based simulation in section \ref{sec:csModel} and a design-based simulation in section \ref{sec:csDesign}.
+Before, we want to introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation, if unfamiliar.
+The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
+As a minimal example see the following lines which are equivalent:
 
-<<>>=
+<<eval=FALSE>>=
+sum(1:10)
+1:10 %>% sum
+@
+
+In \proglang{saeSim} we rely on this operator, although all functions can be used without, we strongly recommend to use it. The following example shows some of the aspects of the package:
+
+<<eval=FALSE>>=
 setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
@@
 \proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
-The pipe operator \proglang{\%>\%} is used to add new components to the setup.
-As said before the composition of a simulation in that manner will focus on the definition of components and hide control structures.
-The next example will repeat the simulation stored in \proglang{setup1} two times.
-The results are returned in a list of \proglang{data.frame}s which have five rows as we sample 5 observations:
+Braking the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
+The composition of a simulation in that manner will focus on the definition of components and hide control structures.
+Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} as input as well as return value.
+The only responsibility of that function is to draw a sample, which makes it easy to find, understand and reuse when published.
+The operator \proglang{\%>\%} is used to add new components to the setup.
 
-<<>>=
-setup1 %>% sim(R = 2) %>% sapply(nrow)
-@
-
-As a side remark: The pipe operator, \proglang{\%>\%}, is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
-As a minimal example see the following lines which are equivalent:
-
-<<>>=
-sum(1:10)
-1:10 %>% sum
-@
-
-\label{sec:caseStudy}
 \subsection{Model-based simulation}
-
+\label{sec:csModel}
 <<echo=FALSE>>=
@@
 @
-
-The first task for the model-based simulation is to generate the data under the model:
+In the following we want to show how to construct a simulation in a model-based setting.
+The goal is to estimate the domain predictions under a FH model.
+Components which are involved are \textit{data generation} and \textit{computing on aggregated data}.
+The first step is to generate the data under the model:
 
@@
 Also are $x_i$, $v_i$ and $e_i$ independent from each other.
-The starting point is always a data table as \textit{base-component}, in this case just with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
-Any random number generator in \proglang{R} can be used, however we have a strictly \textit{normal} model, for which some predefined functions can be used.
+The area-level data for the simulation is generated in each Monte Carlo repetition.
+
+In this case the \textit{base-component} is a data table with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
+Any random number generator in \proglang{R} can be used, however we have normally distributed variates, for which some predefined functions are available.
 
@@
 The error component $e_i$ in the model has different variances which is not covered by a predefined function.
-Thus, as a \textit{generator} function we will define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
+Thus, as a \textit{generator component} we define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
 
@@
 
-Not all necessary functions can be provided by the package.
-As said before, one of the main objectives was to define the interface between components.
-To add the area-level predictions from a Fay-Herriot model we need to define a function for that.
+To add the area-level predictions from a Fay-Herriot model we need to define another component.
 The function takes a \proglang{data.frame} as input and returns the modified version.
-Here we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13} to estimate the EBLUP under the FH model.
+For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
 Finally we add \proglang{comp\_FH} to the process:
@@
 The object \proglang{setup} stores all necessary information to run one iteration of the simulation.
-To start more repetitions, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
-We use \proglang{rbind\_all} from the package \proglang{dplyr} to append the resulting \proglang{list}:
+In the following $R = 100$ repetitions are performed, the result is a \proglang{list} of \proglang{data.frame}s.
+The function \proglang{rbind\_all} from the package \proglang{dplyr} is used to combine the resulting \proglang{list}:
 
@@
 
-An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} which purpose is to distinguish between scenarios, should there be more than one.
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios, should there be more than one.
 At this time we do not provide further tools to process the resulting data.
-As it is a \proglang{data.frame} many packages for processing that data are available in \proglang{R}, in this case \proglang{dplyr} \citep{wickham14} and \proglang{reshape2} \citep{wickham07} have been used.
-The Rmd-file for this article can be checked for further detail, thus we do not see need to provide further tools from here on.
-
-%<<echo=FALSE>>=
-%library(reshape2)
-%library(ggplot2)
-%ggDat <- simResults %>% 
-%  melt(id.vars = c("idD", "trueStat"), 
-%       measure.vars = c("FH", "y"), 
-%       variable.name = "method",
-%       value.name = "prediction") %>% 
-%  mutate(RBIAS = (prediction - trueStat)/trueStat,
-%         RRMSE = (prediction - trueStat)^2/trueStat) %>%
-%  group_by(idD, method) %>% 
-%  summarise(RBIAS = mean(RBIAS),
-%            RMSE = mean(RRMSE)) %>%
-%  as.data.frame
-%@
-%
-%<<modelSimBIAS, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
-%ggplot(ggDat, aes(y = RBIAS, x = method)) + geom_boxplot() + coord_flip()
-%@
-%
-%<<modelSimRMSE, echo = FALSE, fig=TRUE, width = 4, height=4, include=FALSE>>=
-%ggplot(ggDat, aes(y = RMSE, x = method)) + geom_boxplot() + coord_flip()
-%@
-
-%\begin{figure}[h!]
-%\begin{subfigure}{.5\textwidth}
-%\centering
-%\includegraphics[width=.9\linewidth]{saeSim-modelSimBIAS.pdf}
-%\caption{}
-%\end{subfigure}
-%\begin{subfigure}{.5\textwidth}
-%\centering
-%\includegraphics[width=.9\linewidth]{saeSim-modelSimRMSE.pdf}
-%\caption{}
-%\end{subfigure}
-%\caption{RBIAS and RMSE for the conducted model-based simulation}
-%\end{figure}
+As it is a \proglang{data.frame} many packages are available in \proglang{R}.
+This point will be presented in more detail in the design-based study.
 
 \subsection{Design-based simulation}
+\label{sec:csDesign}
 
@@
 For this purpose we use a synthetic population generated from Austrian EU-SILC (European Union Statistics on Income and Living Conditions) data.
-We use this data to illustrate the functionality of the package, the data consists of 25 thousand households and does not represent the true population size of Austria.
-It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is used as example data.
+The data consists of 25 thousand households and does not represent the true population size of Austria.
+It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is used as an example data set.
 To keep this study as simple as possible, we further restrict the data for the main income holder and will only use some of the provided auxiliary information.
@@
 
-For the purpose of the design-based case study we want to apply the earlier introduced BHF estimator which is implemented in the \proglang{R}-package \proglang{sae} \citep{molina13}.
-The function we use, \proglang{eblupBHF}, expects three data objects to produce the predictions.
+Using this data as population we want to repeatedly draw samples from it.
+The sampling design is to draw 10 per cent from each region with simple random sampling.
+For each region the direct estimator for income as well as the EBLUP under the BHF model is computed.
+We use the function \proglang{eblupBHF} from the package \proglang{sae} for that.
+This function expects three data objects to produce the predictions.
 The sampled data, the population means of the auxiliary variables and the population sizes in each domain.
-To store these informations and make them available during the simulation we attach them as attributes to the population data.
+Before we can begin to construct the simulation setup we store these data tables as attributes to the population data.
 There are other options but setting attributes to the processed data is supported in the package and presents a very flexible form of processing data on different aggregation levels.
@@
 
-Before we come to the estimation configuration, the first step is to add a sampling scheme.
+Before we come to the estimation, the first step is to add a sampling scheme.
 As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data.
@@
 
-Another positive aspect of the above definitions is, that each step is relatively small and the purpose clearly defined, which will make them easy to understand, modify and reproduce.
-Finally we will combine the simulation results in an \textit{aggregation-component}, possibly followed by the application of area-level models but skipped in this example.
+Another positive aspect of the above definitions is, that each step is relatively small and the purpose clearly defined, which will make them easy to understand and reuse.
+Finally the simulation results are combined in an \textit{aggregation-component}, possibly followed by the application of area-level models but omitted here.
 The result of this aggregation step will be a \proglang{data.frame} with one row for each region.
@@
 
-To repeat the simulation $R$ times the simulation setup can be passed to the function \proglang{sim}, the resulting \proglang{list} is directly combined using \proglang{rbind\_all}.
+To repeat the simulation $R = 50$ times the simulation setup can be passed to the function \proglang{sim}, the resulting \proglang{list} is directly combined using \proglang{rbind\_all}.
 
@@
 
-To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07}.
+To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for further reshaping of the data.
 
 <<>>=
+library(reshape2)
 ggDat <- melt(simResults,
@@
 
-<<designSimBIAS, fig=TRUE, width = 8.3, height=4, include=FALSE>>=
+<<>>=
+library(ggplot2)
+@
+
+<<designSimBIAS, fig = TRUE, width = 8.3, height=4, include = FALSE>>=
 ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 
-\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+%\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
 
-<<designSimMSE, fig=TRUE, width = 8.3, height=4, include=FALSE>>=
+<<designSimMSE, fig=TRUE, width = 8.3, height=4, include = FALSE>>=
 ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 

### 2014-10-24 saeSim.tex
Überarbeitung von sec 3-4

@@
 By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
-In the next section we will present a case study and focus more on the concrete functionality provided by the package.
+In the next section we present two case studies and introduce some of the main features provided by the package.
 
-\section{Case study}
-Braking the responsibility into what is applied and when it is applied addresses several aspects of reproducibility.
-First, by defining the interface between all components, it is easy to combine them in any combination and thus easy to share and reuse.
-Second, by controlling when components are applied we avoid the necessity of control structures in syntax and emphasise on the definition of components.
-The following example shows these aspects of the package using a predefined simulation setup:
+\section{Case studies}
+\label{sec:caseStudy}
+We will present two case studies, one model-based simulation in section \ref{sec:csModel} and a design-based simulation in section \ref{sec:csDesign}.
+Before, we want to introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation, if unfamiliar.
+The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
+As a minimal example see the following lines which are equivalent:
+
+\begin{Schunk}
+\begin{Sinput}
+> sum(1:10)
+> 1:10 %>% sum
+\end{Sinput}
+\end{Schunk}
+
+In \proglang{saeSim} we rely on this operator, although all functions can be used without, we strongly recommend to use it. The following example shows some of the aspects of the package:
 
@@
 \proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
-The pipe operator \proglang{\%>\%} is used to add new components to the setup.
-As said before the composition of a simulation in that manner will focus on the definition of components and hide control structures.
-The next example will repeat the simulation stored in \proglang{setup1} two times.
-The results are returned in a list of \proglang{data.frame}s which have five rows as we sample 5 observations:
+Braking the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
+The composition of a simulation in that manner will focus on the definition of components and hide control structures.
+Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} as input as well as return value.
+The only responsibility of that function is to draw a sample, which makes it easy to find, understand and reuse when published.
+The operator \proglang{\%>\%} is used to add new components to the setup.
 
-\begin{Schunk}
-\begin{Sinput}
-> setup1 %>% sim(R = 2) %>% sapply(nrow)
-\end{Sinput}
-\begin{Soutput}
-[1] 5 5
-\end{Soutput}
-\end{Schunk}
-
-As a side remark: The pipe operator, \proglang{\%>\%}, is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
-As a minimal example see the following lines which are equivalent:
-
-\begin{Schunk}
-\begin{Sinput}
-> sum(1:10)
-\end{Sinput}
-\begin{Soutput}
-[1] 55
-\end{Soutput}
-\begin{Sinput}
-> 1:10 %>% sum
-\end{Sinput}
-\begin{Soutput}
-[1] 55
-\end{Soutput}
-\end{Schunk}
-
-\label{sec:caseStudy}
 \subsection{Model-based simulation}
-
-The first task for the model-based simulation is to generate the data under the model:
+\label{sec:csModel}
+In the following we want to show how to construct a simulation in a model-based setting.
+The goal is to estimate the domain predictions under a FH model.
+Components which are involved are \textit{data generation} and \textit{computing on aggregated data}.
+The first step is to generate the data under the model:
 
@@
 The object \proglang{setup} stores all necessary information to run one iteration of the simulation.
-To start more repetitions, \proglang{sim} is called, which will return $R = 100$ (as the number of repetitions) \proglang{data.frame}s containing the simulated data from each iteration as a \proglang{list}.
-We use \proglang{rbind\_all} from the package \proglang{dplyr} to combine the resulting \proglang{list} into one \proglang{data.frame}:
+In the following $R = 100$ repetitions are performed, the result is a \proglang{list} of \proglang{data.frame}s.
+The function \proglang{rbind\_all} from the package \proglang{dplyr} is used to combine the resulting \proglang{list}:
 
@@
 
-An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} which purpose is to distinguish between scenarios, should there be more than one.
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios, should there be more than one.
 At this time we do not provide further tools to process the resulting data.
-As it is a \proglang{data.frame} many packages for processing that data are available in \proglang{R}, in this case \proglang{dplyr} \citep{wickham14} and \proglang{reshape2} \citep{wickham07} have been used.
-The Rmd-file for this article can be checked for further detail, thus we do not see need to provide further tools from here on.
+As it is a \proglang{data.frame} many packages are available in \proglang{R}.
+This point will be presented in more detail in the design-based study.
 
 \subsection{Design-based simulation}
+\label{sec:csDesign}
 
@@
 
-To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07}.
+To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for further reshaping of the data.
 

### 2014-10-27 saeSim.Rnw

@@
 
-<<>>=
+<<designSimBIAS, fig = TRUE, width = 8.3, height=4, include = FALSE>>=
 library(ggplot2)
-@
-
-<<designSimBIAS, fig = TRUE, width = 8.3, height=4, include = FALSE>>=
 ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 \begin{itemize}
-	\item Chapter 3 + 4 - what will happen in these chapters?
-	\item Einleitung 4.2 was ist das ziel der design-basierten simulation
-	\item Conclusion
+	\item abstract
+	\item farbe flowchart
 \end{itemize}

### 2014-10-27 saeSim.Rnw
paper update

@@
 \Abstract{
-  The abstract of the article in English
-
+  In this article the \proglang{R}-package \proglang{saeSim} is introduced.
+The package provides a simulation framework for studies in the field of small area estimation.
+As the demand for reliable regional estimates from sample surveys has been substantially grown, small area estimation provides statistical methods to produce such reliable predictions when the sample sizes in regions are small.
+Model- and design-based simulations are used to introduce new methods to the field.
+In this artical a reproducible research approach towards the publication of simulation studies alongside articles and during research is promoted.
+The package aims to assist the researcher during the research process and as a vessel to publish new tools and studies.
 }
-\Keywords{package, small area estimation, reproducible research, simulation, \proglang{R}}
-\Plainkeywords{package, small area estimation, reproducible research, simulation, R} %% without formatting
+\Keywords{package, \proglang{R}, reproducible research, simulation, small area estimation}
+\Plainkeywords{package, R, reproducible research, simulation, small area estimation} %% without formatting
 %% at least one keyword must be supplied
@@
 Reproducible research has become a widely discussed topic in many academic areas.
-For instance in the field of statistics, many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
-Publishing source-code and data alongside in an article draws special attention to authoring the analysis.
+In the field of statistics many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
+Publishing source code and data alongside research results draws special attention to authoring the analysis.
 However, the requirements for source code are different from the written words in the article itself.
@@
 Next to the combination of text and source code, reproducible research aims that the full output of the academic research which is the paper combined with the full computational environment like data and source code, is available.
-However, real data is often very sensitive and governed by strictly confidentiality rules.
+However, real data is often very sensitive and governed by strict confidentiality rules.
 Synthetic data generation mechanisms \citep{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.
@@
 This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios.
-In general, statistical simulation studies are divided in the literature into two concepts:
+In general, statistical simulation studies are divided into two concepts:
 \begin{itemize}
@@
 However, simulation studies are often presented very briefly in academic articles without providing enough details about the underlying structure of the study.
-\cite{Alf10} provide a framework (\proglang{simFrame}) which helps the prospective researcher or data analyst to conduct simulation studies in a reproducible environment.
+\cite{Alf10} provide a framework (\proglang{simFrame}) which helps to conduct simulation studies in a reproducible environment.
 The \proglang{R}-package \proglang{simFrame} \citep{Alf10} is an object-oriented tool for statistical simulation studies based on \proglang{S}4 classes.
@@
 
-The aim of this article is to inform the prospective researcher or data analyst of a new \proglang{R}-package (\proglang{simFrame}) which supports the process of making simulation studies reproducible and offers a \textit{human-readable} interface in the field of small area estimation.
+The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible.
 To be more precise, the package has three main objectives: First, provide tools for data generation which are reproducible.
@@
 
-\textcolor{red}{SONSTIGER TEXT:
-The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
-Groups may be areas or other entities, for example defined by socio-economic characteristics.
-New statistical methods are applied in model-based and design-based simulation studies.
-Considering the demands for reproducible research we propose a framework for simulation studies inside the field of small area estimation.}
-
 \section{Small area estimation}
 \label{sec:SAE}
+
 The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
@@
 As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
-This can be achieved by using additional information from census data to assist the prediction for non-sampled domains or domains with little information.
+This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with little information.
 For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese88} and the area-level model introduced by \cite{fay79}.
@@
 where $\indexDomain = 1, \dots, \nDomains$ and $\indexUnit = 1, \dots, \nUnitIndexed$.
-$y_{\indexDomain\indexUnit}$ is the the dependent variable for domain $\indexDomain$ and unit $\indexUnit$, and $\xUnit$ the corresponding auxiliary information for that unit.
+The population of size $N$ is divided into $D$ non-overlapping small areas of sizes $N_i$ and into $n$ sampled and $N-n$ non-sampled units, denoted by $s$ and $r$ respectively.
+$y_{\indexDomain\indexUnit}$ is the the dependent variable for domain $\indexDomain$ and unit $\indexUnit$, and $\xUnit$ are the corresponding auxiliary information for that unit.
 Furthermore $\randomEffect$ and $\samplingError$ are independent.
-This model can be seen as a linear mixed model from which the best linear unbiased predictor (BLUP) can be derived and is used for the domain prediction \citep{rao03}.
+Let $\hat{\beta}$ denote the best linear unbiased estimator (BLUE) of $\beta$ and $\hat{\randomEffectIndexed}$ defines the linear unbiased predictor (BLUP) of $\randomEffectIndexed$ (cf.\ \citealp{Hen50} or \citealp{Sea71}).
+The empirical best linear unbiased predictor (EBLUP) of the mean in small area $i$ in the Battese-Harter-Fuller model is then given by
+\begin{eqnarray}\label{BHFEBLUP}\hat{\overline{y}}_i^{BHF}&=&N_i^{-1}\Big\{\sum_{j\in s_i}y_{ij}+\sum_{j\in r_i}(\xUnit^\top\hat{{\beta}}+\hat{\randomEffectIndexed})\Big\}.
+\end{eqnarray}
 
@@
 %
-where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$ with $\indexDomain = 1, \dots, \nDomains$ and $\nDomains$ being the total number of areas.
+where $\directStat_{\indexDomain}$ is a direct estimator of a statistic of interest $\trueStat_{\indexDomain}$ for an area $\indexDomain$.
 The sampling error $\samplingError_{\indexDomain}$ is assumed to be independent and normally distributed with known variances $\samplingVarianceIndexed$, i.e.
 $\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$.
-The model is modified with the linking model by assuming a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
+The model is modified with a linking model by assuming a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
 %
@@
 Model \ref{eq:FH} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
+The EBLUP of the small area mean in the Fay-Herriot (FH) model is given by
+\begin{eqnarray}\label{FHEBLUP}\hat{\overline{y}}_i^{FH}&=&\xArea^\top \hat{\beta} + \hat{\randomEffectIndexed}.
+\end{eqnarray}
 
@@
 
-%\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
 
@@
 
-%\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
+\includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
 
@@
 
-The package already provides more than introduced in this article and likewise some tools are still missing.
+The package already provides more than introduced in this article.
 To mention is the support of outlier contaminated data.
-At this time only representative outliers (outlying observations in the population) are supported.
+At this time only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
 However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
@@
 A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
-Tools to process result data after the simulation as well as plotting methods for that data are missing.
+Tools to process result data after the simulation as well as plotting methods for that data are an avenue for further research.
 Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
-
-\begin{itemize}
-	\item Link to simFrame?
-\end{itemize}
-
-\section{TODO}
-\begin{itemize}
-	\item abstract
-	\item farbe flowchart
-\end{itemize}
 

### 2014-10-27 saeSim.tex
update flowcharts und todo
paper update

@@
 > library(ggplot2)
-\end{Sinput}
-\end{Schunk}
-
-\begin{Schunk}
-\begin{Sinput}
 > ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 \label{sec:outlook}
-With \proglang{saeSim} have three objects, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
+With \proglang{saeSim} we have three objectives, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
 By providing the package we not only want to make our own tools available but also open it for contributions.
-The package source is available on CRAN \url{somewhere} and the repository for development at \url{https://github.com/wahani/saeSim}.
-As GitHub allows to share and contribute source code using version control, it is open for submissions.
+The package source is available on CRAN (\url{http://cran.r-project.org/web/packages/saeSim/}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
+As GitHub allows to share and contribute source code using version-control, it is open for submissions.
 Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
 One aspect is the design of simulations as processes of data.
-Furthermore by supporting the definition of small and self contained components, i.e.
-functions, as this reduces the lines of code to be read in order to understand it's purpose.
+Furthermore, we encourage the definition of small and self contained components, i.e.
+functions, as this reduces the lines of code necessary to be read in order to understand it's purpose.
 
-The package already provides more than introduced in this article and likewise some tools are still missing.
-The support of outlier contaminated data.
-At this time only representative outliers (outlying observations in the population) are supported.
+The package already provides more than introduced in this article.
+To mention is the support of outlier contaminated data.
+At this time only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
 However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
-The inclusion of available random numbers from the R-language is already possible and supports easy access to generate group effects as needed in mixed models.
-As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables and errors can be introduced.
+Furthermore, the inclusion of available random number generators available in the R-language is already possible and easy access to generate group effects as needed in mixed models is supported.
+Also, as the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
 
-A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R}.
-Still missing but maybe helpful are tools to process the data after the simulation as well as plotting methods for that data.
-Already available are some simple plots for the simulation setups as well as a summary method, to get information on the expected run time and structure of the resulting data.
-
-\begin{itemize}
-	\item Link to simFrame?
-	\item parallel computations
-	\item Process the results of a simulation
-\end{itemize}
-
-\section{TODO}
-\begin{itemize}
-	\item Chapter 3 + 4 - what will happen in these chapters?
-	\item Einleitung 4.2 was ist das ziel der design-basierten simulation
-	\item Conclusion
-\end{itemize}
+A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
+Tools to process result data after the simulation as well as plotting methods for that data are an avenue for further research.
+Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
 

### 2014-10-28 saeSim.Rnw
Update saeSim paper

@@
 The package provides a simulation framework for studies in the field of small area estimation.
-As the demand for reliable regional estimates from sample surveys has been substantially grown, small area estimation provides statistical methods to produce such reliable predictions when the sample sizes in regions are small.
+As the demand for reliable regional estimates from sample surveys has been substantially grown, small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are small.
 Model- and design-based simulations are used to introduce new methods to the field.
@@
 \Address{
+  Timo Schmid\\
+  Department of Economics\\
+  Freie Universit\"at Berlin\\
+  D-14195 Berlin, Germany\\
+  E-mail: \email{Timo.Schmid@fu-berlin.de}\\
+  URL: \url{http://www.wiwiss.fu-berlin.de/fachbereich/vwl/Schmid}\\
+
   Sebastian Warnholz\\
@@
 }
+
 %% It is also possible to add a telephone and fax number
@@
 <<echo=FALSE>>=
-if(!suppressPackageStartupMessages(require(saeSim))) {
-  install.packages("saeSim")
-  library(saeSim)
+loadAndInstallPackage <- function(packageName) {
+  if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
+    install.packages(packageName)
+    eval(substitute(suppressPackageStartupMessages(library(packageName))))
   } 
+}
+loadAndInstallPackage("saeSim")
+# Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr):
+loadAndInstallPackage("sae")
+loadAndInstallPackage("dplyr")
+loadAndInstallPackage("reshape2")
+loadAndInstallPackage("ggplot2")
 @
@@
 \section{Introduction}
-The demand for reliable small area statistics from sample surveys has been substantial grown over the last decades due to their use in public and private sectors.
+The demand for reliable small area statistics from sample surveys has been substantially grown over the last decades due to their use in public and private sectors.
 In this paper we present a framework for simulation studies inside the field of small area estimation.
@@
 
-Reproducible research has become a widely discussed topic in many academic areas.
+Reproducible research has become a widely discussed topic.
 In the field of statistics many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
@@
 \cite{Bur14} interpreted this as an open research philosophy.
-Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework/ simulation.
-This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios.
-In general, statistical simulation studies are divided into two concepts:
+Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework.
+%This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
+In general, statistical simulation studies can be divided into two concepts:
 \begin{itemize}
@@
 
-However, simulation studies are often presented very briefly in academic articles without providing enough details about the underlying structure of the study.
-\cite{Alf10} provide a framework (\proglang{simFrame}) which helps to conduct simulation studies in a reproducible environment.
-The \proglang{R}-package \proglang{simFrame} \citep{Alf10} is an object-oriented tool for statistical simulation studies based on \proglang{S}4 classes.
+%However, simulation studies are often presented very briefly in academic articles without providing enough details about the underlying structure of the study. 
+\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment.
 It includes a wide range of different features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies.
@@
 
-However, the empirical part is also often presented very briefly in the context of small area estimation.
-Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis.
+However, simulation studies in the context of small area estimation is often presented very briefly .
+Thus, we see the need to have a suited framework to guarantee the reproducibility of analysis.
 To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
@@
 The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible.
-To be more precise, the package has three main objectives: First, provide tools for data generation which are reproducible.
+To be more precise, the package has three main objectives: First, provide tools for data generation.
 Second, unify the process of simulation studies.
@@
 This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with little information.
+
 For the purpose of this article we will introduce two basic models frequently used in small area estimation, the unit-level model introduced by \cite{battese88} and the area-level model introduced by \cite{fay79}.
-
 The unit level model \citep{battese88} can be expressed as:
@@
 Furthermore $\randomEffect$ and $\samplingError$ are independent.
-Let $\hat{\beta}$ denote the best linear unbiased estimator (BLUE) of $\beta$ and $\hat{\randomEffectIndexed}$ defines the linear unbiased predictor (BLUP) of $\randomEffectIndexed$ (cf.\ \citealp{Hen50} or \citealp{Sea71}).
+Let $\hat{\beta}$ denote the best linear unbiased estimator (BLUE) of $\beta$ and $\hat{\randomEffectIndexed}$ the best linear unbiased predictor (BLUP) of $\randomEffectIndexed$ (cf.\ \citealp{Hen50} or \citealp{Sea71}).
 The empirical best linear unbiased predictor (EBLUP) of the mean in small area $i$ in the Battese-Harter-Fuller model is then given by
@@
 with $\indexDomain=1,\dots, \nDomains$. 
-Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship.
+%Note that $\xArea$ is a vector containing area-level (aggregated) information for $\nRegressor$ variables and $\beta$ is a vector ($1\times \nRegressor$) of regression coefficients describing the (linear) relationship.
 The model errors $\randomEffectIndexed$ are assumed to be independent and normally distributed, i.e.
@@
 \end{center}
-\caption{\label{fig:flowdiagram}Process of simulation. Left column are the steps in a simulation. Right column are the corresponding function names to represent those steps in \proglang{R}} 
+\caption{\label{fig:flowdiagram}Process of simulation. Left column are the steps in a simulation. Right column are the corresponding function names to represent those steps in \proglang{R}.} 
 \end{wrapfigure}
@@
 Independent of simulation studies, \cite{wickham14a} as well as \cite{wickham14b} strongly promote this idea by providing tools for cleaning and transforming data.
-In those frameworks every defined function takes a \proglang{data.frame} as input and also returns it modified.
-This leads to a natural connection between all defined functions as the result of one function can be directly passed to the next.
+In those frameworks every defined function takes a \proglang{data.frame} as input and returns it modified.
+This leads to a natural connection between all defined functions as the result of one function can be directly passed to the next as an argument.
 The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasises the process of data manipulation.
@@
 The main focus lies on the description of a simulation as a process of data manipulation.
-Each step in this process can be defined as a self contained component (function) and thus easily replaces extended and most importantly reused.
+Each step in this process can be defined as a self contained component (function) and thus easily replaced, extended and most importantly reused.
 Before we go into any detail of the functionality of the package we will discuss this process behind simulation studies followed by how \proglang{saeSim} maps this process into \proglang{R}.
@@
 The \textit{base} (first component in figure \ref{fig:flowdiagram}) of any simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over the course of the simulation.
-Or from a more technical point of view, is the data generation (the second step in figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted?
-
+Or from a more technical point of view, is the data generation (the second step in figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted.
 Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in figure \ref{fig:flowdiagram}).
@@
 Before, we want to introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation, if unfamiliar.
-The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead of inside out \citep{bache14}.
+The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
 As a minimal example see the following lines which are equivalent:
@@
 The goal is to estimate the domain predictions under a FH model.
-Components which are involved are \textit{data generation} and \textit{computing on aggregated data}.
+Components which are involved are \textit{data generation} and \textit{computing on aggregated data} (see figure \ref{fig:flowdiagram}).
 The first step is to generate the data under the model:
@@
 
-<<results=hide>>=
+<<>>=
 library(saeSim)
-@
-<<>>=
 setup <- base_id(nDomains = 40, nUnits = 1) %>% 
@@
 
-Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows of the resulting data table are printed.
+Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows (the head) of the resulting data table are printed.
 This enables interactivity with the object itself, however it hides that the setup object is a collection of functions to be called.
-The error component $e_i$ in the model has different variances which is not covered by a predefined function.
+In this model the error component $e_i$ has different variances which is not covered by a predefined function.
 Thus, as a \textit{generator component} we define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
-Finally we add \proglang{comp\_FH} to the process:
+Hence we define a function named \proglang{comp\_FH} and add it to the process:
 
-<<results=hide>>=
+<<>>=
 library(sae)
-@
-<<>>=
 comp_FH <- function(dat) {
@@
 
-<<results=hide>>=
+<<>>=
 library(dplyr)
-@
-<<>>=
 simResults <- sim(setup, R = 100) %>% rbind_all
@@
 As it is a \proglang{data.frame} many packages are available in \proglang{R}.
-This point will be presented in more detail in the design-based study.
+In the design-based scenario we show how to process the result data into graphs with only a few lines of code.
 
@@
 
-Using this data as population we want to repeatedly draw samples from it.
+Using this data as population, we want to repeatedly draw samples from it, then predict the domain means by using a direct estimator and a unit-level model.
 The sampling design is to draw 10 per cent from each region with simple random sampling.
 For each region the direct estimator for income as well as the EBLUP under the BHF model is computed.
-We use the function \proglang{eblupBHF} from the package \proglang{sae} for that.
-This function expects three data objects to produce the predictions.
+Although the data offers some more information, we use only \proglang{gender}, \proglang{age} and \proglang{agesq} as predictor variables.
+The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator and used as an example.
+This function expects three data objects and returns domain predictions.
 The sampled data, the population means of the auxiliary variables and the population sizes in each domain.
 Before we can begin to construct the simulation setup we store these data tables as attributes to the population data.
-There are other options but setting attributes to the processed data is supported in the package and presents a very flexible form of processing data on different aggregation levels.
+There are other options but setting attributes to the processed data is a very flexible form of processing data on different aggregation levels.
 
@@
 Another positive aspect of the above definitions is, that each step is relatively small and the purpose clearly defined, which will make them easy to understand and reuse.
-Finally the simulation results are combined in an \textit{aggregation-component}, possibly followed by the application of area-level models but omitted here.
+Finally the simulation results are combined in an \textit{aggregation-component}, possibly followed by the application of area-level models but omitted in this example.
 The result of this aggregation step will be a \proglang{data.frame} with one row for each region.
@@
 
-To further process the simulation results we present two graphics, using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for further reshaping of the data.
+To further process the simulation results we present two plots using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for further reshaping of the data.
+As can be seen, little effort is needed to process the result data.
+Figure \ref{fig:dbBIAS} and \ref{fig:dbMSE} show the Monte-Carlo BIAS and MSE for each region in Austria and for each estimator.
+Keep in mind that the BHF was applied to illustrate the simulation framework.
+There are a number of issues with regard to model choice and variable selection which we will not address any further.
 
@@
 
-<<designSimBIAS, fig = TRUE, width = 8.3, height=4, include = FALSE>>=
+<<eval=FALSE>>=
+library(ggplot2)
+ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
+  geom_boxplot() + theme(legend.position = "bottom")
+ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
+  geom_boxplot() + scale_y_log10() + theme(legend.position = "bottom")
+@
+
+<<designSimBIAS, fig = TRUE, width = 8.3, height=4, include = FALSE, echo = FALSE>>=
 library(ggplot2)
@@
 
+\begin{figure}[!h]
 \includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+\caption{Monte-Carlo BIAS of direct vs. BHF predictor. 50 predictions for each region and estimation technique.}
+\label{fig:dbBIAS}
+\end{figure}
 
-<<designSimMSE, fig=TRUE, width = 8.3, height=4, include = FALSE>>=
+<<designSimMSE, fig=TRUE, width = 8.3, height=4, include = FALSE, echo = FALSE>>=
 ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
@@
 
+\begin{figure}[!h]
 \includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
+\caption{Monte Carlo MSE of direct vs. BHF predictor. 50 predictions for each region and estimation technique.}
+\label{fig:dbMSE}
+\end{figure}
 
@@
 At this time only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
-However, we plan to extend this approach for non-representative outliers (outliers are part of the sample but not the population).
-Furthermore, the inclusion of available random number generators available in the R-language is already possible and easy access to generate group effects as needed in mixed models is supported.
+However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population).
+Furthermore, the inclusion of available random number generators available in the R-language is already possible and access to generate group effects as needed in mixed models is supported.
 Also, as the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.

### 2014-10-28 saeSim.tex
Update saeSim paper

@@
 > library(saeSim)
-\end{Sinput}
-\end{Schunk}
-\begin{Schunk}
-\begin{Sinput}
 > setup <- base_id(nDomains = 40, nUnits = 1) %>% 
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
-Finally we add \proglang{comp\_FH} to the process:
+Hence we define a function named \proglang{comp\_FH} and add it to the process:
 
@@
 > library(sae)
-\end{Sinput}
-\end{Schunk}
-\begin{Schunk}
-\begin{Sinput}
 > comp_FH <- function(dat) {
@@
 > library(dplyr)
-\end{Sinput}
-\end{Schunk}
-\begin{Schunk}
-\begin{Sinput}
 > simResults <- sim(setup, R = 100) %>% rbind_all
@@
 +   geom_boxplot() + theme(legend.position = "bottom")
-\end{Sinput}
-\end{Schunk}
-
-\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
-
-\begin{Schunk}
-\begin{Sinput}
 > ggplot(ggDat, aes(x = region, y = (prediction - trueStat)^2, fill = method)) + 
@@
 
+\begin{figure}[!h]
+\includegraphics[width = \textwidth]{saeSim-designSimBIAS.pdf}
+\caption{Monte-Carlo BIAS of direct vs. BHF predictor. 50 predictions for each region and estimation technique.}
+\label{fig:dbBIAS}
+\end{figure}
+
+\begin{figure}[!h]
 \includegraphics[width = \textwidth]{saeSim-designSimMSE.pdf}
+\caption{Monte Carlo MSE of direct vs. BHF predictor. 50 predictions for each region and estimation technique.}
+\label{fig:dbMSE}
+\end{figure}
 

### 2014-10-31 saeSim.Rnw
update Paper saeSim

@@
 \usepackage{subcaption}
+\newcommand{\red}[1]{\color{red} #1 \color{black} }
 
@@
 \Abstract{
-  In this article the \proglang{R}-package \proglang{saeSim} is introduced.
-The package provides a simulation framework for studies in the field of small area estimation.
-As the demand for reliable regional estimates from sample surveys has been substantially grown, small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are small.
-Model- and design-based simulations are used to introduce new methods to the field.
-In this artical a reproducible research approach towards the publication of simulation studies alongside articles and during research is promoted.
-The package aims to assist the researcher during the research process and as a vessel to publish new tools and studies.
+The demand for reliable regional estimates from sample surveys has been substantially grown over the last decades.
+Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators.
+Model- and design-based simulations are used to gain insights into the quality of the introduced methods.
+In this article we present a framework which may help to guarantee the reproducibility of simulation studies in articles and during research.
+The introduced \proglang{R}-package \proglang{saeSim} is adjusted to provide a simulation environment for the special case of small area estimation.
+The package may allow the prospective researcher during the research process to produce simulation studies with a minimal effort of coding.
 }
-\Keywords{package, \proglang{R}, reproducible research, simulation, small area estimation}
+
+\Keywords{Package, \proglang{R}, reproducible research, simulation study, small area estimation}
 \Plainkeywords{package, R, reproducible research, simulation, small area estimation} %% without formatting
@@
 Reproducible research has become a widely discussed topic.
-In the field of statistics many mostly open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
+In the field of statistics many open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
 Publishing source code and data alongside research results draws special attention to authoring the analysis.
@@
 
-Next to the combination of text and source code, reproducible research aims that the full output of the academic research which is the paper combined with the full computational environment like data and source code, is available.
+Next to the combination of text and source code, reproducible research aims that the full output of the academic research, which is the paper combined with the full computational environment like data and source code, is available.
 However, real data is often very sensitive and governed by strict confidentiality rules.
@@
 %This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
-In general, statistical simulation studies can be divided into two concepts:
+In general, \red{simulation studies in statistics} can be divided into two concepts:
+%
 \begin{itemize}
@@
 
-%However, simulation studies are often presented very briefly in academic articles without providing enough details about the underlying structure of the study. 
 \cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment.
@@
 
-However, simulation studies in the context of small area estimation is often presented very briefly .
-Thus, we see the need to have a suited framework to guarantee the reproducibility of analysis.
+However, simulation studies in the context of small area estimation is often presented very briefly.
+Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis.
 To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
@@
 Section \ref{sec:framework} introduces a framework for simulation studies and how it is supported by the  \proglang{R}-package \proglang{saeSim}.
-To illustrate some of the features of the package we present a case study in Section \ref{sec:caseStudy}.
+To illustrate some of the features of the package we present a model- and design-based simulation study in Section \ref{sec:caseStudy}.
 We conclude the paper in Section \ref{sec:outlook} by summarising the main findings and by providing some avenues for further research.
@@
 
-The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where little or no sampled units are available.
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where less or no sampled units are available.
 Groups may be areas or other entities, for example defined by socio-economic characteristics.
 The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
-As direct estimation of such statistics are considered to be unreliable, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
-This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with little information.
+As direct estimation of such statistics are considered to be unreliable \red{(with respect to MSE)}, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
+This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.
 
@@
 	\randomEffectIndexed \stackrel{iid}{\sim}& N(0, \randomEffectVariance)  \nonumber \\
-	\samplingErrorUnitIndexed \stackrel{iid}{\sim}& N(0, \samplingVariance) \nonumber
+	\samplingErrorUnitIndexed \stackrel{iid}{\sim}& N(0, \samplingVariance) \nonumber,
 \end{eqnarray}
@@
 The population of size $N$ is divided into $D$ non-overlapping small areas of sizes $N_i$ and into $n$ sampled and $N-n$ non-sampled units, denoted by $s$ and $r$ respectively.
-$y_{\indexDomain\indexUnit}$ is the the dependent variable for domain $\indexDomain$ and unit $\indexUnit$, and $\xUnit$ are the corresponding auxiliary information for that unit.
+$y_{\indexDomain\indexUnit}$ is the dependent variable for domain $\indexDomain$ and unit $\indexUnit$, and $\xUnit$ are the corresponding auxiliary information for that unit.
 Furthermore $\randomEffect$ and $\samplingError$ are independent.
 Let $\hat{\beta}$ denote the best linear unbiased estimator (BLUE) of $\beta$ and $\hat{\randomEffectIndexed}$ the best linear unbiased predictor (BLUP) of $\randomEffectIndexed$ (cf.\ \citealp{Hen50} or \citealp{Sea71}).
-The empirical best linear unbiased predictor (EBLUP) of the mean in small area $i$ in the Battese-Harter-Fuller model is then given by
+The empirical best linear unbiased predictor (EBLUP) for the mean in small area $i$ in the Battese-Harter-Fuller model is then given by
 \begin{eqnarray}\label{BHFEBLUP}\hat{\overline{y}}_i^{BHF}&=&N_i^{-1}\Big\{\sum_{j\in s_i}y_{ij}+\sum_{j\in r_i}(\xUnit^\top\hat{{\beta}}+\hat{\randomEffectIndexed})\Big\}.
@@
 Due to reasons of confidentiality unit-level information is not always available.
-Instead only aggregates, or rather the direct estimators may be supplied.
-However, these direct estimations are known to be unreliable, hence in such situations area-level models can be valuable.
+Instead only aggregates \red{for the domains or direct estimators may be supplied}.
+In this case the feasible direct estimates are known to be unreliable in the case of small sample sizes.
+Here area-level models can be valuable.
 The area-level model introduced by \cite{fay79} is build on a sampling model:
@@
 $\samplingError_{\indexDomain}|\trueStat_{\indexDomain} \sim \mathit{N}(0, \samplingVarianceIndexed)$.
-The model is modified with a linking model by assuming a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
+The model assumes a linear relationship between the true area statistic $\trueStat_{\indexDomain}$ and some auxiliary variables $\xArea$:
 %
@@
 %
-Model \ref{eq:FH} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
-The EBLUP of the small area mean in the Fay-Herriot (FH) model is given by
+\red{Fay-Herriot (FH) model (equation \ref{eq:FH})} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
+The EBLUP of the small area mean in the FH model is given by
 \begin{eqnarray}\label{FHEBLUP}\hat{\overline{y}}_i^{FH}&=&\xArea^\top \hat{\beta} + \hat{\randomEffectIndexed}.
@@
 The framework relies strongly on the idea to describe a simulation as a process of data manipulation.
-Independent of simulation studies, \cite{wickham14a} as well as \cite{wickham14b} strongly promote this idea by providing tools for cleaning and transforming data.
+Independent of simulation studies, \cite{wickham14a} and \cite{wickham14b} strongly promote this idea by providing tools for cleaning and transforming data.
 In those frameworks every defined function takes a \proglang{data.frame} as input and returns it modified.
@@
 The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasises the process of data manipulation.
+\red{To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (see section \ref{sec:caseStudy} for an example).}
 
-In \proglang{saeSim} we want to extend this approach to simulation studies where we have the field of small area estimation in mind.
+In \proglang{saeSim} we extend this approach to simulation studies in the field of small area estimation.
 The main focus lies on the description of a simulation as a process of data manipulation.
-Each step in this process can be defined as a self contained component (function) and thus easily replaced, extended and most importantly reused.
-Before we go into any detail of the functionality of the package we will discuss this process behind simulation studies followed by how \proglang{saeSim} maps this process into \proglang{R}.
+Each step in this process can be defined as a self contained component (function) and thus can be easily replaced, extended and most importantly reused.
+Before we go into \red{details of the functionality of the package we discuss the process behind simulation studies} followed by how \proglang{saeSim} maps this process into \proglang{R}.
 
@@
 Figure \ref{fig:flowdiagram} illustrates these levels.
-In the left column the steps of data manipulation are described, the right column presents the function names to define those steps.
+The left column describes the steps of data manipulation, the right column presents the function names to define the corresponding steps.
 The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model.
-We see three different point of views to define a population.
-First \textit{design-based}, which means that a simulation study is based on true or synthetic data of \textit{one} population.
-Second a \textit{semi-model-based} point of view, where only one population is drawn from a model and is fixed in the whole simulation study.
-And third, \textit{model-based} studies which have changing random populations drawn from a model.
+\red{We see} two different point of views to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population.
+Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.
 
-The scope of this article is not not to promote any of those viewpoints, but simply to identify the similarity in them.
-The \textit{base} (first component in figure \ref{fig:flowdiagram}) of any simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over the course of the simulation.
-Or from a more technical point of view, is the data generation (the second step in figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted.
-Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in figure \ref{fig:flowdiagram}).
+The scope of this article is not to promote any of those viewpoints, we just want to incorporate the different simulation concepts in a common framework.
+The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over simulations.
+Or from a more technical point of view, is the data generation (the second step in Figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted.
+Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).
 
-The \textbf{sample-level} is when domain predictions are conducted for unit-level models.
-Independently of how the population is treated, fixed or random, this phase consists of two steps, first drawing a sample, and second conducting computations on the samples (fourth and fifth component in figure \ref{fig:flowdiagram}).
-Given a sample, design or model based small area methods are applied.
-Of interest are estimated parameters, which can be estimated model parameters or domain predictions as well as measures of uncertainty for the estimates.
+The \textbf{sample-level} is necessary when domain predictions are conducted for unit-level models.
+Independently of how the population is treated, fixed or random, this phase consists of two steps: Firstly, draw a sample according to a specific sampling scheme.
+Secondly, conduct computations on the samples (fourth and fifth component in Figure \ref{fig:flowdiagram}).
+Given a sample, small area methods are applied.
+Of interest are, for instance, estimated model parameters, domain predictions or measures of uncertainty (MSE) for the estimates.
 
-As the sample-level is when unit-level models are applied, the \textbf{aggregate-level} is when area-level models are applied (the seventh and last component in figure \ref{fig:flowdiagram}).
+As the sample-level is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}).
 Area-level models in small area estimation typically only use information available for domains (in contrast to units).
-Thus, the question for simulation studies for area-level methods is, if the data is generated on unit-level and used after the aggregation (sixth component in figure \ref{fig:flowdiagram}) or if the data is generated directly on area-level, i.e.
+Thus, the question for simulation studies for area-level methods is, if the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or if the data is generated directly on area-level, i.e.
 drawn from an area-level model.
-Depending on whether unit-level data and sampling are part of the simulation the aggregate-level follows the generation of the population or is based on the aggregated sample.
-Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.
+Depending on whether unit-level data and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample.
+%Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.
 
-Depending on the topic of research, steps in this simulation framework can be more relevant than others or completely irrelevant.
-We see these steps more as a complete list of phases one can encounter, thus single components can be omitted if not relevant in specific applications.
+Depending on the topic of research, \red{some} steps in this simulation framework can be more relevant than others.
+From our perspective, these steps are more a complete list of phases one can conduct.
+Single components may be omitted if not relevant in specific applications.
 For example \textit{data generation} is not relevant if you have population data, or the \textit{sample-level} is not used, when the sample is directly drawn from the model.
@@
 Two layers with separate responsibilities need to be discussed.
-The first is \textit{how} different simulation components can be combined, and the second is \textit{when} or in which order they are applied.
-Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component, which is to use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value.
+The first is \textit{how} different simulation components can be combined, \red{and the second is \textit{when}} they are applied.
+Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component.
+To be precise, we use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value.
 This definition of interfaces, the return value of one component is the input of the next, is used for all existing tools in \proglang{saeSim}.
-
-The second column in figure \ref{fig:flowdiagram} shows how the different steps in a simulation can be accessed.
-It is important to note that the functions in figure \ref{fig:flowdiagram} control the process, the second layer, i.e.
+The second column in Figure \ref{fig:flowdiagram} shows how the different steps in a simulation can be accessed.
+It is important to note that the functions in Figure \ref{fig:flowdiagram} control the process, the second layer, i.e.
 \textit{when} components are applied.
 Each of these functions take a simulation setup object to be modified and a function with the discussed interface as arguments.
-Hence a simulation setup is a collection of functions to be applied in a certain sequence.
-Also the second-layer functions have a defined interface: a \proglang{sim\_setup} as input to be modified and a \proglang{sim\_setup} as output.
-Thus, components can be chained together using the \textit{pipe operator} (\proglang{\%>\%}) from the package \proglang{magrittr}.
-
-With \proglang{saeSim} we want to contribute tools for simulation studies in the field of small area estimation.
-We see the need for sharing tools for data generation and simulation amongst the scientific community and thus defined an interface for these tools as well as a platform to make them accessible.
-By defining the steps behind a simulation we hope to promote a reasonable way to communicate them alongside publications and during research.
-In the next section we present two case studies and introduce some of the main features provided by the package.
+Hence, \red{the pipe operator (\proglang{\%>\%}) can be used to combine components to a simulation setup.}
 
@@
 \label{sec:caseStudy}
-We will present two case studies, one model-based simulation in section \ref{sec:csModel} and a design-based simulation in section \ref{sec:csDesign}.
-Before, we want to introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation, if unfamiliar.
+We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}.
+Before, we introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation.
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
@@
 
-Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we can see that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme.
+Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we notice that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme.
 \proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
-Braking the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
+\red{Separating} the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
 The composition of a simulation in that manner will focus on the definition of components and hide control structures.
@@
 @
-In the following we want to show how to construct a simulation in a model-based setting.
-The goal is to estimate the domain predictions under a FH model.
-Components which are involved are \textit{data generation} and \textit{computing on aggregated data} (see figure \ref{fig:flowdiagram}).
+In the following we show one way how to construct a simulation in a model-based setting.
+The aim is to estimate the domain predictions under a FH model.
+Involved components are \textit{data generation} and \textit{computing on aggregated data} (cf.
+Figure \ref{fig:flowdiagram}).
 The first step is to generate the data under the model:
 
-\[ y_i = 100 + 2 \cdot x_i + v_i + e_i\]
+\[ y_i = 100 + 2 \cdot x_i + v_i + e_i,\]
 
 where $x_i \stackrel{iid}{\sim} N(0, 4^2)$, $v_i \stackrel{iid}{\sim} N(0, 1)$ and $e_i \stackrel{indep}{\sim} N(0, \sigma_i^2)$ with $\sigma_i^2 = 0.1, 0.2, \dots, 4$ and $i = 1, \dots, 40$ as index for the domains.
-Also are $x_i$, $v_i$ and $e_i$ independent from each other.
-The area-level data for the simulation is generated in each Monte Carlo repetition.
+$x_i$, $v_i$ and $e_i$ are independent from each other.
+The area-level data for the simulation is generated in each Monte Carlo replication.
 
 In this case the \textit{base-component} is a data table with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
-Any random number generator in \proglang{R} can be used, however we have normally distributed variates, for which some predefined functions are available.
+Any random number generator in \proglang{R} can be used.
+However, we have normally distributed variates, for which some predefined functions are available in the package.
 
@@
 Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows (the head) of the resulting data table are printed.
-This enables interactivity with the object itself, however it hides that the setup object is a collection of functions to be called.
+This enables interactivity with the object itself, however, it hides that the setup object is a collection of functions to be called.
 In this model the error component $e_i$ has different variances which is not covered by a predefined function.
-Thus, as a \textit{generator component} we define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
+Thus, as a \textit{generator component}, we define a function which takes a \proglang{data.frame} as input and returns it after adding a variable named \proglang{vardir} with the variances and the variable \proglang{e} with the generated random numbers:
 
@@
 
-The last step in data generation is to construct the response variable which will be named \proglang{y} and added to the data.
-Also we will add the \textit{true} area statistic under the model to the data:
+The last step in data generation is to construct the response variable which is named \proglang{y} and is added to the data.
+Furthermore, we add the \textit{true} area statistic under the model to the data:
 
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
-Hence we define a function named \proglang{comp\_FH} and add it to the process:
+Hence, we define a function named \proglang{comp\_FH} and add it to the process:
 
@@
 The object \proglang{setup} stores all necessary information to run one iteration of the simulation.
-In the following $R = 100$ repetitions are performed, the result is a \proglang{list} of \proglang{data.frame}s.
+In the following $R = 100$ repetitions are performed.
+The result is a \proglang{list} of \proglang{data.frame}s.
 The function \proglang{rbind\_all} from the package \proglang{dplyr} is used to combine the resulting \proglang{list}:
@@
 
-An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios, should there be more than one.
+An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios.
 At this time we do not provide further tools to process the resulting data.
-As it is a \proglang{data.frame} many packages are available in \proglang{R}.
+Many packages are available in \proglang{R} to handle \proglang{data.frame}.
 In the design-based scenario we show how to process the result data into graphs with only a few lines of code.
@@
 
-In the design-based simulation we want to illustrate the use of \proglang{saeSim} when starting from data of a population.
+In the design-based simulation we illustrate the use of \proglang{saeSim} under a fixed population.
 For this purpose we use a synthetic population generated from Austrian EU-SILC (European Union Statistics on Income and Living Conditions) data.
-The data consists of 25 thousand households and does not represent the true population size of Austria.
-It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is used as an example data set.
-To keep this study as simple as possible, we further restrict the data for the main income holder and will only use some of the provided auxiliary information.
+The data consists of 25 thousand households.
+It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is also used as an example data set.
+To keep this study as simple as possible, we further restrict the data on the main income holder and only use some of the provided auxiliary information.
 
@@
 
-Using this data as population, we want to repeatedly draw samples from it, then predict the domain means by using a direct estimator and a unit-level model.
-The sampling design is to draw 10 per cent from each region with simple random sampling.
-For each region the direct estimator for income as well as the EBLUP under the BHF model is computed.
-Although the data offers some more information, we use only \proglang{gender}, \proglang{age} and \proglang{agesq} as predictor variables.
-The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator and used as an example.
+Using this data as population, we repeatedly draw samples from it.
+Then we predict the domain means by using a direct estimator and a unit-level model.
+The sampling design is to draw a 10 per cent sample from each region with simple random sampling.
+For each region the direct estimator for income and the EBLUP under the BHF model is computed.
+Although the data offers some more information, we only use \proglang{gender}, \proglang{age} and \proglang{agesq} as covariates.
+The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator.
 This function expects three data objects and returns domain predictions.
-The sampled data, the population means of the auxiliary variables and the population sizes in each domain.
-Before we can begin to construct the simulation setup we store these data tables as attributes to the population data.
-There are other options but setting attributes to the processed data is a very flexible form of processing data on different aggregation levels.
+The three objects are the sampled data, the population means of the auxiliary variables and the population sizes in each domain.
+Before we begin to construct the simulation setup, we store these data tables as attributes to the population data.
+There are other options but \red{adding attributes to the data} is a very flexible form of processing data on different aggregation levels.
 
@@
 As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data.
-Then the sampling component is added, in which we define to draw 10 per cent of the observations from each domain with simple random sampling.
+Then the sampling component is added, in which we define to draw 10 per cent sample of the observations from each domain with simple random sampling.
 
@@
 
-What now needs to be done, is to define the components which add the desired estimates to the data.
-Here we will compute the mean of income in each domain as the direct estimator and the EBLUP under the BHF model.
-Although this could be done in one step, we will separate the two computations to illustrate how to combine several estimations and define each component independent of one another.
-This focus on the definition of each component and meeting the convention of the defined interface is the intended approach.
-It will automatically organise the simulation and each component is arranged using the simulation framework.
-Hence, we will define two functions, one for adding the direct estimates and one for adding the EBLUP.
+In the next step, we define components which \red{add the estimates of interest} to the data.
+Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
+Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other.
+This focus on the definition of each component and  on meeting the convention of the defined interface is the intended approach.
+It automatically organises the simulation and each component is arranged using the simulation framework.
+Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
 
@@
 
-Another positive aspect of the above definitions is, that each step is relatively small and the purpose clearly defined, which will make them easy to understand and reuse.
-Finally the simulation results are combined in an \textit{aggregation-component}, possibly followed by the application of area-level models but omitted in this example.
-The result of this aggregation step will be a \proglang{data.frame} with one row for each region.
+\red{A positive} aspect of the above definitions is, that the code for each step is relatively short and the purpose is clearly defined.
+This may help to improve readability and to reproduce the research.
+Finally, the simulation results are combined in an \textit{aggregation-component}, possibly followed by the application of area-level models.
+The result of this aggregation step is a \proglang{data.frame} with one row for each region.
 
@@
 
-To repeat the simulation $R = 50$ times the simulation setup can be passed to the function \proglang{sim}, the resulting \proglang{list} is directly combined using \proglang{rbind\_all}.
+To repeat the simulation $R = 50$ times the simulation setup is passed to the function \proglang{sim}. The resulting \proglang{list} is directly combined using \proglang{rbind\_all}.
 
@@
 To further process the simulation results we present two plots using the package \proglang{ggplot2} \citep{wickham09} and \proglang{reshape2} \citep{wickham07} for further reshaping of the data.
-As can be seen, little effort is needed to process the result data.
 Figure \ref{fig:dbBIAS} and \ref{fig:dbMSE} show the Monte-Carlo BIAS and MSE for each region in Austria and for each estimator.
 Keep in mind that the BHF was applied to illustrate the simulation framework.
-There are a number of issues with regard to model choice and variable selection which we will not address any further.
+There are a number of issues with regard to model choice, variable selection and outliers, which we will not discuss in this context.
 
@@
 \end{figure}
+\clearpage
 
@@
 \label{sec:outlook}
-With \proglang{saeSim} we have three objectives, making simulation tools available and reusable, unify the process behind simulations and third assist the researcher to design her code in a transparent way.
-By providing the package we not only want to make our own tools available but also open it for contributions.
+From our perspective, \red{there is a the need} for sharing tools for data generation and simulation amongst the scientific community to guarantee the reproducibility of research.
+\red{\proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation.
+By defining the steps of a simulation we may promote a reasonable way to communicate results in academic articles and during research.}
+
 The package source is available on CRAN (\url{http://cran.r-project.org/web/packages/saeSim/}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
 As GitHub allows to share and contribute source code using version-control, it is open for submissions.
-Apart from the availability of specific utility functions, we hope to promote and support the design of source code for simulation studies.
+Apart from the availability of specific utility functions, we may promote and support the design of source code for simulation studies.
 One aspect is the design of simulations as processes of data.
 Furthermore, we encourage the definition of small and self contained components, i.e.
-functions, as this reduces the lines of code necessary to be read in order to understand it's purpose.
+functions.
+This reduces the lines of code necessary to be read in order to understand it's purpose.
 
-The package already provides more than introduced in this article.
+The package provides more features than introduced in this article.
 To mention is the support of outlier contaminated data.
@@
 However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population).
-Furthermore, the inclusion of available random number generators available in the R-language is already possible and access to generate group effects as needed in mixed models is supported.
-Also, as the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
+\red{Furthermore, an interface to random number generators available in the R-language is available.} The user can also generate group effects as needed in mixed models.
+As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
 
 A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
-Tools to process result data after the simulation as well as plotting methods for that data are an avenue for further research.
-Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
+\red{Tools to process result data after the simulation, i.e.
+summaries as well as plotting methods, are an avenue for further research.} Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
 

### 2014-10-31 saeSim.tex
update Paper saeSim

@@
 \label{sec:csModel}
-In the following we want to show how to construct a simulation in a model-based setting.
-The goal is to estimate the domain predictions under a FH model.
-Components which are involved are \textit{data generation} and \textit{computing on aggregated data} (see figure \ref{fig:flowdiagram}).
+In the following we show one way how to construct a simulation in a model-based setting.
+The aim is to estimate the domain predictions under a FH model.
+Involved components are \textit{data generation} and \textit{computing on aggregated data} (cf.
+Figure \ref{fig:flowdiagram}).
 The first step is to generate the data under the model:
 
-\[ y_i = 100 + 2 \cdot x_i + v_i + e_i\]
+\[ y_i = 100 + 2 \cdot x_i + v_i + e_i,\]
 
 where $x_i \stackrel{iid}{\sim} N(0, 4^2)$, $v_i \stackrel{iid}{\sim} N(0, 1)$ and $e_i \stackrel{indep}{\sim} N(0, \sigma_i^2)$ with $\sigma_i^2 = 0.1, 0.2, \dots, 4$ and $i = 1, \dots, 40$ as index for the domains.
-Also are $x_i$, $v_i$ and $e_i$ independent from each other.
-The area-level data for the simulation is generated in each Monte Carlo repetition.
+$x_i$, $v_i$ and $e_i$ are independent from each other.
+The area-level data for the simulation is generated in each Monte Carlo replication.
 
 In this case the \textit{base-component} is a data table with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
-Any random number generator in \proglang{R} can be used, however we have normally distributed variates, for which some predefined functions are available.
+Any random number generator in \proglang{R} can be used.
+However, we have normally distributed variates, for which some predefined functions are available in the package.
 

### 2015-01-12 saeSim.Rnw
saeSim-Paper: 1st submission

@@
 \usepackage{subcaption}
-\newcommand{\red}[1]{\color{red} #1 \color{black} }
 
@@
 %This may provide valuable insights about the quality of the introduced methods in a controlled environment under different scenarios. 
-In general, \red{simulation studies in statistics} can be divided into two concepts:
+In general, simulation studies in statistics can be divided into two concepts:
 %
@@
 The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
-As direct estimation of such statistics are considered to be unreliable \red{(with respect to MSE)}, methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
+As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
 This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.
@@
 Due to reasons of confidentiality unit-level information is not always available.
-Instead only aggregates \red{for the domains or direct estimators may be supplied}.
+Instead only aggregates for the domains or direct estimators may be supplied.
 In this case the feasible direct estimates are known to be unreliable in the case of small sample sizes.
@@
 %
-\red{Fay-Herriot (FH) model (equation \ref{eq:FH})} is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
+The Fay-Herriot (FH) model in (\ref{eq:FH}) is effectively a random-intercept model where the distribution of the error term $\samplingErrorIndexed$ is heterogeneous and known.
 The EBLUP of the small area mean in the FH model is given by
@@
 The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasises the process of data manipulation.
-\red{To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (see section \ref{sec:caseStudy} for an example).}
+To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (cf.
+Section \ref{sec:caseStudy}).
 
@@
 Each step in this process can be defined as a self contained component (function) and thus can be easily replaced, extended and most importantly reused.
-Before we go into \red{details of the functionality of the package we discuss the process behind simulation studies} followed by how \proglang{saeSim} maps this process into \proglang{R}.
+Before we go into details of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.
 
@@
 The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model.
-\red{We see} two different point of views to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population.
+We see two different point of views to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population.
 Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.
@@
 
-Depending on the topic of research, \red{some} steps in this simulation framework can be more relevant than others.
+Depending on the topic of research, some steps in this simulation framework can be more relevant than others.
 From our perspective, these steps are more a complete list of phases one can conduct.
@@
 Two layers with separate responsibilities need to be discussed.
-The first is \textit{how} different simulation components can be combined, \red{and the second is \textit{when}} they are applied.
+The first is \textit{how} different simulation components can be combined, and the second is \textit{when} they are applied.
 Regarding the first, in \proglang{saeSim} we put a special emphasis on the interface of each component.
 To be precise, we use functions which take a \proglang{data.frame} as argument and have a \proglang{data.frame} as return value.
-This definition of interfaces, the return value of one component is the input of the next, is used for all existing tools in \proglang{saeSim}.
+The return value of one component is the input of the next.
+This definition of interfaces is used for all existing tools in \proglang{saeSim}.
 The second column in Figure \ref{fig:flowdiagram} shows how the different steps in a simulation can be accessed.
@@
 Each of these functions take a simulation setup object to be modified and a function with the discussed interface as arguments.
-Hence, \red{the pipe operator (\proglang{\%>\%}) can be used to combine components to a simulation setup.}
+Hence, the pipe operator (\proglang{\%>\%}) can be used to combine separate components to a simulation setup.
 
@@
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
-As a minimal example see the following lines which are equivalent:
+As a simple example see the following lines which are equivalent:
 
@@
 \proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
-\red{Separating} the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
+Separating the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
 The composition of a simulation in that manner will focus on the definition of components and hide control structures.
@@
 Before we begin to construct the simulation setup, we store these data tables as attributes to the population data.
-There are other options but \red{adding attributes to the data} is a very flexible form of processing data on different aggregation levels.
+There are other options but adding attributes to the data is a very flexible form of processing data on different aggregation levels.
 
@@
 
-In the next step, we define components which \red{add the estimates of interest} to the data.
+In the next step, we define components which add the estimates of interest to the data.
 Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
@@
 
-\red{A positive} aspect of the above definitions is, that the code for each step is relatively short and the purpose is clearly defined.
+A positive aspect of the above definitions is, that the code for each step is relatively short and the purpose is clearly defined.
 This may help to improve readability and to reproduce the research.
@@
 \label{sec:outlook}
-From our perspective, \red{there is a the need} for sharing tools for data generation and simulation amongst the scientific community to guarantee the reproducibility of research.
-\red{\proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation.
-By defining the steps of a simulation we may promote a reasonable way to communicate results in academic articles and during research.}
+From our perspective, there is a need for sharing tools for data generation and simulation amongst the scientific community to guarantee the reproducibility of research.
+\proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation.
+By defining the steps of a simulation we may promote a reasonable way to communicate results in academic articles and during research.
 
@@
 However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population).
-\red{Furthermore, an interface to random number generators available in the R-language is available.} The user can also generate group effects as needed in mixed models.
+Furthermore, an interface to \proglang{R} random number generators is available.
+The user can also generate group effects as needed in mixed models.
 As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.
@@
 A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
-\red{Tools to process result data after the simulation, i.e.
-summaries as well as plotting methods, are an avenue for further research.} Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
+Tools to process result data after the simulation, i.e.
+summaries or plotting methods, are avenues for further research.
+Already available are some simple plots for the simulation setups as well as a summary method to get information on the expected runtime and structure of the resulting data.
 

### 2015-01-12 saeSim.tex
saeSim-Paper: 1st submission

@@
           region   direct      BHF trueStat idR simName
-1     Burgenland 23083.61 20800.15 22005.42   1        
+1     Burgenland 23083.61 20800.16 22005.42   1        
 2  Lower Austria 20414.91 20264.56 19813.37   1        
 3         Vienna 20756.78 20422.85 20395.84   1        
-4      Carinthia 19581.64 19912.43 19486.18   1        
+4      Carinthia 19581.64 19912.42 19486.18   1        
 5         Styria 19443.11 19757.42 19335.39   1        

### 2015-01-23 replies_to_referee/Replies_to_referee.tex
replies and changes referee 1

\documentclass[11pt]{article}

\usepackage{setspace}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{amsmath}
\usepackage{amsmath, amsthm, amssymb}
%\usepackage{revsymb}
%\usepackage{eurosym}
\usepackage[pdftex]{graphicx}
\usepackage{natbib}
\usepackage{lineno}
\usepackage{lscape}
\usepackage{color}
\usepackage[figuresright]{rotating}
\newtheorem{thm}{Theorem}[section]
\newcommand{\sgn}{\text{sgn}}

\setlength{\textwidth}{15cm}
\setlength{\textheight}{23cm} \topmargin-1cm %\evensidemargin2cm
\oddsidemargin1cm

\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\bed}{\begin{displaymath}}
\newcommand{\eed}{\end{displaymath}}
%
% MATH -------------------------------------------------------------------
\newcommand{\U}{{\cal U}}
\newcommand{\R}{{\cal R}}
\newcommand{\abs}[1]{\left\vert#1\right\vert}
\newcommand{\set}[1]{\left\{#1\right\}}
\newcommand{\bra}[1]{\left(#1\right)}
\newcommand{\braq}[1]{\left[#1\right]}

\newcommand{\eps}{\varepsilon}
\newcommand{\si}{\sigma}
\newcommand{\ka}{\kappa}
\newcommand{\tr}{^{T}}
\newcommand{\bbeta}{\boldsymbol{\beta}}
\newcommand{\bGamma}{\boldsymbol{\Gamma}}
\newcommand{\ppsi}{\vec{\psi}}
\newcommand{\bpsi}{\vec\psi}
\newcommand{\btheta}{\vec\theta}
\newcommand{\bomega}{\vec\omega}
\newcommand \bDelta {\vec\Delta}
\newcommand{\bgamma}{\vec{\gamma}}
\newcommand{\beps}{\vec{\varepsilon}}

\def \cI {{\cal I}}
\def \bA {{\mathbf A}}
\def \bB {{\mathbf B}}
\def \bC {{\mathbf C}}
\def \bD {{\mathbf D}}
\def \bb {{\mathbf b}}
\def \be {{\mathbf e}}
\def \bG {{\mathbf G}}
\def \bH {{\mathbf H}}
\def \bh {{\mathbf h}}
\def \bI {{\mathbf I}}
\def \bL {{\mathbf L}}
\def \bn {{\mathbf n}}
\def \br {{\mathbf r}}
\def \bP {{\mathbf P}}
\def \bq {{\mathbf q}}
\def \bQ {{\mathbf Q}}
\def \bR {{\mathbf R}}
\def \bs {{\mathbf s}}
\def \bt {{\mathbf t}}
\def \bX {{\mathbf X}}
\def \bx {{\mathbf x}}
\def \by {{\mathbf y}}
\def \bu {{\mathbf u}}
\def \bv {{\mathbf v}}
\def \bV {{\mathbf V}}
\def \bZ {{\mathbf Z}}
\def \bz {{\mathbf z}}
\def \bW {{\mathbf W}}
\def \bw {{\mathbf w}}
\def \zero {{\mathbf 0}}

\def \diag {\mbox{diag}}
\def \uno {\mathbf 1}

\def \diag {\mbox{diag}}
\def \uno {\mathbf 1}
%\def\b#1{\mbox{\boldmath $#1$}}    % - \b: bold in formulas
%\def\bl#1{\mbox{\footnotesize \boldmath {$#1$}}} % - \bl: bold little formulas
\def\m#1{\mbox{#1}}                % - \m: text in formulas
\def\ml#1{\mbox{\scriptsize #1}} % - \ml: little text in formulas
\def\ha#1{\mbox{$\hat{\b #1}$}}
%\def\vec#1{\mbox{\boldmath $#1$}}

\newcommand{\sumuni}{\sum_{i\in\U}}
\newcommand{\sums}{\sum_{i\in s}}

\newcommand{\tcr}{\textcolor{red}}
\newcommand{\tcb}{\textcolor{blue}}

\newtheorem{Theorem}{Theorem}
\newtheorem{Remark}{Remark}
\newtheorem{Lemma}{Lemma}
\newtheorem{Corollary}{Corollary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%bibliography
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% The \cite command functions as follows:
 %   \citet{key} ==>>                Jones et al. (1990)
 %   \citet*{key} ==>>               Jones, Baker, and Smith (1990)
 %   \citep{key} ==>>                (Jones et al., 1990)
 %   \citep*{key} ==>>               (Jones, Baker, and Smith, 1990)
 %   \citep[chap. 2]{key} ==>>       (Jones et al., 1990, chap. 2)
 %   \citep[e.g.][]{key} ==>>        (e.g. Jones et al., 1990)
 %   \citep[e.g.][p. 32]{key} ==>>   (e.g. Jones et al., p. 32)
 %   \citeauthor{key} ==>>           Jones et al.
 %   \citeauthor*{key} ==>>          Jones, Baker, and Smith
 %   \citeyear{key} ==>>             1990

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{{Simulation Tools for Small Area Estimation:\\
Introducing the R-package saeSim} \\Replies to referee}
\author{S. Warnholz
\and T. Schmid
}

\date{} \maketitle

%\begin{abstract}
%This is the abstract
%\end{abstract}

%\textbf{Keywords:} These are the keywords.

%\doublespacing

\textcolor{red}{We are very grateful to the Editor and the two reviewers for their constructive comments. We have done our best to incorporate them in the revision. The following notes explain how we addressed each comment.}

\section*{Replies to reviewer A}

The manuscript introduces the R package saeSim, which simplifies writing code for simulation studies in small area statistics. The manuscript is enjoyable to read, but contains some shortcomings as well as several typos and other mistakes. The software seems useful for small area statisticians and could be a valuable contribution to the community. I particularly like the notion of treating simulation as a data manipulation process.

\vspace{0.5cm}

\noindent There are only minor issues that need to be addressed.

\begin{itemize}
\item
	Page 2: The authors cite Kolb (2013) for synthetic data generation. They should also mention what is available in R, for instance the approach by Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) that is implemented in package simPop.

	\textcolor{red}{We mow reference Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) together with Kolb (2013). The R-package simPop is now mentioned in the paragraph where we also cite simFrame, also on page 2.}

\item
	Page 2: The authors mention NUTS levels without explaining what they are. Please add a short explanation, including what the abbreviation NUTS stands for.

	\textcolor{red}{We deleted the reference to the NUTS levels. After revision the paragraph looses no relevant information to follow the argument. The revised version is now as follows:}

	\begin{quote}
	\textit{\textcolor{red}{
	Survey statistics are used, for example, in order to deliver specific indicators as a basis for
economic and political decision processes. Especially regional or group-specific comparisons
are of interest (cf. Schmid and Münnich 2014). Surveys which shall provide sufficient data
for these regional indicators, however, are generally designed for larger areas. Hence, sample
information on more detailed levels, e.g. municipalities, is hardly available so that classical
estimation methods (direct estimators) may lead to high variances of the estimates (cf. Ghosh
and Rao 1994). In this case, small area estimation methods may reveal highly improved results
for the target estimates. Small area estimation has become more and more attractive over
the last decade:
	}}
	\end{quote}

\item
	Page 5, last paragraph: I'm not sure which line in the simple example for the pipe operator is more readable. The line "sum(1:10)" translates into "sum of 1 to 10". The line "1:10 \%$>$\% sum" tanslates into "generate 1 to 10, then take the sum". I'm sure that the authors can find a simple example that is better suited to illustrate their point.

	\textcolor{red}{We changed the example into:}
	\verb'colMeans(matrix(rnorm(10), ncol = 2))' \textcolor{red}{which translates to} \verb'rnorm(10) %>% matrix(ncol = 2) %>% colMeans' \textcolor{red}{, and is now an actual improvement in readability.}

\item
	Page 6 and 7, code examples: The authors load package saeSim in each of the two code examples. Yet there is another code chunk before those examples which use functionality from the package. If readers try to execute all code in the order it appears in the paper, they will get error messages. I suggest to load the package in the beginning of Section 4 (in a separate chunk), and to remove this line from the two examples to focus on the relevant code.

	\textcolor{red}{We now load saeSim (and magrittr) in the beginning of section 4. We checked the code again, so that all expressions are valid when executed in the order in which they appear in the article. Also we made the seed available to the reader. Furthermore the package sae produced naming conflicts as it loads a lot of dependencies. We do not load the package but reference to it with the '::' operator, which is acceptable as we only use two functions from this package.}

\item
	Page 8, last line: The authors write "... we store these data tables...". Are those data frames or data tables? In R, this can be confusing due to the data.table package.

	\textcolor{red}{To avoid any confusion we changed it into 'data frame'. The paragraph is quoted as a reply to you next remark.}

\item
	Page 9: The authors state that they store some information as attritutes to the main data frame. Attributes can be a dangerous thing in R as there are some functions for manipulating data that may remove any attributes. Please give a discussion on this issue and provide more motivation for using attributes.

	\textcolor{red}{We agree that relying on attributes can be a weakness. The problem is, that very often we do not have a single data frame to process, but also meta data attached. We can make that meta data available by taking advantage of R's lexical scoping rules. However, this is a dangerous path as the functions in which we need that meta data are no longer self contained. They depend on the state of objects other than their arguments and we want to avoid that. Another possibility is to make meta data available only to the functions in which they are needed by using closures. This ensures that the functions are self contained but adds unnecessary complexity for the purpose of this article as advanced functional programming techniques are not "mainstream" for R users. Also we could design an own \textit{data class} which is more formal to ensure type consistency (for example using a S4-class). However, we tried to design saeSim such that it can be used with as many existing tools as possible. We think this is possible by sticking to the "data.frame in, data.frame out" philosophy. Thus, we decided to support functions which preserve attributes. All present functions in the package will preserve attributes of the main data frame. If you have suggestions to improve this we would appreciate it. We added the discussion in a separate paragraph as follows:}
	\begin{quote}
	\textit{
	\textcolor{red}{Before we begin to construct the simulation setup, we store these data frames as attributes
to the population data. However, extra care is is needed because not all functions for
manipulating data frames in R will preserve their attributes. Functions in saeSim all support
this approach. Yet, in user defined functions this needs to be kept in mind by the author.
Adding attributes to the data is a very flexible form of processing data on different aggregation
levels and we believe this to be a reasonable trade-off. Of course other options can be applied
within the possibilities of the R language.
	}
	}
	\end{quote}
\item
	Page 13: To the best of my knowledge, the preferred format for CRAN links is http://CRAN.R-project.org/package=saeSim (also note the capitalization of CRAN and R).\textcolor{red}{ -- done}
\item
	Page 13: For non-representative outliers, the authors give the explanation "outliers are part of the sample but not the population". This may be confusing to some readers. I suggest that they add "e.g., incorrectly recorded values".\textcolor{red}{ -- done}

\end{itemize}

\vspace{0.5cm}

\noindent Comments regarding language are given in the following. There may be more mistakes, hence I recommend that the authors ask a colleague to proofread the manuscript (preferably an English native speaker).

\noindent\textcolor{red}{Our apologies for the inconvenience for proofreading the article. We followed your suggestion and the manuscript has been proofread again.}

\begin{itemize}
\item
	Page 1, abstract and first paragraph: "has been substantially grown" to "has grown" \textcolor{red}{-- done}
\item
	Page 3, line -8: "is build on a sampling model" to "is built on a sampling model" \textcolor{red}{-- done}
\item
	Page 4, line -2: "different point of views" to "different points of view" \textcolor{red}{-- done}
\item
	Page 6, lines 1-2: "In saeSim, we rely on this operator, although all functions can be used without, we strongly recommend to use it." to "In saeSim, we rely on this operator. Although all functions can be used without it, we strongly recommend its usage." \textcolor{red}{-- done}
\item
	Page 6, second paragraph: "... which has a data.frame as input as well as return value." The correct "... which has a data.frame as input as well as as return value." is cumbersome since as appears twice in a row, so I suggest to change this to "... which has a data.frame both as input and as return value."  \textcolor{red}{-- done}

\item
	Page 10, first paragraph: "This focus on the definition of each component and on meeting the convention of the defined interface is the intended approach." I'm confused by this sentence, please rephrase.

	\textcolor{red}{We deleted the sentence as their seems to be no loss of information. The paragraph now reads as:}	
	\begin{quote}
	\textit{
	\textcolor{red}{
		In the next step, we define components which add the estimates of interest to the data. Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model. Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other. This automatically organises the simulation and each component is arranged using the simulation framework. Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
		}
		}
	\end{quote}
\item
	Page 13, second paragraph: "version-control" to "version control" \textcolor{red}{-- done}
\item
	Page 13, second paragraph: "it's purpose" to "its purpose" \textcolor{red}{-- done}
\end{itemize}

\pagebreak
\section*{Replies to reviewer C}

The package appears to be useful for most statisticians working with small area methods. It is a good idea to build the framework using the idea of process of data manipulation. This makes the package easy to use. The manuscript is interesting and useful, and I find it acceptable for
publishing after minor revision.

\begin{itemize}
\item
	The authors should mention - probably in Section 4 - that in order to repeat a simulation with identical results, the seed used in the original simulation has to be known.

	\textcolor{red}{We added this information right before we start illustrating the model-based simulation. Also we added the seed visibly in the code as before it was set in a hidden chunk. The second paragraph in section 4.1 now reads as follows:}
	\begin{quote}
	\textit{
\textcolor{red}{In this case the \textit{base-component} is a data frame with an id variable named idD and constructed with the function base\_id. Any random number generator in R can be used. However, we have normally distributed variates, for which some predefined functions are available in the package. For the reproducibility of the following results we also set the seed to 1. The seed is not part of a simulation setup in saeSim but needs to be supplied by the researcher.
	}
	}
	\end{quote}
\end{itemize}

\vspace{0.5cm}

\noindent There are some grammatical errors:

\begin{itemize}
\item
	(1) abstract: remove 'been' from "...has been substantially grown" \textcolor{red}{-- changed to: "... has grown substantially"}
\item
	(2) Introduction: remove 'been' from "...has been substantially..." \textcolor{red}{-- changed to: "... has grown substantially"}
\item
	(3) Introduction (last two lines on page 1): rephrase "...reproducible research aims that the full output of the academic research,..." using "...aims at the availability of the full... " \textcolor{red}{-- done}
\item
	(4) Replace 'neighboured' by 'neighbouring' \textcolor{red}{-- done}
\item
	(5) At the end of page 1, remove '-' in "source-code" \textcolor{red}{-- done}
\item
	(6) In the beginning of section 2 (second line), replace 'less' by 'few' in "...for domains where less or no sampled..." \textcolor{red}{-- done}
\item
	(7) Below equation (1), replace 'build' by 'built' in "...introduced by Fay and Herriot (1979) is build..." \textcolor{red}{-- done}
\end{itemize}

\end{document}

### 2015-01-23 saeSim.Rnw
replies and changes referee 1

@@
 
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-%% additional packages
+%% additional packages and settings which are not part of the template:
 \usepackage{wrapfig}
@@
 \include{mathOperators}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%% declarations for jss.cls %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
 
@@
 \Abstract{
-The demand for reliable regional estimates from sample surveys has been substantially grown over the last decades.
+The demand for reliable regional estimates from sample surveys \red{has grown substantially} over the last decades.
 Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators.
@@
 %% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+\newcommand{\red}[1]{\color{red} #1 \color{black} }
 
@@
 <<echo=FALSE>>=
-loadAndInstallPackage <- function(packageName) {
-  if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
-    install.packages(packageName)
-    eval(substitute(suppressPackageStartupMessages(library(packageName))))
-  } 
-}
-loadAndInstallPackage("saeSim")
-# Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr):
-loadAndInstallPackage("sae")
-loadAndInstallPackage("dplyr")
-loadAndInstallPackage("reshape2")
-loadAndInstallPackage("ggplot2")
+# loadAndInstallPackage <- function(packageName) {
+#   if(!eval(substitute(suppressPackageStartupMessages(require(packageName))))) {
+#     install.packages(packageName)
+#     eval(substitute(suppressPackageStartupMessages(library(packageName))))
+#   } 
+# }
+# loadAndInstallPackage("saeSim")
+# # Keep order in which packages are loaded, there are naming conflicts between dependencies (MASS and dplyr) which are loaded and attached by the package sae:
+# loadAndInstallPackage("sae")
+# loadAndInstallPackage("dplyr")
+# loadAndInstallPackage("reshape2")
+# loadAndInstallPackage("ggplot2")
 @
@@
 \section{Introduction}
-The demand for reliable small area statistics from sample surveys has been substantially grown over the last decades due to their use in public and private sectors.
+The demand for reliable small area statistics from sample surveys \red{has grown substantially} over the last decades due to their use in public and private sectors.
 In this paper we present a framework for simulation studies inside the field of small area estimation.
@@
 Reproducible research has become a widely discussed topic.
-In the field of statistics many open-source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
+In the field of statistics many open source tools like the \proglang{R}-language \citep{r14} and \LaTeX, dynamic reporting packages like \proglang{knitr} \citep{yihui13}, \proglang{sweave} \citep{leisch02} and more recently \proglang{rmarkdown} \citep{allaire14}, make the integration of text and source code for statistical analysis possible.
 Publishing source code and data alongside research results draws special attention to authoring the analysis.
@@
 
-Next to the combination of text and source code, reproducible research aims that the full output of the academic research, which is the paper combined with the full computational environment like data and source code, is available.
+Next to the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational environment like data and source code.
 However, real data is often very sensitive and governed by strict confidentiality rules.
-Synthetic data generation mechanisms \citep{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.
-\cite{Bur14} interpreted this as an open research philosophy.
+\red{Synthetic data generation mechanisms as discussed in \cite{alfons2011} and \cite{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.} \cite{Bur14} interpreted this as an open research philosophy.
 Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework.
@@
 
-\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment.
-It includes a wide range of different features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies.
+\red{\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment.
+It includes a wide range of features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies.
 \proglang{simFrame} was originally developed for simulations in the context of survey statistics but is now designed to be as general as possible \citep[cf.][]{Alf10}.
+Furthermore the package \proglang{simPop} \citep{Alf14} supports the generation of synthetic population data.
+This can be a suitable environment in scenarios where the reproducibility of results and confidentiality issues both play an important role.}
 
@@
 Especially regional or group-specific comparisons are of interest \citep[cf.][]{Sch13}.
-Surveys which shall provide the sufficient data for these regional indicators, however, are generally designed for larger areas (NUTS 1-2 level).
-Hence, sample information on more detailed levels, like NUTS3, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}.
+Surveys which shall provide sufficient data for these regional indicators, however, are generally designed for larger areas.
+Hence, sample information on more detailed levels, e.g.
+municipalities, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}.
 In this case, small area estimation methods may reveal highly improved results for the target estimates.
@@
 
-However, simulation studies in the context of small area estimation is often presented very briefly.
+However, simulation studies in the context of small area estimation \red{are} often presented very briefly.
 Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis.
@@
 Second, unify the process of simulation studies.
-Third, make the source-code of simulation studies available, such that it supports the conducted research in a transparent manner.
+Third, make the source code of simulation studies available, such that it supports the conducted research in a transparent manner.
 
@@
 
-The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where less or no sampled units are available.
+The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available.
 Groups may be areas or other entities, for example defined by socio-economic characteristics.
 The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
-As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighboured or \textit{similar} domains.
+As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighbouring or \textit{similar} domains.
 This can be achieved by using additional information from census data or registers to assist the prediction for non-sampled domains or domains with small sample sizes.
@@
 Here area-level models can be valuable.
-The area-level model introduced by \cite{fay79} is build on a sampling model:
+The area-level model introduced by \cite{fay79} is built on a sampling model:
 %
@@
 The \textbf{population-level} defines the data on which a study is conducted and may be a true population, synthetic population data or randomly generated variates from a model.
-We see two different point of views to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population.
+We see two different points of view to define a population: Firstly, \textit{design-based} simulations, which means that a simulation study is based on true or synthetic data of \textit{one} population.
 Secondly, \textit{model-based} simulations, which have changing random populations drawn from a model.
@@
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
-As a simple example see the following lines which are equivalent:
+\red{As a simple example see the following lines which are equivalent with respect to their functionality:}
 
 <<eval=FALSE>>=
-sum(1:10)
-1:10 %>% sum
+library(magrittr)
+colMeans(matrix(rnorm(10), ncol = 2))
+rnorm(10) %>% matrix(ncol = 2) %>% colMeans
 @
 
-In \proglang{saeSim} we rely on this operator, although all functions can be used without, we strongly recommend to use it. The following example shows some of the aspects of the package:
+In \proglang{saeSim}, we rely on this operator. Although all functions can be used without it, we strongly recommend its usage. The following example shows some of the aspects of the package:
+
+<<eval=TRUE, echo=FALSE>>=
+library(saeSim)
+@
 
 <<eval=FALSE>>=
+library(saeSim)
 setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
@@
 The composition of a simulation in that manner will focus on the definition of components and hide control structures.
-Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} as input as well as return value.
+Any function can be passed to \proglang{sim\_sample} which has a \proglang{data.frame} both as input and as return value.
 The only responsibility of that function is to draw a sample, which makes it easy to find, understand and reuse when published.
@@
 \label{sec:csModel}
-<<echo=FALSE>>=
-set.seed(1) # for reproduction of the results
-@
+
 In the following we show one way how to construct a simulation in a model-based setting.
@@
 
-In this case the \textit{base-component} is a data table with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
+In this case the \textit{base-component} is a data frame with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
 Any random number generator in \proglang{R} can be used.
 However, we have normally distributed variates, for which some predefined functions are available in the package.
+\red{For the reproducibility of the following results we also set the seed to 1.
+The seed is not part of a simulation setup in \proglang{saeSim} but needs to be supplied by the researcher.}
 
 <<>>=
-library(saeSim)
+set.seed(1)
 setup <- base_id(nDomains = 40, nUnits = 1) %>% 
@@
 <<>>=
-library(sae)
 comp_FH <- function(dat) {
-  modelFH <- eblupFH(y ~ x, vardir, data = dat)
+  modelFH <- sae::eblupFH(y ~ x, vardir, data = dat)
   dat$FH <- modelFH$eblup
@@
 An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios.
-At this time we do not provide further tools to process the resulting data.
-Many packages are available in \proglang{R} to handle \proglang{data.frame}.
+At this time we do not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}.
 In the design-based scenario we show how to process the result data into graphs with only a few lines of code.
@@
 The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator.
-This function expects three data objects and returns domain predictions.
+This function expects three data objects and returns \red{the} domain predictions.
 The three objects are the sampled data, the population means of the auxiliary variables and the population sizes in each domain.
-Before we begin to construct the simulation setup, we store these data tables as attributes to the population data.
-There are other options but adding attributes to the data is a very flexible form of processing data on different aggregation levels.
+
+\red{Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
+However, extra care is needed because not all functions for manipulating data frames in \proglang{R} will preserve their attributes.
+Functions in \proglang{saeSim} all support this approach.
+Yet, in user defined functions this needs to be kept in mind by the author.
+Adding attributes to the data is a very flexible form of processing data on different aggregation levels and we believe this to be a reasonable trade-off.
+Of course other options can be applied within the possibilities of the \proglang{R} language.}
 
@@
 
-In the next step, we define components which add the estimates of interest to the data.
+\red{In the next step, we define components which add the estimates of interest to the data.
 Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
 Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other.
-This focus on the definition of each component and  on meeting the convention of the defined interface is the intended approach.
-It automatically organises the simulation and each component is arranged using the simulation framework.
-Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
+This automatically organises the simulation and each component is arranged using the simulation framework.
+Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.}
 
@@
   modelBHF <- 
-    eblupBHF(eqIncome ~ age + agesq + gender, region, meanxpop = popMeans,
+    sae::eblupBHF(eqIncome ~ age + agesq + gender, region, meanxpop = popMeans,
              popnsize = attr(dat, "popN"), data = dat)
@@
 <<>>=
-library(reshape2)
-ggDat <- melt(simResults,
+ggDat <- reshape2::melt(simResults,
               id.vars = c("region", "trueStat"), 
@@
 
-The package source is available on CRAN (\url{http://cran.r-project.org/web/packages/saeSim/}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
-As GitHub allows to share and contribute source code using version-control, it is open for submissions.
+The package source is available on CRAN (\url{http://CRAN.R-project.org/package=saeSim}) and the repository for development on GitHub (\url{https://github.com/wahani/saeSim}).
+As GitHub allows to share and contribute source code using version control, it is open for submissions.
 Apart from the availability of specific utility functions, we may promote and support the design of source code for simulation studies.
@@
 functions.
-This reduces the lines of code necessary to be read in order to understand it's purpose.
+This reduces the lines of code necessary to be read in order to understand its purpose.
 
@@
 At this time only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
-However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population).
-Furthermore, an interface to \proglang{R} random number generators is available.
-The user can also generate group effects as needed in mixed models.
+\red{However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population, e.g., incorrectly recorded values).
+Furthermore, an interface to random number generators in \proglang{R} is available.} The user can also generate group effects as needed in mixed models.
 As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.

### 2015-01-23 saeSim.tex
replies and changes referee 1

@@
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
-As a simple example see the following lines which are equivalent:
+\red{As a simple example see the following lines which are equivalent with respect to their functionality:}
 
@@
 \begin{Sinput}
-> sum(1:10)
-> 1:10 %>% sum
+> library(magrittr)
+> colMeans(matrix(rnorm(10), ncol = 2))
+> rnorm(10) %>% matrix(ncol = 2) %>% colMeans
 \end{Sinput}
@@
 
-In \proglang{saeSim} we rely on this operator, although all functions can be used without, we strongly recommend to use it. The following example shows some of the aspects of the package:
+In \proglang{saeSim}, we rely on this operator. Although all functions can be used without it, we strongly recommend its usage. The following example shows some of the aspects of the package:
 
@@
 \begin{Sinput}
+> library(saeSim)
 > setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
@@
 \label{sec:csModel}
+
 In the following we show one way how to construct a simulation in a model-based setting.
@@
 
-In this case the \textit{base-component} is a data table with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
+In this case the \textit{base-component} is a data frame with an id variable named \proglang{idD} and constructed with the function \proglang{base\_id}.
 Any random number generator in \proglang{R} can be used.
 However, we have normally distributed variates, for which some predefined functions are available in the package.
+\red{For the reproducibility of the following results we also set the seed to 1.
+The seed is not part of a simulation setup in \proglang{saeSim} but needs to be supplied by the researcher.}
 
@@
 \begin{Sinput}
-> library(saeSim)
+> set.seed(1)
 > setup <- base_id(nDomains = 40, nUnits = 1) %>% 
@@
 \begin{Sinput}
-> library(sae)
 > comp_FH <- function(dat) {
-+   modelFH <- eblupFH(y ~ x, vardir, data = dat)
++   modelFH <- sae::eblupFH(y ~ x, vardir, data = dat)
 +   dat$FH <- modelFH$eblup
@@
 +   modelBHF <- 
-+     eblupBHF(eqIncome ~ age + agesq + gender, region, meanxpop = popMeans,
++     sae::eblupBHF(eqIncome ~ age + agesq + gender, region, meanxpop = popMeans,
 +              popnsize = attr(dat, "popN"), data = dat)
@@
 \begin{Sinput}
-> library(reshape2)
-> ggDat <- melt(simResults,
+> ggDat <- reshape2::melt(simResults,
 +               id.vars = c("region", "trueStat"), 

### 2015-01-26 saeSim.Rnw
saeSim updates von Timo

@@
 \Abstract{
-The demand for reliable regional estimates from sample surveys \red{has grown substantially} over the last decades.
+The demand for reliable regional estimates from sample surveys has substantially grown over the last decades.
 Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators.
@@
 \section{Introduction}
-The demand for reliable small area statistics from sample surveys \red{has grown substantially} over the last decades due to their use in public and private sectors.
+The demand for reliable small area statistics from sample surveys has substantially grown over the last decades due to their use in public and private sectors.
 In this paper we present a framework for simulation studies inside the field of small area estimation.
@@
 However, real data is often very sensitive and governed by strict confidentiality rules.
-\red{Synthetic data generation mechanisms as discussed in \cite{alfons2011} and \cite{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.} \cite{Bur14} interpreted this as an open research philosophy.
+Synthetic data generation mechanisms as discussed in \cite{alfons2011} or \cite{Kol11} can be used to provide safe data which is publicly available to enable the community to reproduce the analysis and results.
+\cite{Bur14} interpreted this as an open research philosophy.
 Such synthetic data sets can be used to test newly proposed statistical methods in a close-to-reality framework.
@@
 
-\red{\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment.
+\cite{Alf10} provide the \proglang{R}-package \proglang{simFrame} which helps to conduct simulation studies in a reproducible environment.
 It includes a wide range of features (like data generation, sampling schemes, outlier contamination mechanisms and missing values) to conduct simulation studies.
@@
 Furthermore the package \proglang{simPop} \citep{Alf14} supports the generation of synthetic population data.
-This can be a suitable environment in scenarios where the reproducibility of results and confidentiality issues both play an important role.}
+This can be a suitable environment in scenarios where the reproducibility of results and confidentiality issues play an important role.
 
@@
 
-However, simulation studies in the context of small area estimation \red{are} often presented very briefly.
+However, simulation studies in the context of small area estimation are often presented very briefly.
 Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis.
@@
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
-\red{As a simple example see the following lines which are equivalent with respect to their functionality:}
+As a simple example see the following lines which are equivalent with respect to their functionality:
 
@@
 However, we have normally distributed variates, for which some predefined functions are available in the package.
-\red{For the reproducibility of the following results we also set the seed to 1.
-The seed is not part of a simulation setup in \proglang{saeSim} but needs to be supplied by the researcher.}
+For the reproducibility of the following results we also set the seed to 1.
+The seed is not part of a simulation setup in \proglang{saeSim} but needs to be defined by the researcher.
 
@@
 The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator.
-This function expects three data objects and returns \red{the} domain predictions.
+This function expects three data objects and returns the domain predictions.
 The three objects are the sampled data, the population means of the auxiliary variables and the population sizes in each domain.
 
-\red{Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
-However, extra care is needed because not all functions for manipulating data frames in \proglang{R} will preserve their attributes.
-Functions in \proglang{saeSim} all support this approach.
-Yet, in user defined functions this needs to be kept in mind by the author.
-Adding attributes to the data is a very flexible form of processing data on different aggregation levels and we believe this to be a reasonable trade-off.
-Of course other options can be applied within the possibilities of the \proglang{R} language.}
+Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
+This allows us to process on the same time a single data frame and some meta data.
+It is important to notice that some functions for manipulating data frames in \proglang{R} don't preserve their attributes.
+The prospective user of the \proglang{saeSim} has to keep this in mind when implementing user defined functions.
+However, all functions in \proglang{saeSim} are able to preserve their attributes.
+Other options can be applied within the possibilities of the \proglang{R} language.
+For instance, one could use closures to make the meta data only available for specific functions.
+This approach needs advanced functional programming skills and may add an additional level of complexity to the package user.
+However, from our perspective, adding attributes to the data is be a very flexible form of processing data on different aggregation levels and is used in this package.
 
@@
 
-\red{In the next step, we define components which add the estimates of interest to the data.
+In the next step, we define components which add the estimates of interest to the data.
 Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
@@
 This automatically organises the simulation and each component is arranged using the simulation framework.
-Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.}
+Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
 
@@
 At this time only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
-\red{However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population, e.g., incorrectly recorded values).
-Furthermore, an interface to random number generators in \proglang{R} is available.} The user can also generate group effects as needed in mixed models.
+However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population, e.g., incorrectly recorded values).
+Furthermore, an interface to random number generators in \proglang{R} is available.
+The user can also generate group effects as needed in mixed models.
 As the response is created by an \proglang{R} expression, any form of non-linearity in the relationship between response and auxiliary variables as well as error components can be modelled.

### 2015-01-26 replies_to_referee/Replies_to_referee.tex
saeSim corrections

@@
 
-\textcolor{red}{We are very grateful to the Editor and the two reviewers for their constructive comments.
+We are very grateful to the Editor and the two reviewers for their constructive comments.
+These have been very helpful in preparing the revised version of this paper.
 We have done our best to incorporate them in the revision.
-The following notes explain how we addressed each comment.}
+The following notes explain how we addressed each comment.
 
@@
 
-	\textcolor{red}{We mow reference Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) together with Kolb (2013).
-The R-package simPop is now mentioned in the paragraph where we also cite simFrame, also on page 2.}
+	Reply: We now reference Alfons, Kraft, Templ \& Filzmoser (2011, Statistical Methods \& Applications) together with Kolb (2013).
+The R-package simPop is now mentioned in the paragraph where we also cite simFrame, also on page 2.
 
@@
 
-	\textcolor{red}{We deleted the reference to the NUTS levels. After revision the paragraph looses no relevant information to follow the argument. The revised version is now as follows:}
-
-	\begin{quote}
-	\textit{\textcolor{red}{
+	Reply: We deleted the reference to the NUTS levels. After the revision the paragraph doesn't lose relevant information to follow the common theme. The revised version is now as follows:\\\\
+	\textit{
 	Survey statistics are used, for example, in order to deliver specific indicators as a basis for
 economic and political decision processes. Especially regional or group-specific comparisons
-are of interest (cf. Schmid and Münnich 2014). Surveys which shall provide sufficient data
+are of interest (cf. Schmid and M\"unnich 2014). Surveys which shall provide sufficient data
 for these regional indicators, however, are generally designed for larger areas. Hence, sample
@@
 the last decade:
-	}}
-	\end{quote}
+	}
 
@@
 
-	\textcolor{red}{We changed the example into:}
-	\verb'colMeans(matrix(rnorm(10), ncol = 2))' \textcolor{red}{which translates to} \verb'rnorm(10) %>% matrix(ncol = 2) %>% colMeans' \textcolor{red}{, and is now an actual improvement in readability.}
+	Reply: We acknowledge that we have to be more specific here. We changed the example to:
+	\verb'colMeans(matrix(rnorm(10), ncol = 2))' which translates to \\\verb'rnorm(10) %>% matrix(ncol = 2) %>% colMeans'.
 
@@
 
-	\textcolor{red}{We now load saeSim (and magrittr) in the beginning of section 4.
+	Reply: We load now saeSim (and magrittr) in the beginning of section 4.
 We checked the code again, so that all expressions are valid when executed in the order in which they appear in the article.
-Also we made the seed available to the reader.
+We also made the seed available to the reader.
 Furthermore the package sae produced naming conflicts as it loads a lot of dependencies.
-We do not load the package but reference to it with the '::' operator, which is acceptable as we only use two functions from this package.}
+We do not load the package but reference to it with the '::' operator.
 
@@
 
-	\textcolor{red}{To avoid any confusion we changed it into 'data frame'. The paragraph is quoted as a reply to you next remark.}
+	Reply: To avoid any confusion we changed it into 'data frame'. The paragraph is quoted as a reply to you next remark.
 
 \item
-	Page 9: The authors state that they store some information as attritutes to the main data frame.
+	Page 9: The authors state that they store some information as attributes to the main data frame.
 Attributes can be a dangerous thing in R as there are some functions for manipulating data that may remove any attributes.
@@
 
-	\textcolor{red}{We agree that relying on attributes can be a weakness.
-The problem is, that very often we do not have a single data frame to process, but also meta data attached.
-We can make that meta data available by taking advantage of R's lexical scoping rules.
-However, this is a dangerous path as the functions in which we need that meta data are no longer self contained.
-They depend on the state of objects other than their arguments and we want to avoid that.
+Reply: We agree that relying on attributes may be dangerous in R.
+The problem is that in some situation we have to process a single data frame plus some meta data.
+An alternative is to make that meta data available by taking advantage of R's lexical scoping rules.
+However, this may be a dangerous path as the functions, which need the meta data, are no longer self contained.
+They depend on the specific state of the objects instead of their arguments.
+We want to avoid this situation.
 Another possibility is to make meta data available only to the functions in which they are needed by using closures.
-This ensures that the functions are self contained but adds unnecessary complexity for the purpose of this article as advanced functional programming techniques are not "mainstream" for R users.
-Also we could design an own \textit{data class} which is more formal to ensure type consistency (for example using a S4-class).
+This ensures that the functions are self contained but adds unnecessary complexity because advanced functional programming techniques are not "mainstream" for R users.
+We also could design an own \textit{data class} which is more formal to ensure type consistency (for example using a S4-class).
 However, we tried to design saeSim such that it can be used with as many existing tools as possible.
@@
 All present functions in the package will preserve attributes of the main data frame.
-If you have suggestions to improve this we would appreciate it.
-We added the discussion in a separate paragraph as follows:}
-	\begin{quote}
+We have added the following paragraph in the paper (Section 4.2):\\\\
 	\textit{
-	\textcolor{red}{Before we begin to construct the simulation setup, we store these data frames as attributes
-to the population data. However, extra care is is needed because not all functions for
-manipulating data frames in R will preserve their attributes. Functions in saeSim all support
-this approach. Yet, in user defined functions this needs to be kept in mind by the author.
-Adding attributes to the data is a very flexible form of processing data on different aggregation
-levels and we believe this to be a reasonable trade-off. Of course other options can be applied
-within the possibilities of the R language.
+	Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
+This allows us to process on the same time a single data frame and some meta data.
+It is important to notice that some functions for manipulating data frames in R don't preserve their attributes.
+The prospective user of the saeSim has to keep this in mind when implementing user defined functions.
+However, all functions in saeSim are able to preserve their attributes.
+Other options can be applied within the possibilities of the R language.
+For instance, one could use closures to make the meta data only available for specific functions.
+This approach needs advanced functional programming skills and may add an additional level of complexity to the package user.
+However, from our perspective, adding attributes to the data is be a very flexible form of processing data on different aggregation levels and is used in this package.
 	}
-	}
-	\end{quote}
 \item
-	Page 13: To the best of my knowledge, the preferred format for CRAN links is http://CRAN.R-project.org/package=saeSim (also note the capitalization of CRAN and R).\textcolor{red}{ -- done}
+	Page 13: To the best of my knowledge, the preferred format for CRAN links is http://CRAN.R-project.org/package=saeSim (also note the capitalization of CRAN and R).
+
+    Reply: This has been corrected.
 \item
@@
 This may be confusing to some readers.
-I suggest that they add "e.g., incorrectly recorded values".\textcolor{red}{ -- done}
+I suggest that they add "e.g., incorrectly recorded values".
+
+Reply: This has been added.
 
@@
 
-\noindent\textcolor{red}{Our apologies for the inconvenience for proofreading the article. We followed your suggestion and the manuscript has been proofread again.}
+\noindent Reply: We strongly apology for the mistakes in the article.
+We did a careful double check of the paper.
+In addition, we followed your suggestion to check the manuscript by an English native speaker.
 
@@
 \item
-	Page 1, abstract and first paragraph: "has been substantially grown" to "has grown" \textcolor{red}{-- done}
+	Page 1, abstract and first paragraph: "has been substantially grown" to "has grown" -- done
 \item
-	Page 3, line -8: "is build on a sampling model" to "is built on a sampling model" \textcolor{red}{-- done}
+	Page 3, line -8: "is build on a sampling model" to "is built on a sampling model" -- done
 \item
-	Page 4, line -2: "different point of views" to "different points of view" \textcolor{red}{-- done}
+	Page 4, line -2: "different point of views" to "different points of view" -- done
 \item
 	Page 6, lines 1-2: "In saeSim, we rely on this operator, although all functions can be used without, we strongly recommend to use it." to "In saeSim, we rely on this operator.
-Although all functions can be used without it, we strongly recommend its usage." \textcolor{red}{-- done}
+Although all functions can be used without it, we strongly recommend its usage." -- done
 \item
@@
 which has a data.frame as input as well as as return value." is cumbersome since as appears twice in a row, so I suggest to change this to "...
-which has a data.frame both as input and as return value."  \textcolor{red}{-- done}
+which has a data.frame both as input and as return value."  -- done
 
@@
 
-	\textcolor{red}{We deleted the sentence as their seems to be no loss of information. The paragraph now reads as:}	
-	\begin{quote}
+	Reply: We acknowledge that the sentence may create some confusion to the prospective reader.
+Therefore, we have deleted to sentence to make the paragraph more clear.
+In the revised version of the paper we say the following:\\\\
 	\textit{
-	\textcolor{red}{
 		In the next step, we define components which add the estimates of interest to the data.
@@
 		}
-		}
-	\end{quote}
 \item
-	Page 13, second paragraph: "version-control" to "version control" \textcolor{red}{-- done}
+	Page 13, second paragraph: "version-control" to "version control". -- done
 \item
-	Page 13, second paragraph: "it's purpose" to "its purpose" \textcolor{red}{-- done}
+	Page 13, second paragraph: "it's purpose" to "its purpose". -- done
 \end{itemize}
@@
 
-	\textcolor{red}{We added this information right before we start illustrating the model-based simulation.
-Also we added the seed visibly in the code as before it was set in a hidden chunk.
-The second paragraph in section 4.1 now reads as follows:}
-	\begin{quote}
-	\textit{
-\textcolor{red}{In this case the \textit{base-component} is a data frame with an id variable named idD and constructed with the function base\_id.
+	Reply: We agree with this comment.
+We have added this information right before we start illustrating the model-based simulation.
+We have also added the seed in the code.
+In the first version, the seed was set in a hidden chunk.
+In Section 4.1 in the revised version of the paper we say the following:\\\\
+	\textit{In this case the \textit{base-component} is a data frame with an id variable named idD and constructed with the function base\_id.
 Any random number generator in R can be used.
@@
 For the reproducibility of the following results we also set the seed to 1.
-The seed is not part of a simulation setup in saeSim but needs to be supplied by the researcher.
-	}
-	}
-	\end{quote}
+The seed is not part of a simulation setup in saeSim but needs to be defined by the researcher.}
+
 \end{itemize}
@@
 
+\noindent Reply: We strongly apology for the grammatical errors in the article. We did a careful double check of the paper. In addition, the manuscript was checked by an English native speaker.
+
 \begin{itemize}
-\item
-	(1) abstract: remove 'been' from "...has been substantially grown" \textcolor{red}{-- changed to: "... has grown substantially"}
-\item
-	(2) Introduction: remove 'been' from "...has been substantially..." \textcolor{red}{-- changed to: "... has grown substantially"}
-\item
-	(3) Introduction (last two lines on page 1): rephrase "...reproducible research aims that the full output of the academic research,..." using "...aims at the availability of the full...
-" \textcolor{red}{-- done}
-\item
-	(4) Replace 'neighboured' by 'neighbouring' \textcolor{red}{-- done}
-\item
-	(5) At the end of page 1, remove '-' in "source-code" \textcolor{red}{-- done}
-\item
-	(6) In the beginning of section 2 (second line), replace 'less' by 'few' in "...for domains where less or no sampled..." \textcolor{red}{-- done}
-\item
-	(7) Below equation (1), replace 'build' by 'built' in "...introduced by Fay and Herriot (1979) is build..." \textcolor{red}{-- done}
+\item[(1)]abstract: remove 'been' from "...has been substantially grown" -- done
+\item[(2)]Introduction: remove 'been' from "...has been substantially..."-- done
+\item[(3)]Introduction (last two lines on page 1): rephrase "...reproducible research aims that the full output of the academic research,..." using "...aims at the availability of the full...
+" -- done
+\item[(4)]Replace 'neighboured' by 'neighbouring' -- done
+\item[(5)]At the end of page 1, remove '-' in "source-code" -- done
+\item[(6)]In the beginning of section 2 (second line), replace 'less' by 'few' in "...for domains where less or no sampled..." -- done
+\item[(7)]Below equation (1), replace 'build' by 'built' in "...introduced by Fay and Herriot (1979) is build..." -- done
 \end{itemize}

### 2015-01-26 saeSim.Rnw
saeSim corrections

@@
 Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators.
-Model- and design-based simulations are used to gain insights into the quality of the introduced methods.
-In this article we present a framework which may help to guarantee the reproducibility of simulation studies in articles and during research.
-The introduced \proglang{R}-package \proglang{saeSim} is adjusted to provide a simulation environment for the special case of small area estimation.
-The package may allow the prospective researcher during the research process to produce simulation studies with a minimal effort of coding.
+Model- and design-based simulations are used to gain insights into the quality of \red{the methods utilized}.
+In this article we present a framework \red{which may help to support }the reproducibility of simulation studies in articles and during research.
+\red{The \proglang{R}-package \proglang{saeSim} is adjusted} to provide a simulation environment for the special case of small area estimation.
+The package may allow the prospective researcher during the research process to produce simulation studies \red{with minimal coding effort.}
 }
@@
 %% end of declarations %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-\newcommand{\red}[1]{\color{red} #1 \color{black} }
+\newcommand{\red}[1]{\textcolor{red}{#1}}
 
@@
 The demand for reliable small area statistics from sample surveys has substantially grown over the last decades due to their use in public and private sectors.
-In this paper we present a framework for simulation studies inside the field of small area estimation.
+In this paper we present a framework for simulation studies \red{within} the field of small area estimation.
 This tool might be useful for the prospective researcher or data analyst to provide reproducible research.
@@
 
-Next to the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational environment like data and source code.
+\red{Besides }the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational \red{environment, like} data and source code.
 However, real data is often very sensitive and governed by strict confidentiality rules.
@@
 Then, samples are selected repeatedly from the underlying finite population and different estimation methods are applied in each replication.
-The obtained estimates are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
+The estimates so obtained are compared to the true values of the population, for instance, in terms of relative bias (RB) or relative root mean squared error (RRMSE).
 \item Model-based: The simulation study uses data drawn from certain distributions.
 In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme.
-The sample is used to estimate the quantity of interest and quality measures (like RB and RRMSE) are derived.
+The sample is used to estimate the quantity of interest \red{for which} quality measures (like RB and RRMSE) are derived.
 \end{itemize}
@@
 Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes.
-Especially regional or group-specific comparisons are of interest \citep[cf.][]{Sch13}.
-Surveys which shall provide sufficient data for these regional indicators, however, are generally designed for larger areas.
-Hence, sample information on more detailed levels, e.g.
+\red{Of special interest here are regional or group specific comparisons \citep[cf.][]{Sch13}.
+Surveys which are utilized to report these regional indicators, however, are generally designed for larger areas.} \red{Hence sample} information on more detailed levels, e.g.
 municipalities, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}.
-In this case, small area estimation methods may reveal highly improved results for the target estimates.
+\red{In this case small} area estimation methods may reveal highly improved results for the target estimates.
 Small area estimation has become more and more attractive over the last decade:
@@
 However, simulation studies in the context of small area estimation are often presented very briefly.
-Thus, there is a need to have a suited framework to guarantee the reproducibility of analysis.
-To the best of our knowledge, there is not any \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
+\red{Thus there is }a need to have \red{a suitable framework} to guarantee the reproducibility of analysis.
+To the best of our knowledge, \red{there is no} \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
 
 The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible.
-To be more precise, the package has three main objectives: First, provide tools for data generation.
-Second, unify the process of simulation studies.
-Third, make the source code of simulation studies available, such that it supports the conducted research in a transparent manner.
+To be more precise, \red{the suggested package} has three main objectives: First, \red{to provide} tools for data generation.
+Second, \red{to unify} the process of simulation studies.
+Third, \red{to make} the source code of simulation studies available, such that it supports the conducted research in a transparent manner.
 
-The paper is organised as follows.
+\red{This paper} is organised as follows.
 In Section \ref{sec:SAE} we give a short introduction to small area estimation focusing mainly on unit-level \citep{battese88} and area-level models \citep{fay79}.
@@
 
-The objective of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available.
-Groups may be areas or other entities, for example defined by socio-economic characteristics.
-The demand for such estimators is rising as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
+\red{The aim} of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available.
+Groups may be areas or other entities \red{defined, for example, by} socio-economic characteristics.
+The demand for such estimators \red{is increasing} as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
 As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighbouring or \textit{similar} domains.
@@
 In those frameworks every defined function takes a \proglang{data.frame} as input and returns it modified.
-This leads to a natural connection between all defined functions as the result of one function can be directly passed to the next as an argument.
-The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasises the process of data manipulation.
+This leads to a natural connection between all defined functions \red{since} the result of one function can be directly passed to the next as an argument.
+The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only \red{emphasizes} the process of data manipulation.
 To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (cf.
@@
 In \proglang{saeSim} we extend this approach to simulation studies in the field of small area estimation.
-The main focus lies on the description of a simulation as a process of data manipulation.
+\red{The main focus lies in} the description of a simulation as a process of data manipulation.
 Each step in this process can be defined as a self contained component (function) and thus can be easily replaced, extended and most importantly reused.
-Before we go into details of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.
+Before we \red{go into the details} of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.
 
-Simulation studies in small area estimation address three different levels, the population, the sample and data on aggregated level.
+Simulation studies in small area estimation address three \red{different levels; these are the population}, the sample and data on aggregated level.
 Figure \ref{fig:flowdiagram} illustrates these levels.
@@
 
-The scope of this article is not to promote any of those viewpoints, we just want to incorporate the different simulation concepts in a common framework.
-The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study is a data table, the question is, if this data is \textit{fixed} or \textit{random} over simulations.
+\red{The scope of this article is not to opt for viewpoints.
+The aim is to incorporate the different simulation concepts in a common framework.} The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study \red{is a data table; here the question is whether this data is \textit{fixed} or \textit{random} over simulations}.
 Or from a more technical point of view, is the data generation (the second step in Figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted.
-Depending on the choice of a fixed or random population it is necessary to recompute the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).
+Depending on the choice of a fixed or random population it is necessary to \red{re-compute} the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).
 
 The \textbf{sample-level} is necessary when domain predictions are conducted for unit-level models.
-Independently of how the population is treated, fixed or random, this phase consists of two steps: Firstly, draw a sample according to a specific sampling scheme.
-Secondly, conduct computations on the samples (fourth and fifth component in Figure \ref{fig:flowdiagram}).
+Independently of how the population is treated \red{- whether as fixed or random - }this phase consists of two steps: \red{Firstly, drawing} a sample according to a specific sampling scheme.
+{Secondly, conducting} computations on the samples (fourth and fifth component in Figure \ref{fig:flowdiagram}).
 Given a sample, small area methods are applied.
@@
 
-As the sample-level is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}).
+\red{Since the sample-level} is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}).
 Area-level models in small area estimation typically only use information available for domains (in contrast to units).
-Thus, the question for simulation studies for area-level methods is, if the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or if the data is generated directly on area-level, i.e.
+\red{Thus, the question for simulation studies for area-level methods is, whether the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or the data is generated directly on area-level, i.e.
 drawn from an area-level model.
-Depending on whether unit-level data and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample.
+Depending on whether or not unit-level data} and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample.
 %Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.
@@
 
-From this considerations, \proglang{saeSim} maps the different steps into \proglang{R}.
+\red{Seen this way,} \proglang{saeSim} maps the different steps into \proglang{R}.
 Two layers with separate responsibilities need to be discussed.
@@
 We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}.
-Before, we introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation.
+\red{First though, we} introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation.
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
@@
 Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we notice that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme.
-\proglang{sim\_sample} is responsible to control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
+\red{\proglang{sim\_sample} is responsible as a control} when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
 Separating the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
@@
 Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows (the head) of the resulting data table are printed.
-This enables interactivity with the object itself, however, it hides that the setup object is a collection of functions to be called.
+This enables interactivity with the object \red{itself; however, it hides the fact that the setup} object is a collection of functions to be called.
 In this model the error component $e_i$ has different variances which is not covered by a predefined function.
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
-Hence, we define a function named \proglang{comp\_FH} and add it to the process:
+\red{Hence we }define a function named \proglang{comp\_FH} and add it to the process:
 
@@
 An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios.
-At this time we do not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}.
+\red{Currently we do} not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}.
 In the design-based scenario we show how to process the result data into graphs with only a few lines of code.
@@
 It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is also used as an example data set.
-To keep this study as simple as possible, we further restrict the data on the main income holder and only use some of the provided auxiliary information.
+To keep this study as simple as possible, \red{we further restrict the data to the main income holder} and only use some of the provided auxiliary information.
 
@@
 The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator.
-This function expects three data objects and returns the domain predictions.
+\red{This function takes three data }objects and returns the domain predictions.
 The three objects are the sampled data, the population means of the auxiliary variables and the population sizes in each domain.
 
-Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
-This allows us to process on the same time a single data frame and some meta data.
-It is important to notice that some functions for manipulating data frames in \proglang{R} don't preserve their attributes.
-The prospective user of the \proglang{saeSim} has to keep this in mind when implementing user defined functions.
-However, all functions in \proglang{saeSim} are able to preserve their attributes.
-Other options can be applied within the possibilities of the \proglang{R} language.
-For instance, one could use closures to make the meta data only available for specific functions.
-This approach needs advanced functional programming skills and may add an additional level of complexity to the package user.
-However, from our perspective, adding attributes to the data is be a very flexible form of processing data on different aggregation levels and is used in this package.
+\red{Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
+This allows us to process meta data alongside the main data frame.
+It is important to note that not all functions for manipulating data frames in \proglang{R} preserve these attributes.
+Users of \proglang{saeSim} have to keep this in mind when they implement new functions.
+Defining the interfaces between components differently is one possibility to avoid the usage of attributes.
+This can be done, for example, by using generic vectors or S4 classes instead of data frames.
+However this will add complexity to the process of data manipulation underlying the package which we try to avoid by following the paradigm: \textit{data frame in, data frame out}.
+Thus all functions in \proglang{saeSim} preserve the attributes of the main data frame.}
 
@@
 As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data.
-Then the sampling component is added, in which we define to draw 10 per cent sample of the observations from each domain with simple random sampling.
+Then the sampling component is added, \red{where the definition is to draw 10 per cent samples} of the observations from each domain with simple random sampling.
 
@@
 Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
-Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other.
+Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define \red{each component independently of the others}.
 This automatically organises the simulation and each component is arranged using the simulation framework.
-Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
+\red{Hence we }define two functions, one for adding the direct estimates and one for adding the EBLUP.
 
@@
 
-A positive aspect of the above definitions is, that the code for each step is relatively short and the purpose is clearly defined.
+A positive aspect of the above definitions \red{is that the} code for each step is relatively short and the purpose is clearly defined.
 This may help to improve readability and to reproduce the research.
@@
 \label{sec:outlook}
-From our perspective, there is a need for sharing tools for data generation and simulation amongst the scientific community to guarantee the reproducibility of research.
+From our perspective, there is a need for sharing tools for data generation \red{and simulation among the scientific community} to guarantee the reproducibility of research.
 \proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation.
@@
 
-The package provides more features than introduced in this article.
-To mention is the support of outlier contaminated data.
-At this time only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
+The package provides more features \red{than are} introduced in this article.
+\red{One may mention in this context the support of outlier contaminated data.
+Currently only representative outliers} (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
 However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population, e.g., incorrectly recorded values).

### 2015-01-26 saeSim.tex
saeSim corrections

@@
 The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator.
-This function expects three data objects and returns the domain predictions.
+\red{This function takes three data }objects and returns the domain predictions.
 The three objects are the sampled data, the population means of the auxiliary variables and the population sizes in each domain.
 
-Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
-This allows us to process on the same time a single data frame and some meta data.
-It is important to notice that some functions for manipulating data frames in \proglang{R} don't preserve their attributes.
-The prospective user of the \proglang{saeSim} has to keep this in mind when implementing user defined functions.
-However, all functions in \proglang{saeSim} are able to preserve their attributes.
-Other options can be applied within the possibilities of the \proglang{R} language.
-For instance, one could use closures to make the meta data only available for specific functions.
-This approach needs advanced functional programming skills and may add an additional level of complexity to the package user.
-However, from our perspective, adding attributes to the data is be a very flexible form of processing data on different aggregation levels and is used in this package.
+\red{Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
+This allows us to process meta data alongside the main data frame.
+It is important to note that not all functions for manipulating data frames in \proglang{R} preserve these attributes.
+Users of \proglang{saeSim} have to keep this in mind when they implement new functions.
+Defining the interfaces between components differently is one possibility to avoid the usage of attributes.
+This can be done, for example, by using generic vectors or S4 classes instead of data frames.
+Yet this will add complexity to the process of data manipulation underlying the package which we try to avoid by following the paradigm: \textit{data frame in, data frame out}.
+Thus all functions in \proglang{saeSim} preserve the attributes of the main data frame.}
 

### 2015-01-27 replies_to_referee/Replies_to_referee.tex
saeSim proofread

@@
 Survey statistics are used, for example, in order to deliver specific indicators as a basis for
-economic and political decision processes. Especially regional or group-specific comparisons
-are of interest (cf. Schmid and M\"unnich 2014). Surveys which shall provide sufficient data
-for these regional indicators, however, are generally designed for larger areas. Hence, sample
+economic and political decision processes. Of special interest here are regional or group
+specific comparisons (cf. Schmid and Münnich 2014). Surveys which are utilized to report
+these regional indicators, however, are generally designed for larger areas. Hence sample
 information on more detailed levels, e.g. municipalities, is hardly available so that classical
 estimation methods (direct estimators) may lead to high variances of the estimates (cf. Ghosh
-and Rao 1994). In this case, small area estimation methods may reveal highly improved results
+and Rao 1994). In this case small area estimation methods may reveal highly improved results
 for the target estimates. Small area estimation has become more and more attractive over
@@
 We think this is possible by sticking to the "data.frame in, data.frame out" philosophy.
-Thus, we decided to support functions which preserve attributes.
+Thus we decided to support functions which preserve attributes.
 All present functions in the package will preserve attributes of the main data frame.
-We have added the following paragraph in the paper (Section 4.2):\\\\
+We added the following paragraph to section 4.2:\\\\
 	\textit{
-	Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
-This allows us to process on the same time a single data frame and some meta data.
-It is important to notice that some functions for manipulating data frames in R don't preserve their attributes.
-The prospective user of the saeSim has to keep this in mind when implementing user defined functions.
-However, all functions in saeSim are able to preserve their attributes.
-Other options can be applied within the possibilities of the R language.
-For instance, one could use closures to make the meta data only available for specific functions.
-This approach needs advanced functional programming skills and may add an additional level of complexity to the package user.
-However, from our perspective, adding attributes to the data is be a very flexible form of processing data on different aggregation levels and is used in this package.
+	Before we begin to construct the simulation setup, we store these data frames as attributes to
+the population data. This allows us to process meta data alongside the main data frame. It
+is important to note that not all functions for manipulating data frames in R preserve these
+attributes. Users of saeSim have to keep this in mind when they implement new functions.
+Defining the interfaces between components differently is one possibility to avoid the usage
+of attributes. This can be done, for example, by using generic vectors or S4 classes instead of
+data frames. However this will add complexity to the process of data manipulation underlying
+the package which we try to avoid by following the paradigm: data frame in, data frame out.
+Thus all functions in saeSim preserve the attributes of the main data frame.
 	}
@@
 
-\noindent Reply: We strongly apology for the mistakes in the article.
-We did a careful double check of the paper.
+\noindent Reply: We apologise for the mistakes in the article.
+We did a careful double check during the revision.
 In addition, we followed your suggestion to check the manuscript by an English native speaker.
@@
 
-	Reply: We acknowledge that the sentence may create some confusion to the prospective reader.
-Therefore, we have deleted to sentence to make the paragraph more clear.
+	Reply: We acknowledge that the sentence may create some confusion.
+Therefore we have deleted the sentence to improve the readability of the paragraph.
 In the revised version of the paper we say the following:\\\\
 	\textit{
-		In the next step, we define components which add the estimates of interest to the data.
-Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
-Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independent of each other.
-This automatically organises the simulation and each component is arranged using the simulation framework.
-Hence, we define two functions, one for adding the direct estimates and one for adding the EBLUP.
+In the next step, we define components which add the estimates of interest to the data. Here
+we compute the direct estimator of the mean income in each domain and the EBLUP under
+the BHF model. Although this could be done in one step, we separate the two computations to
+illustrate how to combine several estimations and how to define each component independently
+of the others. This automatically organises the simulation and each component is arranged
+using the simulation framework. Hence we define two functions, one for adding the direct
+estimates and one for adding the EBLUP.
 		}
@@
 
-\noindent Reply: We strongly apology for the grammatical errors in the article. We did a careful double check of the paper. In addition, the manuscript was checked by an English native speaker.
+\noindent Reply: We apologise for the errors in the article. We did a careful double check of the paper. In addition, the manuscript was checked by an English native speaker.
 

### 2015-01-27 saeSim.Rnw
saeSim proofread

@@
 The demand for reliable regional estimates from sample surveys has substantially grown over the last decades.
-Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in regions are too small to apply direct estimators.
-Model- and design-based simulations are used to gain insights into the quality of \red{the methods utilized}.
-In this article we present a framework \red{which may help to support }the reproducibility of simulation studies in articles and during research.
-\red{The \proglang{R}-package \proglang{saeSim} is adjusted} to provide a simulation environment for the special case of small area estimation.
-The package may allow the prospective researcher during the research process to produce simulation studies \red{with minimal coding effort.}
+Small area estimation provides statistical methods to produce reliable predictions when the sample sizes in specific regions are too small to apply direct estimators.
+Model- and design-based simulations are used to gain insights into the quality of the methods utilized.
+In this article we present a framework which may help to support the reproducibility of simulation studies in articles and during research.
+The \proglang{R}-package \proglang{saeSim} is adjusted to provide a simulation environment for the special case of small area estimation.
+The package may allow the prospective researcher during the research process to produce simulation studies with minimal coding effort.
 }
@@
 The demand for reliable small area statistics from sample surveys has substantially grown over the last decades due to their use in public and private sectors.
-In this paper we present a framework for simulation studies \red{within} the field of small area estimation.
+In this paper we present a framework for simulation studies within the field of small area estimation.
 This tool might be useful for the prospective researcher or data analyst to provide reproducible research.
@@
 
-\red{Besides }the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational \red{environment, like} data and source code.
+Besides the combination of text and source code, reproducible research aims at the availability of the full academic research, which is the paper combined with the full computational environment, like data and source code.
 However, real data is often very sensitive and governed by strict confidentiality rules.
@@
 In each iteration, the population is generated from a model and a sample is selected according to a specific sampling scheme.
-The sample is used to estimate the quantity of interest \red{for which} quality measures (like RB and RRMSE) are derived.
+The sample is used to estimate the quantity of interest for which quality measures (like RB and RRMSE) are derived.
 \end{itemize}
@@
 Survey statistics are used, for example, in order to deliver specific indicators as a basis for economic and political decision processes.
-\red{Of special interest here are regional or group specific comparisons \citep[cf.][]{Sch13}.
-Surveys which are utilized to report these regional indicators, however, are generally designed for larger areas.} \red{Hence sample} information on more detailed levels, e.g.
+Of special interest here are regional or group specific comparisons \citep[cf.][]{Sch13}.
+Surveys which are utilized to report these regional indicators, however, are generally designed for larger areas.
+Hence sample information on more detailed levels, e.g.
 municipalities, is hardly available so that classical estimation methods (direct estimators) may lead to high variances of the estimates \citep[cf.][]{Gho94}.
-\red{In this case small} area estimation methods may reveal highly improved results for the target estimates.
+In this case small area estimation methods may reveal highly improved results for the target estimates.
 Small area estimation has become more and more attractive over the last decade:
@@
 However, simulation studies in the context of small area estimation are often presented very briefly.
-\red{Thus there is }a need to have \red{a suitable framework} to guarantee the reproducibility of analysis.
-To the best of our knowledge, \red{there is no} \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
+Thus there is a need to have a suitable framework to guarantee the reproducibility of analysis.
+To the best of our knowledge, there is no \proglang{R}-package or framework adjusted for the special case of small area estimation which provides a simulation environment.
 
 The aim of this article is to introduce a new \proglang{R}-package, \proglang{saeSim}, which supports the process of making simulation studies in the field of small area estimation reproducible.
-To be more precise, \red{the suggested package} has three main objectives: First, \red{to provide} tools for data generation.
-Second, \red{to unify} the process of simulation studies.
-Third, \red{to make} the source code of simulation studies available, such that it supports the conducted research in a transparent manner.
+To be more precise, the suggested package has three main objectives: First, to provide tools for data generation.
+Second, to unify the process of simulation studies.
+Third, to make the source code of simulation studies available, such that it supports the conducted research in a transparent manner.
 
-\red{This paper} is organised as follows.
+This paper is organised as follows.
 In Section \ref{sec:SAE} we give a short introduction to small area estimation focusing mainly on unit-level \citep{battese88} and area-level models \citep{fay79}.
@@
 
-\red{The aim} of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available.
-Groups may be areas or other entities \red{defined, for example, by} socio-economic characteristics.
-The demand for such estimators \red{is increasing} as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
+The aim of small area estimation is to produce reliable statistics (means, quantiles, proportions, etc.) for domains where few or no sampled units are available.
+Groups may be areas or other entities defined, for example, by socio-economic characteristics.
+The demand for such estimators is increasing as they are used for fund allocation, educational and health programs \citep{pfeffermann13}.
 As direct estimation of such statistics are considered to be unreliable (with respect to MSE), methods in small area estimation try to improve the domain predictions by borrowing strength from neighbouring or \textit{similar} domains.
@@
 In those frameworks every defined function takes a \proglang{data.frame} as input and returns it modified.
-This leads to a natural connection between all defined functions \red{since} the result of one function can be directly passed to the next as an argument.
-The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only \red{emphasizes} the process of data manipulation.
+This leads to a natural connection between all defined functions since the result of one function can be directly passed to the next as an argument.
+The symbioses of these packages with the pipe operator (\proglang{\%>\%}) from the package \proglang{magrittr} \citep{bache14} only emphasizes the process of data manipulation.
 To avoid nested function calls the operator can be used to improve the readability as expressions can be read from left to right (cf.
@@
 In \proglang{saeSim} we extend this approach to simulation studies in the field of small area estimation.
-\red{The main focus lies in} the description of a simulation as a process of data manipulation.
+The main focus lies in the description of a simulation as a process of data manipulation.
 Each step in this process can be defined as a self contained component (function) and thus can be easily replaced, extended and most importantly reused.
-Before we \red{go into the details} of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.
+Before we go into the details of the functionality of the package we discuss the process behind simulation studies and how \proglang{saeSim} maps this process into \proglang{R}.
 
-Simulation studies in small area estimation address three \red{different levels; these are the population}, the sample and data on aggregated level.
+Simulation studies in small area estimation address three different levels; these are the population, the sample and data on aggregated level.
 Figure \ref{fig:flowdiagram} illustrates these levels.
@@
 
-\red{The scope of this article is not to opt for viewpoints.
-The aim is to incorporate the different simulation concepts in a common framework.} The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study \red{is a data table; here the question is whether this data is \textit{fixed} or \textit{random} over simulations}.
+The scope of this article is not to opt for viewpoints.
+The aim is to incorporate the different simulation concepts in a common framework.
+The \textit{base} (first component in Figure \ref{fig:flowdiagram}) of a simulation study is a data table; here the question is whether this data is \textit{fixed} or \textit{random} over simulations.
 Or from a more technical point of view, is the data generation (the second step in Figure \ref{fig:flowdiagram}) repeated in each simulation run or omitted.
-Depending on the choice of a fixed or random population it is necessary to \red{re-compute} the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).
+Depending on the choice of a fixed or random population it is necessary to re-compute the population domain-statistics like domain means and variances, or other statistics of interest (third component in Figure \ref{fig:flowdiagram}).
 
 The \textbf{sample-level} is necessary when domain predictions are conducted for unit-level models.
-Independently of how the population is treated \red{- whether as fixed or random - }this phase consists of two steps: \red{Firstly, drawing} a sample according to a specific sampling scheme.
+Independently of how the population is treated - whether as fixed or random - this phase consists of two steps: Firstly, drawing a sample according to a specific sampling scheme.
 {Secondly, conducting} computations on the samples (fourth and fifth component in Figure \ref{fig:flowdiagram}).
@@
 
-\red{Since the sample-level} is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}).
+Since the sample-level is necessary when unit-level models are applied, the \textbf{aggregate-level} is conducted when area-level models are applied (the seventh and last component in Figure \ref{fig:flowdiagram}).
 Area-level models in small area estimation typically only use information available for domains (in contrast to units).
-\red{Thus, the question for simulation studies for area-level methods is, whether the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or the data is generated directly on area-level, i.e.
+Thus the question for simulation studies for area-level methods is whether the data is generated on unit-level and is used after the aggregation (sixth component in Figure \ref{fig:flowdiagram}) or whether the data is generated directly on area-level, i.e.
 drawn from an area-level model.
-Depending on whether or not unit-level data} and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample.
+Depending on whether or not unit-level data and sampling are part of the simulation process, the aggregate-level follows the generation of the population or is based on the aggregated sample.
 %Again, we do not promote a specific viewpoint but simply allow steps in the process of simulation to be omitted.
@@
 
-\red{Seen this way,} \proglang{saeSim} maps the different steps into \proglang{R}.
+Seen this way, \proglang{saeSim} maps the different steps into \proglang{R}.
 Two layers with separate responsibilities need to be discussed.
@@
 We present two applications of \proglang{saeSim}, one model-based simulation in Section \ref{sec:csModel} and a design-based simulation in Section \ref{sec:csDesign}.
-\red{First though, we} introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation.
+First, though, we introduce some basic functionalities as the pipe operator (\proglang{\%>\%}) needs some explanation.
 The pipe operator is designed to make otherwise nested expressions more readable as a line can be read from left to right, instead from inside out \citep{bache14}.
@@
 Without knowing anything about the setup defined in \proglang{sim\_base\_lm} we notice that \proglang{setup1} and \proglang{setup2} only differ in the applied sampling scheme.
-\red{\proglang{sim\_sample} is responsible as a control} when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
+\proglang{sim\_sample} is responsible as a control when a function is applied (after the population-level) and \proglang{sample\_number(5)} and \proglang{sample\_fraction(0.05)} define the explicit way of drawing samples.
 Separating the responsibility of each component into what is applied and when it is applied makes it possible to add new components to any step in the process.
@@
 Note that if you print a simulation setup to the console, as in the above example, one simulation run is performed and only the first rows (the head) of the resulting data table are printed.
-This enables interactivity with the object \red{itself; however, it hides the fact that the setup} object is a collection of functions to be called.
+This enables interactivity with the object itself; however, it hides the fact that the setup object is a collection of functions to be called.
 In this model the error component $e_i$ has different variances which is not covered by a predefined function.
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
-\red{Hence we }define a function named \proglang{comp\_FH} and add it to the process:
+Hence we define a function named \proglang{comp\_FH} and add it to the process:
 
@@
 An additional variable \proglang{idR} is automatically added as an ID-variable for the iteration as well as a variable \proglang{simName} to distinguish between scenarios.
-\red{Currently we do} not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}.
+In \proglang{saeSim} we do not provide further tools to process the resulting data as there are many tools readily available in \proglang{R}.
 In the design-based scenario we show how to process the result data into graphs with only a few lines of code.
@@
 It is published alongside the \proglang{R}-package \proglang{simFrame} \citep{Alf10} where it is also used as an example data set.
-To keep this study as simple as possible, \red{we further restrict the data to the main income holder} and only use some of the provided auxiliary information.
+To keep this study as simple as possible, we further restrict the data to the main income holder and only use some of the available auxiliary information.
 
@@
 The function \proglang{eblupBHF} from the package \proglang{sae} is an implementation of the BHF estimator.
-\red{This function takes three data }objects and returns the domain predictions.
+This function takes three data objects and returns the domain predictions.
 The three objects are the sampled data, the population means of the auxiliary variables and the population sizes in each domain.
 
-\red{Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
+Before we begin to construct the simulation setup, we store these data frames as attributes to the population data.
 This allows us to process meta data alongside the main data frame.
@@
 However this will add complexity to the process of data manipulation underlying the package which we try to avoid by following the paradigm: \textit{data frame in, data frame out}.
-Thus all functions in \proglang{saeSim} preserve the attributes of the main data frame.}
+Thus all functions in \proglang{saeSim} preserve the attributes of the main data frame.
 
@@
 As stated earlier, the starting point of a simulation setup is to provide a \proglang{data.frame} as \textit{base-component} which, in this case, is the population data.
-Then the sampling component is added, \red{where the definition is to draw 10 per cent samples} of the observations from each domain with simple random sampling.
+Then the sampling component is added, where the definition is to draw 10 per cent samples of the observations from each domain with simple random sampling.
 
@@
 Here we compute the direct estimator of the mean income in each domain and the EBLUP under the BHF model.
-Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define \red{each component independently of the others}.
+Although this could be done in one step, we separate the two computations to illustrate how to combine several estimations and how to define each component independently of the others.
 This automatically organises the simulation and each component is arranged using the simulation framework.
-\red{Hence we }define two functions, one for adding the direct estimates and one for adding the EBLUP.
+Hence we define two functions, one for adding the direct estimates and one for adding the EBLUP.
 
@@
 
-A positive aspect of the above definitions \red{is that the} code for each step is relatively short and the purpose is clearly defined.
+A positive aspect of the above definitions is that the code for each step is relatively short and the purpose is clearly defined.
 This may help to improve readability and to reproduce the research.
@@
 \label{sec:outlook}
-From our perspective, there is a need for sharing tools for data generation \red{and simulation among the scientific community} to guarantee the reproducibility of research.
+From our perspective, there is a need for sharing tools for data generation and simulation among the scientific community in order to guarantee the reproducibility of research.
 \proglang{saeSim} may provide an adequate framework for pursuing this aim in the field of small area estimation.
@@
 
-The package provides more features \red{than are} introduced in this article.
-\red{One may mention in this context the support of outlier contaminated data.
-Currently only representative outliers} (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
+The package provides more features than are introduced in this article.
+One may mention in this context the support of outlier contaminated data.
+Currently only representative outliers (outlying observations in the population) are supported \citep[cf.][]{Cha86}.
 However, we plan to extend this feature to non-representative outliers (outliers are part of the sample but not the population, e.g., incorrectly recorded values).

### 2015-01-27 saeSim.tex
saeSim proofread

@@
 This can be done, for example, by using generic vectors or S4 classes instead of data frames.
-Yet this will add complexity to the process of data manipulation underlying the package which we try to avoid by following the paradigm: \textit{data frame in, data frame out}.
-Thus all functions in \proglang{saeSim} preserve the attributes of the main data frame.}
+However this will add complexity to the process of data manipulation underlying the package which we try to avoid by following the paradigm: \textit{data frame in, data frame out}.
+Thus all functions in \proglang{saeSim} preserve the attributes of the main data frame.
 

### 2015-02-12 saeSim.Rnw
update nach review 2

@@
 <<eval=FALSE>>=
-library(magrittr)
+library("magrittr")
 colMeans(matrix(rnorm(10), ncol = 2))
@@
 <<eval=TRUE, echo=FALSE>>=
-library(saeSim)
+library("saeSim")
 @
@@
 <<eval=FALSE>>=
-library(saeSim)
+library("saeSim")
 setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
+To avoid naming conflicts between the dependencies of \proglang{sae} and the package \proglang{dplyr} \citep{wickham14a} we make use of the double colon operator in order to access the function without attaching the package.
 Hence we define a function named \proglang{comp\_FH} and add it to the process:
@@
   modelFH <- sae::eblupFH(y ~ x, vardir, data = dat)
-  dat$FH <- modelFH$eblup
+  dat$FH <- as.numeric(modelFH$eblup)
   dat
 }
+
 setup <- setup %>% sim_comp_agg(comp_FH)
@@
 <<>>=
-library(dplyr)
+library("dplyr")
 simResults <- sim(setup, R = 100) %>% rbind_all
@@
 <<eval=FALSE>>=
-library(ggplot2)
+library("ggplot2")
 ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 <<designSimBIAS, fig = TRUE, width = 8.3, height=4, include = FALSE, echo = FALSE>>=
-library(ggplot2)
+library("ggplot2")
 ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 
@@
 \end{figure}
-\clearpage
 
@@
 
-A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallel} package in \proglang{R} \citep{r14}.
+A more technical feature is a back-end for parallel computations which is a link to the \proglang{parallelMap} package in \proglang{R} \citep{bischl15}.
 Tools to process result data after the simulation, i.e.

### 2015-02-12 saeSim.tex
update nach review 2

@@
 \begin{Sinput}
-> library(magrittr)
+> library("magrittr")
 > colMeans(matrix(rnorm(10), ncol = 2))
@@
 \begin{Sinput}
-> library(saeSim)
+> library("saeSim")
 > setup1 <- sim_base_lm() %>% sim_sample(sample_number(5))
@@
 \begin{Soutput}
+data.frame [40 x 3]
+
    idD          x          v
@@
 6    6 -3.2818735 -0.7074952
+.. ...        ...        ...
 \end{Soutput}
@@
 \begin{Soutput}
+data.frame [40 x 5]
+
    idD          x          v vardir          e
@@
 6    6  1.3318015  0.7126663    0.6  1.7088396
+.. ...        ...        ...    ...        ...
 \end{Soutput}
@@
 +   modelFH <- sae::eblupFH(y ~ x, vardir, data = dat)
-+   dat$FH <- modelFH$eblup
++   dat$FH <- as.numeric(modelFH$eblup)
 +   dat
@@
 \begin{Soutput}
+data.frame [40 x 8]
+
    idD         x          v vardir          e         y  trueStat        FH
@@
 6    6  9.990646 -2.0001649    0.6 -0.7754272 117.20570 117.98113 118.08379
+.. ...       ...        ...    ...        ...       ...       ...       ...
 \end{Soutput}
@@
 \begin{Sinput}
-> library(dplyr)
+> library("dplyr")
 > simResults <- sim(setup, R = 100) %>% rbind_all
@@
 \begin{Soutput}
+data.frame [2,500 x 5]
+
        region eqIncome age agesq gender
@@
 6  Burgenland 19369.91  63  3969 female
+..        ...      ... ...   ...    ...
 \end{Soutput}
@@
 \begin{Soutput}
+data.frame [9 x 4]
+
           region   direct      BHF trueStat
@@
 6  Upper Austria 20636.94 20504.37 20517.29
+..           ...      ...      ...      ...
 \end{Soutput}
@@
 \begin{Sinput}
-> library(ggplot2)
+> library("ggplot2")
 > ggplot(ggDat, aes(x = region, y = prediction - trueStat, fill = method)) + 

### 2015-02-20 saeSim.tex
update

@@
 \usepackage{subcaption}
+\usepackage{placeins} % \FloatBarrier before conclusion
 
@@
 For the estimation of the EBLUP under the FH model we use the function \proglang{eblupFH} from the package \proglang{sae} \citep{molina13}.
-To avoid naming conflicts between the dependencies of \proglang{sae} and the package \proglang{dplyr} \citep{wickham14a} we make use of the double colon operator in order to access the function without attaching the package.
+To avoid naming conflicts between the dependencies of \proglang{sae} and the package \proglang{dplyr} \citep{wickham14a} we make use of the double colon operator in order to call the function \proglang{eblupFH} without attaching the package.
 Hence we define a function named \proglang{comp\_FH} and add it to the process:
@@
 \begin{Sinput}
-> ggDat <- reshape2::melt(simResults,
+> ggDat <- reshape2::melt(
++   simResults,
 +   id.vars = c("region", "trueStat"), 
@@
 
+\FloatBarrier
 \section{Outlook}
